### 2017-04-01 appendix.tex
source commit

\section {Appendix}

\section {Netlist at different levels of abstractions}
%Figure~\ref{fig:v2c-example} shows the Verilog RTL 
%design described at different levels of granularity: \emph{bit-level},
%\emph{word-level}, \emph{software-level}. Note that the word-level 
%netlist shown here is not a standard representation but is tool specific. 
One of the challenges in the Verilog to C translation is the handling of 
parallelism, which arises from dependencies between procedural blocks 
and continuous (wire) assignments or combinatorial exchanges (feedback loop) 
between modules, as shown in Figure~\ref{fig:v2c-example}. 
The code on the left shows a Verilog design with a combinatorial 
feedback loop. The equivalent bit-level, word-level netlist and software netlist 
in C is shown in the second, third and forth column respectively.
The top level module $\mathit{top}$ in the Verilog code instantiates two sub-modules, $A$ and $B$. 
The combinatorial exchanges between module $\mathit{top}$, $A$ and $B$ are modeled in the 
function $A\_comb()$ in the software netlist model. The function $A\_comb()$ contains
an assumption that encodes the dependencies over corresponding signals in the 
combinatoral logic. The sequential clocked block in module $A$ is modeled in a separate 
function $A\_seq()$. The difference between word-level 
netlist and software netlist is that the control-flow 
structure is retained in the later. Whereas, the control-flow structure 
is lost in bit-level or word-level netlist. Thus, the translation 
to software netlist gives an opportunity for the backend analysis engine to 
exploit the feasibility of the control-flow structure using various 
path-based symbolic execution techniques, such as eager path-pruning, 
path-merging or loop acceleration techniques.

\begin{figure}[h]
\tiny
\begin{tabular}{l|l|l|l}
\hline
 Verilog & Bit-level netlist & Word-level netlist & Software netlist \\
\hline
\begin{lstlisting}[mathescape=true,language=Verilog]
module A(clk,x,bar,
        foo,y,msg);
 input clk,x,bar;
 output y,foo,msg;
 reg [2:0] q;
 wire [2:0] msg; 
 assign foo=x;
 assign y=bar;
 assign msg = q;
 always @(posedge clk) 
 begin
  if(x) q = foo+1;
  else  q = y+5;  
 end
endmodule

module B(foo,bar);
input foo;
output bar;
assign bar=foo;
endmodule

module top(x,clk);
 input x, clk;
 wire x,y,foo,bar,clk;
 wire [2:0] msg;
 A a(.clk(clk), .x(x),
 .bar(bar),.foo(foo),
 .y(y), .msg(msg));
 B b(foo,bar);
endmodule
\end{lstlisting}
&
\begin{lstlisting}[mathescape=true,language=C]
Variable map:
  input[0]=9,input[1]=10, input[2]=11, 
  input[3]=12, input[4]=13, input[5]=14, 
  input[6]=15, input[7]=19, input[8]=23, 
  input[9]=24, input[10]=25, input[11]=38, 
  top.b.foo=8, top.a.bar=4, top.a.x=3, 
  top.a.clk=2, top.clk=1, top.x=0

  Wire: top.b.bar=8,top.a.q_aux1[0]=!4,
  top.a.q_aux1[1]=4,top.a.q_aux1[2]=true,
  top.a.q_aux0[0]=!3,top.a.q_aux0[1]=3,
  top.a.q_aux0[2]=false,top.a.msg[0]=5, 
  top.a.msg[1]=6,top.a.msg[2]=7, 
  top.msg[0]=23,top.msg[1]=24,
  top.msg[2]=25,top.bar=38,top.foo=19,
  top.y=15,top.a.foo=3,top.a.y=4,

  Latch: top.a.q[0]=5, 
  top.a.q[1]=6, top.a.q[2]=7

Next state functions:
  NEXT(top.a.q[0])=!var(3) & !var(4)
  NEXT(top.a.q[1])=!(!var(3) & 
  !(!var(3) & var(4)))
  NEXT(top.a.q[2])=!var(3)

Transition constraints: 
  !(var(4) & !var(15)) & !(!var(4) & var(15))
  !(var(3) & !var(19)) & !(!var(3) & var(19))
  !(var(5) & !var(23)) & !(!var(5) & var(23))
  !(var(6) & !var(24)) & !(!var(6) & var(24))
  !(var(7) & !var(25)) & !(!var(7) & var(25))
  !(var(8) & !var(38)) & !(!var(8) & var(38))
  !(var(2) & !var(1)) & !(!var(2) & var(1))
  !(var(3) & !var(0)) & !(!var(3) & var(0))
  !(var(4) & !var(38)) & !(!var(4) & var(38))
  !(var(8) & !var(19)) & !(!var(8) & var(19))
  TRUE
  \end{lstlisting}
&
\begin{lstlisting}[mathescape=true,language=C]
State constraints:
top.a.foo==top.a.x
top.a.y==top.a.bar
top.a.msg==top.a.q
top.a.q_aux0== 
top.a.foo+3'b1
top.a.q_aux1== 
top.a.y+3'b101
top.a.clk==top.clk
top.a.x==top.x
top.a.bar==top.bar
top.a.foo==top.foo
top.a.y==top.y
top.a.msg==top.msg
top.b.bar==top.b.foo
top.b.foo==top.foo
top.b.bar==top.bar

Transisition 
constraints:
next(top.a.q)==
top.a.x? 
top.a.q_aux0:
top.a.q_aux1
\end{lstlisting}
&
\begin{lstlisting}[mathescape=true,language=C]
typedef unsigned char _u8;
struct module_A {
 _Bool clk,x,bar,y,foo;
 _u8 q; }
struct module_B {
  _Bool foo, bar; };
struct module_top {
  _Bool x,y,foo,bar,clk;
  struct module_A a;
  struct module_B b; };
extern struct module_top top;

void A_seq() {
 if(top.x)
  top.a.q = top.a.foo + 1;
 else
  top.a.q = top.a.y + 5;
}

void A_comb() {
  assume((top.a.foo == top.a.x)
  && (top.a.y == top.a.bar) 
  && (top.a.x == top.x)
  && (top.a.foo == top.foo) 
  && (top.a.bar == top.bar)
  && (top.a.y == top.y) 
  && (top.b.bar == top.b.foo)
  && (top.b.foo == top.foo) 
  && (top.b.bar == top.bar)
  && (top.msg == top.a.msg) 
  && (top.a.q == top.a.msg));
}
void main() {
 A_seq(); 
 A_comb();
}
\end{lstlisting}
\\
\hline
\end{tabular}
\caption{Verilog design representation at different levels of granularity}
\label{fig:v2c-example}
\end{figure}

\section {Structure of Software netlist model}
\textbf{Software netlist Model:} The pseudo-code for the software netlist 
model generated by \emph{v2c} is shown in figure~\ref{figure:structure}.

\begin{figure}[t]
\tiny
\begin{tabular}{l}
\hline
 Pseudo-code for software-netlist model \\
\hline
\begin{lstlisting}[mathescape=true,language=C]
// parameter definition
// macro definition
struct state_elements_design
  // declare all state-holding elements
  // of the current module 
};
struct state_elements_design sdesign;
int initial_block() { //initialization of nets }
// Input are passed by value and output by reference
int design (data_type input, data_type *output) {

  // shadow variable declaration
  declare shadow variables for 
  non-blocking assignments to 
  the register elements

  // continuous assignments
  Place all continuous statements which 
  are only dependant on input

  // always block 
  Place the always block respecting
  intra-modular dependencies
  // procedural statements are bit-precise

  // continuous assignments
  Place all continuous statements which 
  are updated by signals that are 
  driven from the always block

  // Module instantiations 
  Place all module instances 
  with proper mapping of 
  input and output ports

} // end of design module

int main() {
  // local varaibles 
  declare all local variables 
  which are passed to the design 
  initial_block(); // call to initial block
  // check if the design is sequential.
  // if so, then put a  while(1) wrapper
  while(1) {
   // nondeterministic assignments
   nondeterministically assign inputs values  
   // call the design
   design(input, &output);
  }
  // Assertions 
  Place the C assertions here 
} //end main 
\end{lstlisting}
\\
\hline
\end{tabular}
\caption{Skeleton of the software netlist model generated by \emph{v2c}}
\label{figure:structure}
\end{figure}

%%===============================================================================\
\para{Bit-precise code generation:}
%%===============================================================================\
\emph{v2c} generates a bit-precise software netlist model in~C.  The tool
automatically handles complex bit-level operators in Verilog like
bit-select or part-select operators from a vector, concatenation operators,
reduction OR and other operators.  \emph{v2c} retains the word-level structure 
of the Verilog RTL and generates vectored expressions. 
Figure~\ref{figure:bit} shows Verilog code (at the top) and the generated C
expressions (at the bottom) which are combinations of bit-wise and
arithmetic operators like bit-wise OR, AND, multiplication, subtraction,
shifts and other C operators.

\begin{figure*}[htbp]
\scriptsize
\begin{tabular}{l|l|l}
\hline
Bit-select & Part-select (System Verilog) & Concatenation \\
\hline
\begin{lstlisting}[mathescape=true,language=Verilog]
wire [7:0] in1,in2;
reg [7:0] out1,out2;
out1[7:5] = in1[4:2];
out2[6] = in2[4];
\end{lstlisting}
&
\begin{lstlisting}[mathescape=true,language=Verilog]
reg [31:0] in, out;
for(i=0;i<=3;i++) begin
out[8*i +: 8]=in[8*i +: 8];
end
\end{lstlisting}
&
\begin{lstlisting}[mathescape=true,language=Verilog]
wire [7:0] in1, in2;
reg [9:0] out;
out = {in2[5:2],in1[6:1]};
\end{lstlisting}
\\
\hline
\begin{lstlisting}[mathescape=true,language=C]
unsigned char in1,in2;
struct smain { 
 unsigned char out1,out2; } sm;
sm.out1 = sm.out1 & 0x1f | 
(((in1 & 0x1c)>>2)<<5);
sm.out2 = (sm.out2 & 0xbf)| 
(((in2 & 0x10)>>4)<<6); 
\end{lstlisting}
&
\begin{lstlisting}[mathescape=true,language=C]
struct smain {
 unsigned int in,out; } sm;
for(i=0;i<=3;i++) {
 x=8*i+(8-1); y=8*i;
 sm.out=(sm.out&!(2^31-2^y))
 |(sm.in&(2^31-2^y)); }
\end{lstlisting}
&
\begin{lstlisting}[mathescape=true,language=C]
unsigned char in1,in2;
struct smain { 
 unsigned char out; } sm;
sm.out = (((in2 >> 2)
 & 0xF) << 6)|
 ((in1 >> 1) & 0x3F);
\end{lstlisting}
\\
\hline
\end{tabular}
\caption{Handling Bit-select, part-select from vectors and concatenation}
\label{figure:bit}
\end{figure*}

%=======================================================================================
\section{Monolithic and Path-based Symbolic Execution} 
%=======================================================================================
Figure~\ref{figure:simulation} gives the path constraints generated 
by path-based and BMC based tools. Given a program fragment on the 
left shown in column~1, the path constraints corresponding to three paths 
in the program is shown in column~[2--4]. Note that all paths in this 
program are feasible. The monolithic path constraint generated by BMC 
is shown in column~5. BMC-based tools \emph{always} merges---generating 
only a \emph{single} bit-vector formula $C$ for a given unwinding bound $k$.  Note that 
this formula is linear in the size of the program and linear in $k$ 
even if there is an exponential number of paths in the program.  
For the constriant in column~5, the symbolic values of variables 
are computed as expressions over the initial values of variables 
$m$ and $t$, whereas the branching in the program yields expressions with 
the $\mathit{ite}$ operator.

\begin{figure}[t]
\scriptsize
\begin{tabular}{l|l|l|l|l}
\hline
Program & Path & Path & Path & Monolithic \\
        & Constraint 1 & Constraint 2 & Constraint 3 & Constraint\\
\hline
\begin{lstlisting}[mathescape=true,language=C]
void top(){
 if(reset) {
  m = 0;
  t = 0;
 }
 else {
  if(c > d)
   m = c+d;
  else
   t = (c & 3)<<d;
 }
}
\end{lstlisting}
&
\begin{minipage}{1.5cm}
$\begin{array}[t]{@{}l}
C_1 \; \equiv \\
\;\;\mathit{\mathit{reset}}_1 \neq 0\; \land \\
\;\; m_2 = 0\;\land \\
\;\; t_2 = 0
\end{array}$
\end{minipage}
&
\begin{minipage}{1.5cm}
$\begin{array}[t]{@{}l}
C_2 \; \equiv \\
\;\;\mathit{\mathit{reset}}_1=0\; \land \\
\;\;d_1 \ngeq c_1\; \land \\
\;\;m_3 = c_1 + d_1
\end{array}$
\end{minipage}
&
\begin{minipage}{1.5cm}
$\begin{array}[t]{@{}l}
C_3\; \equiv \\
\;\;\mathit{\mathit{reset}}_1 = 0\; \land \\
\;\;d_1 \ge c_1\; \land \\
\;\;t_3 = (c_1\&3) \\
          <\!\!<d_1
\end{array}$
\end{minipage}
&
\begin{minipage}{5cm}
$\begin{array}{l@{\,\,}c@{\,\,}l}
C &\iff& ((\mathit{\mathit{guard}}_1 =  \neg(\mathit{\mathit{reset}}_1 = 0)) \land \\
  &    & (m_2 = 0) \land (t_2 = 0) \land \\
  &    & (m_3 = m_1) \land (t_3 = t_1) \land \\
  &    & (\mathit{guard}_2 = \neg(d_1 >= c_1)) \land \\
  &    & (m_4 = c_1 + d_1) \land (m_5 = t_3) \land \\
  &    & (t_4 = (c_1 \& 3) <\!\!< d_1) \land \\
  &    & (x_6 = \mathit{ite}(\mathit{\mathit{guard}}_2, m_4, m_5)) \land \\
  &    & (t_5 = \mathit{ite}(\mathit{\mathit{guard}}_2, t_3, t_4)) \land \\
  &    & (m_7 = \mathit{ite}(\mathit{\mathit{guard}}_1, 0, m_6)) \land \\
  &    & (t_6 = \mathit{ite}(\mathit{\mathit{guard}}_1, 0, t_5)))
\end{array}$
\end{minipage}
\\
\hline 
\end{tabular} 
\caption{Path-based and monolithic symbolic execution}
\label{figure:simulation}
\end{figure}

%=======================================================================================
\section{Firmware Model in Hardware/Software Co-verification} 
%=======================================================================================
Figure~\ref{firmware} shows a fragment of the firmware model for the UART IP. 
The firmware implements linux style inb() and outb() functions to communicate 
with the hardware ports. The $wb$ class of functions communicate with the 
wishbone bus interface. The $set\_inputs()$ and the $next\_timeframe()$
functions are the primitives for \textsc{HW-CBMC} that direct the tool 
to set the inputs to the hardware signals and advance the clock signal 
respectively. In the monolithic software netlist model, this is implemented 
by actually invoking the top level function in the software netlist model. 
The top level function in software netlist corresponds to the top module 
of the UART IP core.

The firmware begins by resetting the UART IP which is followed by a $wb\_idle()$  
function. Then, the actual operation starts by setting the appropriate values to
the memory mapped registers which is propagated to the hardware modules.  
The firmware here sets the UART in loopback mode with interrupt enabled. We 
verify properites over the hardware firmware interactions. In particular, we 
verify whether the transmitted data is same as the received data in the loopback
mode. This is done by putting an assertion in the firmware model that checks the 
data from the transmitter and the receiver module.

\begin{figure*}
\scriptsize
\begin{tabular}{l|l}
\hline
Wishbone Interface & Firmware \\
\hline
\begin{lstlisting}[mathescape=true,language=C]
typedef unsigned char u8;
unsigned char inb 
 (unsigned long port) {
  return wb_read(port);
}
void outb (u8 value, 
 unsigned long port) {
  wb_write(port, value);
}
void wb_reset(void) {
 rtfSimpleUart.rst_i = 1;
 set_inputs();
 next_timeframe();
 rtfSimpleUart.rst_i = 0;
 rtfSimpleUart.stb_i = 0; 
 rtfSimpleUart.cyc_i = 0;
}
void wb_idle() {
 set_inputs();
 next_timeframe();
}
void wb_write(_u32 addr, 
             _u8 b) {
 rtfSimpleUart.adr_i = addr;
 rtfSimpleUart.dat_i = b;
 rtfSimpleUart.we_i = 1;
 rtfSimpleUart.cyc_i = 1;
 rtfSimpleUart.stb_i = 1;
 set_inputs();
 next_timeframe();
 rtfSimpleUart.we_i = 0;
 rtfSimpleUart.cyc_i = 0;
 rtfSimpleUart.stb_i = 0;
}
\end{lstlisting}
&
\begin{lstlisting}[mathescape=true,language=C]
int main() {
wb_reset();
wb_idle();
// Configure the uart
outb (0x13, UART_MC);  
outb (0x80, UART_CM3);
outb (0x00, UART_CM2);
outb (0x00, UART_CM1);
outb (0x00, UART_CR);  
outb (0x03, UART_IE); 
char tx_b[] = "Hello world";
_u8 istatus = 0;
char rx_b[100];
int i=0,c=0,d=0;
for (i=0; i<1990; i++){
if (rtfSimpleUart.irq_o){
 istatus=inb(UART_IS)&0x0c;
 if(istatus==0x0c){
 //it was a tx_empty interrupt
 outb(*(tx_b+c),UART_TR);
 c++;
 }
 else{//istatus==0x04
 //it was an rx_data interrupt
  rx_b[d] = inb(UART_TR);
  d++;
 }
}else {
 // no interrupt. 
 wb_idle();
 wb_idle();
 }
}
for(i=0; i<=10; i++)
 assert(rx_b[i] == tx_b[i]);
}
\end{lstlisting}
\\
\hline
\end{tabular}
\caption{Firmware model for UART IP}
\label{firmware} 
\end{figure*}

\newpage
%=======================================================================================
\section{\verifox: Tool Flow} 
%=======================================================================================
Figure~\ref{verifox} shows the overall tool flow for \verifox. Given a 
hardware desing in Verilog RTL and a property in System Verilog Assertion
language (SVA), the tool \emph{v2c} automatically generate the software netlist 
model in C following the synthesis semantics. Our experimental result shows that 
the proposed tool flow can be used for hardware property verification as well as 
co-verification in the peresence of a firmware. A monolithic model is generated in
C along with the firmware or a user-specified assumption which specify the 
partition constraint for state-space decomposition. The tool perform
property-driven slicing on the monolithic C program. The sliced program is then
passed to the symbolic execution engine. This engine explores the input 
sliced program in a depth-first manner with aggressive path pruning strategy. 
The generated path-constraints are encoded incrementally and passed to the
underlying solver only if it is feasible. \verifox either shows that the program 
is correct with respect to the given assertions or returns a counterexample
trace violating the property. The command line option to run verifox is shown
below:
\begin{lstlisting}[basicstyle=\scriptsize]
verifox-pi <C-file-name> // partial incremental mode with SAT
verifox-fi <C-file-name> // full incremental mode with SAT
\end{lstlisting}
\begin{figure*}

\tikzstyle{rblock}=[rounded corners,draw=black]
\tikzstyle{block}=[draw=black]
\centering
\begin{tikzpicture}

\node (v2c) [rblock] {\scs{\emph{v2c}}};
\node (snl) [block,below of=v2c] {\scs{Software-netlist}};
\draw[->] (v2c) -- (snl);

\node (HD) [above left=.3cm and .3cm of v2c] {\scs{\parbox{8em}{Hardware Design \\ (in Verilog)}}};
\draw[->] (HD) -- (v2c);

\node (prop) [above right=.3cm and .3cm of v2c] {\scs{\parbox{8em}{Property \\ (in SVA)}}};
\draw[->] (prop) -- (v2c);

\node (cmm) [block,below of=snl] {\scs{\parbox{9em}{Composite Monolithic Model}}};
\draw[->] (snl) -- (cmm);

\node (dcmm) [left=1cm of cmm] {};
\node (fw) [above=.1cm of dcmm  ] {\scs{Firmware}};
\node (as) [below=.1cm of dcmm] {\scs{Assumptions}};
\draw[->] (fw) -- (cmm);
\draw[->] (as) -- (cmm);

\node (pds) [block,below of=cmm] {\scs{\parbox{8em}{Property-driven slicing}}};
\draw[->] (cmm) -- (pds);

\node (tp) [block,below=.8cm of pds] {\scs{Paths Exploration}};
\node (iss) [block,below right=.5cm  and .05cm of tp.east] {\scs{\parbox{6em}{Incremental SAT solving}}};
\node (sat) [rblock,below=1.5cm of tp] {\scs{SAT solver}};
\node (ipp) [block,left=2cm of iss] {\scs{\parbox{6em}{Infeasible path pruning}}};

\draw [<->] (tp) -- (iss);
\draw [<->] (tp) -- (ipp);
\draw [<->] (sat) -- (iss);
\draw [<->] (sat) -- (ipp);

\node (vfbox) [rblock,fit={(tp) (iss) (sat) (ipp)}] {};
\draw[->] (pds) -- (vfbox);

\node (verifox) [right=.2cm of tp] {\scs{{\bf \verifox}}};

\node (safe) [above right=.2cm and .2cm of vfbox.east] {\scs{Verification Successful}};
\node (unsafe) [below right=.2cm and .2cm of vfbox.east] {\scs{\parbox{8em}{Verification Failed (Counterexample)}}};

\draw[->] (vfbox.9) -- (safe);
\draw[->] (vfbox.-12) -- (unsafe);

\end{tikzpicture}
\caption{\verifox tool flow \label{verifox}}
\end{figure*}

### 2017-04-01 paper.tex
source commit

\documentclass[format=acmsmall, review=false, screen=true]{acmart}

\usepackage{booktabs} % For formal tables

%\usepackage[ruled]{algorithm2e} % For algorithms
%\renewcommand{\algorithmcfname}{ALGORITHM}
%\SetAlFnt{\small}
%\SetAlCapFnt{\small}
%\SetAlCapNameFnt{\small}
%\SetAlCapHSkip{0pt}
%\IncMargin{-\parindent}

%\IEEEoverridecommandlockouts

\usepackage{colortbl}

\newcommand{\dkcmt}[1]{{\color{red} [{#1}]}}
\newcommand{\rmcmt}[1]{{\color{magenta} [{#1}]}}
\newcommand{\sjcmt}[1]{{\color{blue} [{#1}]}}
\newcommand{\tmcmt}[1]{{\color{orange} [{#1}]}}

\usepackage{tikz}
\usetikzlibrary{shapes,arrows,positioning,decorations.markings,chains,fit,shapes.multipart}
\usepackage{import}
\usepackage{times}
\usepackage{graphicx}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{mathptm}
\usepackage{rotating}
\usepackage{color}
\usepackage{listings}
\usepackage{verbatim}
\usepackage{comment}
\usepackage{alltt}
%\usepackage{subfigure}
\usepackage{mdwlist}
\usepackage{multirow}
\usepackage[algo2e,linesnumbered,ruled,lined]{algorithm2e}
\usepackage{url}
\makeatother

\newcommand{\tool}[1]{\textsc{#1}\xspace}
\newcommand{\symex}{\tool{path-symex}}
\newcommand{\ebmc}{\tool{ebmc}}
\newcommand{\hector}{\tool{hector}}
\newcommand{\slec}{\tool{slec}}
\newcommand{\symexv}{\tool{path-symex 5.0}}
\newcommand{\cbmcv}{\tool{cbmc}}
\newcommand{\cbmcver}{\tool{cbmc 5.2}}
\newcommand{\ebmcv}{\tool{ebmc 4.2}}
\newcommand{\hwcbmcv}{\tool{hw-cbmc}}
\newcommand{\hwcbmcver}{\tool{hw-cbmc 5.0}}
\newcommand{\acdcl}{\tool{acdcl}}
\newcommand{\summarizer}{\tool{summarizer 1.0}}
\newcommand{\abc}{\tool{ABC}}
\newcommand{\yosys}{\tool{Yosys 0.5}}
\newcommand{\verifoxver}{\tool{VerifOx 0.1}}
\newcommand{\verifox}{\tool{VerifOx}}
\newcommand{\iimc}{\tool{iimc}}
\newcommand{\klee}{\tool{klee}}
\newcommand{\symbiotic}{\tool{symbiotic}}
\newcommand{\kleever}{\tool{klee 1.0.0}}
\newcommand{\symbioticver}{\tool{symbiotic 3.0.1}}

\newcommand{\Omit}[1]{}
\newcommand{\scs}[1]{\scriptsize{#1}}

\input{symbols}
\input{refs}

\begin{document}

\title{Mining Scenario/Transaction Pairs HW/SW Co-verification Using Symbolic Execution}

\maketitle

%
%===============================================================================
\begin{abstract}
%===============================================================================
%
Time-to-market pressure requires early development of firmware and other
drivers for circuitry well before RTL is finished.  A key risk is divergence
of the hardware RTL from the behavior expected by the software.  Formal
methods can deliver proof that the RTL and the firmware match, but are
difficult to scale up.  We propose to identify partitions of the firmware and
the RTL that follow transaction boundaries by means of path-based symbolic
simulation with custom path-pruning.  We have implemented this approach in
our tool \verifox.  We have experimentally compared \verifox with a
conventional approach, which constructs a single monolithic SAT/SMT
instance, and observe speedups of an order of magnitude over conventional 
approach for proving safety properties as well as detecting firmware/hardware bugs.
%
\end{abstract}

%===============================================================================
\section{Introduction}
%===============================================================================
Hardware/software co-verification is broadly performed at two different
phases in the design cycle: pre-RTL and post-RTL.  In the pre-RTL phase,
engineers write high-level software (SW) models for Intellectual Property (IP), 
which are commonly known as {\em Transaction Level Model}s
(TLM)~\cite{codes14}.  TLMs are typically implemented using the SystemC TLM
library~\cite{tlm} or as plain C programs.  The goal of a TLM is to capture
enough functionality of the hardware (HW) such that it is possible to execute the
SW (drivers/firmware) against it.  Consequently, the TLMs are
incomplete, as they are designed to contain only those behaviors that are
observable by the SW (the drivers or firmware).  In particular, TLMs
are often not cycle-accurate.  These models are used to verify high-level
functionality of the system well before the RTL is
available~\cite{codes14,codes15}. Co-verification of the TLM and the
SW is typically performed by means of testing.

In the post-RTL phase, when the RTL design is available, hardware/software
co-verification becomes more complex.  Unlike the TLM, which only captures
limited design functionality, the RTL implements cycle-accurate behavior
of the final HW, and addresses concerns related to power, area and
timing.  Verification is mandatory to assert that the driver or firmware (FW) 
is executed correctly together with the RTL.  However, the verification of
FW given in C/C++ together with the RTL given in a hardware
description language (HDL) such as Verilog/VHDL is a challenging task due to
the timing and semantic mismatch between the two models -- for example,
FW running on a processor could be much faster than the HW
model it interacts with.  The effectiveness of testing is
thus severely limited in post-RTL co-verification.

Common practice in industry for system-level co-verification is to 
either use emulators/accelerators or Instruction Set Simulators (ISS). 
However, no rigorous formal verification effort is
performed at the post-RTL phase to ensure the validity of the
FW-HW interactions~\cite{vlsid13}.  With this aim in mind, the
primary contribution of this paper is to develop an automated and scalable
hardware/software co-verification methodology that detects FW-HW bugs in the 
presence of an RTL implementation.

Note that whenever we refer to ``hardware'' from this point onwards, we mean
an RTL implementation and not a TLM.  A firmware services the requests from
the application software layer or its interacting hardware components. 
Similarly, the hardware services the requests from the firmware or the
physical environment.  Thus, the firmware and its interacting hardware
components can be seen as a set of services.  In this paper, we call a
hardware RTL service a {\em Hardware Transaction} $(\mathcal{HT})$.  Closest
to our notion of $\mathcal{HT}$ is the micro-architecture-level transaction
by Mahajan et al.~\cite{mcbmq}.  We call a FW service a {\em Firmware
Transaction} ($\mathcal{FT}$).  $\mathcal{FT}$ is an untimed finite-state
machine that is manifested as control-flow paths in the FW, similar to
transactions in TLM~\cite{codes14}.  A~{\em scenario} $(\mathcal{S})$ in a
co-verification environment typically configures the hardware in a way that
restricts the interaction between $\mathcal{FT}$ and $\mathcal{HT}$.  In
other words, given a $\mathcal{S}$, the firmware only exercises a fragment
of the HW state-space.  This renders many interactions between
$\mathcal{HT}$ and $\mathcal{FT}$ infeasible.  A {\em Scenario/Transaction}
pair is a set of valid interactions between $\mathcal{HT}$ and
$\mathcal{FT}$ for a particular~$\mathcal{S}$.  Thus, it is necessary to
automatically mine Scenario/Transaction pairs to scale HW/SW co-verification
to SoC level designs.  A conventional, monolithic approach, e.g., an
approach based on BMC~\cite{CKY03}, cannot exploit this infeasibility.  The
key idea in this paper is to use path-based symbolic execution to
automatically infer such Scenario/Transaction pairs and check their validity
using backend solvers.

\Omit{
A system is comprised of a set of concurrent FW and HW transactions which
interleaves asynchronously. It is well recognized that concurrency is at
the heart of co-verification. The number of interleavings between the FW
and HW threads can be large, which can become a bottleneck in the
verification process. }

The concurrency between the HW and SW components is a key challenge in
co-verification.  In this paper, we exploit specific interaction patterns
between the FW and HW to reduce the number of interleavings.  We observe
that this interaction pattern follows a producer-consumer relationship --
the master module (producer) solely updates the shared registers which are
consumed by the slave (consumer).  This key observation allows us to
sequentialize a concurrent FW-HW model following specific interaction
patterns.

Generating a unified FW-HW model for co-verification is a well-known 
technique. Notably, Kurshan et al.~modeled HW and 
SW using finite state machines~\cite{fmsd02}, Monniaux in~\cite{emsoft07} modeled
HW and SW as C programs which are formally pushdown systems (PDS), 
Li et al.~in~\cite{fase10} used Buchi Automata to abstractly
model a hardware and PDS to abstractly model a software to generate a unified SW-HW model, 
called Buchi Pushdown System ({\em BPDS}). In this paper, we propose an 
orthogonal approach for co-verification.  
The HW RTL model in Verilog is automatically synthesized to a 
word-level cycle-accurate representation, called, 
{\em software netlist} $(\mathcal{SN})$, in ANSI-C~\cite{mtk2016}. 
The FW model is then instrumented with the call to the 
top level procedure of $\mathcal{SN}$ following specific FW-HW interaction 
patterns. Note that the top level procedure in $\mathcal{SN}$
is the same as the top level module in HW, since the 
synthesis step from RTL to $\mathcal{SN}$ preserves the 
RTL module hierarchy. This results in a unified single-threaded software model, 
that contains both FW and $\mathcal{SN}$ 
(synthesized hardware RTL). We call this 
unified FW-HW model, a {\em program netlist} (${\mathcal{PN}}$). 
This representation enables us to apply
broad range of verification techniques which have 
been less commonly explored in formal hardware/software 
co-verification based on netlists. In particular, we 
apply path-based symbolic execution and bounded model checking (BMC). 
In this paper, we present a path-based symbolic execution tool, 
\verifox, to uncover FW-HW design bugs in ${\mathcal{PN}}$. 
We compare our tool with the state-of-the-art BMC based 
co-verification tool, \hwcbmcv. Our experimental results show 
that path-based symbolic execution is order of magnitude 
faster than the BMC based approaches.

%===============================================================================
%\subsection{Contributions}
%===============================================================================
In this paper, we make the following contributions:
\begin{enumerate}
\item {\em Co-verification using Symbolic Execution:} 
In this paper, we introduce a notion of {\em transaction} 
in HW RTL and FW models. We present a unified FW-HW model, 
called {\em Program Netlist}, in C, for the co-verification task. 
To this end, we present a path-based symbolic execution algorithm that is 
able to automatically find scenario/transaction pairs from a 
program netlist and check their validity. 
To the best of our knowledge, this is the first attempt to 
perform path-based symbolic execution of 
C (FW) and Verilog RTL (HW) models by synthesizing 
them to a unified program netlist model.

\item {\em {\verifox} -- A tool for HW/SW co-verification:} We address the
co-verification problem at post-RTL phase and present a tool, \verifox, for
bounded HW/SW co-verification of IP level and SoC level design.  \verifox
supports IEEE 1364-2005 System Verilog standards and the C89, C99 standards. 
\verifox also supports SAT and SMT backends for constraint solving.  We
distribute the HW/SW co-verification tools, \hwcbmcv and \verifox, along
with hardware benchmarks in Verilog RTL and firmware C models
here~\footnote{https://drive.google.com/folderview?id=0BynC6sd-wTYgWVQ4bXNtRDB5a2c\&usp=sharing}. 
\end{enumerate}

\section{Scenarios and Transaction}
%\section{Preliminaries}
In this section, we start by presenting a running example of FW, followed
by some definitions and notations.\\    
%===============================================================================
\subsection{Running Example}
{\bf Running example: }
%===============================================================================
Figure~\ref{firmware} gives a fragment of a FW model for a Universal 
Asynchronous Transmitter/ Receiver (UART) IP.  The
$wb$ class of functions communicate with the {\em wishbone} bus interface to
set/reset the UART input ports and read/write data through the bus
interface.  The FW implements Linux style inb() and outb() functions which
invokes the $wb$ functions to communicate with the UART.  Due to space
limitation, we could not accommodate all $wb$ functions.  The FW begins by
resetting the UART IP which is followed by a $wb\_idle()$ function.  The 
FW then configures the UART in {\em loopback} mode using $outb$ function calls. 
Inside the loop, the firmware checks for a {\em transmitter} or {\em
receiver} interrupt by reading the Interrupt Status register $(UART\_IS)$. 
Depending on the type of interrupt, the firmware either receives a data packet 
or sends a data packet over the serial output. We verify that the transmitted 
data is the same as the received data in the {\em loopback} mode using an 
assertion in the firmware model. Note that $set\_inputs()$ and
$next\_timeframe()$ functions, used in $wb$ functions, are 
primitives in \textsc{HW-CBMC} that direct the tool to set the 
inputs to the HW signals and advance the HW clock, respectively.

\Omit{
The $set\_inputs()$ and the $next\_timeframe()$ functions are primitives
in \textsc{HW-CBMC} that direct the tool to set the inputs to the HW
signals and advance the HW clock, respectively.  Recall that $\mathcal{SN}$
is the synthesized word-level representation of HW RTL. In the unified
FW-HW model, $\mathcal{PN}$, these primitives are implemented by invoking
the top level module of $\mathcal{SN}$ which is the top module of the UART
RTL IP core.
}

\Omit{ 
In Figure~\ref{firmware}, the firmware executes scenario, $\mathcal{S}$, 
to configure the UART IP in {\em loopback} mode. A property $\psi$ can be as follows: \\
{\em If the content of memory mapped registers (mode configuration and interrupt 
enable) is, $UART\_MC = 0x13$ and $UART\_IE = 0x03$,  then the serial output of 
the transmitter, $UART\_TX$, should not be in high-impedance $(Z)$ state and 
the transmitter buffer must not be EMPTY.}  \\
Note that the antecedent of the property (configuring the UART in 
loopback with interrupt enabled) defines a scenario and the 
consequent defines the condition on the HW transaction. 
In this example, $\mathcal{T}$ \sjcmt{Where did
$\mathcal{T}$ come from?} is a finite-duration service 
through the UART state machine, $(UART\_TX and UART\_RX)$, that 
is spread over multiple clock cycles. 
}

\begin{figure}[t]
\scriptsize
\begin{tabular}{l|l}
\hline
Wishbone Interface & Main Module \\
\hline
\begin{lstlisting}[mathescape=true,language=C]
typedef unsigned char u8;
unsigned char inb 
 (unsigned long port) {
  return wb_read(port);
}
void outb (u8 value, 
 unsigned long port) {
  wb_write(port, value);
}
void wb_reset(void) {
 rst_i = 1;
 set_inputs();
 next_timeframe();
 rst_i = 0;
 stb_i = 0; 
 cyc_i = 0;
}
void wb_idle() {
 set_inputs();
 next_timeframe();
}
void wb_write(_u32 addr, 
     _u8 b) {
 adr_i = addr;
 dat_i = b;
 we_i = 1;
 cyc_i = 1;
 stb_i = 1;
 set_inputs();
 next_timeframe();
 we_i = 0;
 cyc_i = 0;
 stb_i = 0;
}
\end{lstlisting}
&
\begin{lstlisting}[mathescape=true,language=C]
int main() {
wb_reset();
wb_idle();
// Configure the uart
outb (0x13, UART_MC);  
outb (0x80, UART_CM3);
outb (0x00, UART_CM2);
outb (0x00, UART_CM1);
outb (0x00, UART_CR);  
outb (0x03, UART_IE); 
char tx_b[] = "Hello world";
_u8 status = 0;
char rx_b[100];
int i=0,c=0,d=0;
// data transfer in loopback
for (i=0; i<1990; i++){
if (irq_o){
 status=inb(UART_IS)&0x0c;
 if(istatus==0x0c){
 //it was a tx_empty interrupt
 outb(*(tx_b+c),UART_TR); c++;
 }
 else{ //status==0x04
 //it was an rx_data interrupt
  rx_b[d] = inb(UART_TR); d++;
 }
}else {
 // no interrupt. 
 wb_idle();
 wb_idle();
 }
}
// property
for(i=0; i<=10; i++)
 assert(rx_b[i] == tx_b[i]);
}
\end{lstlisting}
\\
\hline
\end{tabular}
\caption{Firmware model of UART IP}
\label{firmware} 
\end{figure}
%
\textbf{Scenario ($\mathcal{S}$):}
Let $B$ denote a set of all possible behaviors of a system. A scenario is a set of 
constraints $\mathcal{S}$ that restrict the system behaviors
to $B' \subseteq B$. For example, the left hand side of Figure~\ref{fig:st}. 
gives an example scenario for the UART FW shown in Figure~\ref{firmware}. 
Here, $\mathcal{S}$ configure the UART IP in {\em loopback} mode with 
interrupt enabled.

\Omit{ 
\textbf{Use case:}
A {\em Use case} is a set of scenarios that satisfy 
a particular goal. A use case completes successfully 
when that goal is satisfied. A complete set of use cases 
defines all the behaviors required of the system. For example, 
a use case in case of UART IP may be to transmit 
the data through the serial port. A scenario is an 
instance of a use case. 
}
%
\begin{figure}[t]
\scalebox{.55}{\import{figures/}{st.pspdftex}}
\caption{Scenario and Firmware Transaction
\label{fig:st}}
\end{figure}

\textbf{Firmware Transaction ($\mathcal{FT}$):} 
A Firmware Transaction ($\mathcal{FT}$) is an untimed state machine 
with a start state and an end state, which is similar to the notion of 
transactions in TLM~\cite{codes14}. 
Each transition in $\mathcal{FT}$ is guarded with a quantifier free predicates
over FW variables and HW signals.
If the guard evaluates to $TRUE$, it may perform some action, which may be 
read/write data. If the guard is not specified, it is assumed to be $TRUE$.
$\mathcal{FT}$ is often manifested as control-flow paths in the firmware. 
The right hand side of Figure~\ref{fig:st} gives a 
$\mathcal{FT}$ for the UART firmware code shown in Figure~\ref{firmware}. 
It has a start state and an end state. $\mathcal{FT}$ is triggered from 
UART output signal, $irq_o$. An execution of $\mathcal{FT}$, also called a 
FW transaction instance, takes a simple path from start state to end state. 
The path taken by an execution is determined by the state of 
the FW variables or its interacting HW signals. Repeated execution of 
$\mathcal{FT}$ can happen only in a sequential manner.

\textbf{Hardware Transaction ($\mathcal{HT}$):} 
Let us consider a HW RTL design with \textit{input} $\{I\}$, 
\textit{output} $\{O\}$, \textit{wires} $\{Wire\}$ and a set of 
state elements such as \textit{Registers} $\{Reg\}$, \textit{Memory}
$\{Mem\}$ ($Mem$ is a sequence of registers). Here, 
$\{I\} \subseteq \{Wire\}$, and $\{O\} \subseteq \{Reg\} \cup \{Wire\}$.
All state elements are fixed-width unsigned integers.

Let $\mathcal{G}$ be the set of quantifier free boolean predicates over 
state elements, $\{Reg\}$, $\{Mem\}$, $\{Wire\}$.  
A {\em transaction step}, $\varphi$, is defined by 2 tuple,
$\varphi \equiv \langle \Gamma_{\varphi}, \Delta_{\varphi} \rangle$, where 
$\Gamma_{\varphi} \equiv \{\alpha_1, \alpha_2, \ldots \alpha_{m}\}$
is a set of concurrent state updates to $\{Reg\}$, $\{Mem\}$, $\{Wire\}$ 
and $\Delta_{\varphi} \equiv \{\beta_1, \beta_2, \ldots \beta_{n}\} \subseteq
\mathcal{G}$.

A {\em Hardware Transaction} $(\mathcal{HT}) = (V, \Sigma, \rightarrow, init,
comp)$ is a labelled transition system, where $V$ is a set of transaction steps
$\varphi$ with a unique source vertex, $init \in V$, and a unique sink vertex, 
$comp \in V$, $\Sigma$ is a set of labels such that $\Sigma \subseteq 2^{G}$ and  
$\rightarrow \subseteq V \times \Sigma \times V$ is a set of labelled
transitions.

Each execution of $\mathcal{HT}$ is a non-empty 
sequence of transaction steps where each transaction step 
happens in a single clock. The first step is called {\em initiation event}
(\textit{init}). Assuming the duration of $\mathcal{HT}$ is finite, 
there must exist some distinguishable last completion event (\textit{comp}). 
%Operationally, an execution of $\mathcal{HT}$ begins at \textit{init}. 
After a transaction step $\varphi$ is executed, the set of concurrent state
update $\Gamma_{\varphi}$ is carried out and the value of boolean predicates
in $\Delta_{\varphi}$ is evaluated to determine the next step
$\varphi_{next}$, that is, a predicate $\beta_i \in \Delta_{\varphi}$
enables a transaction step.  This process continues until $\mathcal{HT}$
reaches \textit{comp} state.  Note that $\mathcal{FT}$ can update some state
elements of $\mathcal{HT}$ during its write action, based on which
predicates in $\Delta_{\varphi}$ may be computed. 
Figure~\ref{fig:interleaving2} gives a fragment of $\mathcal{HT}$
corresponding to the top module of UART IP.  Let us consider a possible
execution of $\mathcal{HT}$, $(init \rightarrow t_1 \rightarrow t_4
\rightarrow t_6 \rightarrow comp)$.  At $init$, the FW sets the HW input
signal, $(rst\_i==0)$, based on which the execution follows the edge to
$t_1$.  At $t_1$, the predicate, $cs$, is computed based on HW input
signals, $cyc\_i$, $stb\_i$, $adr\_i$ and $we\_i$.  Assuming that $cs\_i
\&\& we\_i$ holds true, the execution proceeds to step $t_4$ which computes
predicates based on the values in $adr\_i$.  The next step is determined by
the values of predicates, $'UART\_MC, 'UART\_IE, 'UART\_CT$.  Assuming that
$'UART\_MC$ holds true, the execution proceeds to $t_6$.  During the
execution of $t_6$, three parallel state update $(dtr\_no, rts\_no,
loopback)$ and two predicate evaluation ($\beta_1,\beta_2)$ is performed
based on the updates to state elements.  After $t_6$, the execution of
$\mathcal{HT}$ leads to $comp$ and the transaction finishes its execution. 
Note that the dotted edges in $\mathcal{HT}$ denotes that eventually the
execution reaches $comp$.  The update of state elements are shown in
rectangular boxes, whereas the evaluation of boolean predicates are shown
inside the rounded boxes.  The blue arrows point to the state updates or
predicate evaluation at a particular~$\varphi$.

\begin{figure}[t]
\scalebox{.55}{\import{figures/}{fw-hw-interleaving.pspdftex}}
\caption{Some HW Transactions for UART
\label{fig:interleaving2}}
\end{figure}

\textbf{Scenario/Transaction Pairs}
%
A scenario, $\mathcal{S}$, restricts the interaction between $\mathcal{HT}$
and $\mathcal{FT}$.  Similar to service-function based transaction in
TLM~\cite{hvc}, we view $\mathcal{FT}$ and $\mathcal{HT}$ as a set of
service in response to its interacting $\mathcal{HT}$ or $\mathcal{FT}$,
respectively.  A {\em Scenario/Transaction} pair is a set of valid
interactions between $\mathcal{HT}$ and $\mathcal{FT}$ for a
particular~$\mathcal{S}$.  For example, an UART IP contains a {\em
transmitter} and a {\em receiver} module.  Let us assume that a scenario,
$\mathcal{S}$, configure a UART in {\em transmission} mode.  Then the
interaction between $\mathcal{FT}$ and $\mathcal{HT}$ is constrained to
contain only those interactions that are relevant to the {\em transmitter}
module.  By contrast, the interactions with respect to the {\em receiver}
module is irrelevant for $\mathcal{S}$.  However, when $\mathcal{S}$
configures a UART in {\em loopback} mode, then the interaction between
$\mathcal{FT}$ and $\mathcal{HT}$ must contain transactions in {\em
transmitter} as well as {\em receiver} module.

This constrained interactions can be exploited 
to decompose the verification state-space. 
This requires an automatic technique for scenario driven 
partitioning of the FW-HW transactions to generate only 
relevant {\em Scenario/Transaction} pairs. Conventional 
approaches for co-verification construct a unified 
FW-HW model in FSM or BPDS that restrict such decomposition. 
In this paper, we built a unified FW-HW model in C program 
which enable us to automatically generate such {\em scenario/transaction} 
pairs using path-based symbolic execution techniques. The details 
of our technique are explained in the next section.
%
\Omit{
\textbf{Problem Statement}
Given a FW model in C, HW models in Verilog RTL, a property $\psi$ and 
a set of scenarios, the goal is to check whether $\psi$ holds under all 
scenarios in the combined FW-HW model. 
}
%
\section{Proposed Methodology}
Figure~\ref{proposed-flow} describes our overall tool framework. In the
subsequent section, we describe each step in details.

\begin{figure}[t]
%\centering
\scalebox{.48}{\import{figures/}{work-flow.pspdftex}}
\caption{Proposed HW/SW Co-verification Flow
\label{proposed-flow}}
\end{figure}

%\subsection{Software netlist}
{\bf Software netlist:}
The hardware circuits in Verilog RTL is automatically 
synthesized to a word level C program, called a 
\textit{software netlist}~\cite{mtk2016,mskm2016} using the 
tool {\em v2c}~\cite{mtk2016}. {\em v2c} follows synthesis semantics and not 
simulation semantics. The generated code is cycle-accurate as well as 
bit-precise. {\em v2c} automatically translates concurrent statements 
in Verilog such as procedural blocks and continuous assignments to 
a semantically equivalent C program.

A \textit{software netlist} $\mathcal{SN}$ is defined as follows:
\Omit{
a four-tuple $\langle L, A, l_0, l_e
\rangle$, where $L$ is a finite set of locations, modelling the values of
the program counter in the corresponding sequential code, $l_0 \in L$ is the initial
location, $l_e \in L$ is the error location, and $A \subseteq L \times M
\times L$ is the control flow automaton.  The edges in $A$ are labelled
with a quantifier-free first-order formula over program variables drawn from
the set $M$. These formulas encode an assignment and
take the form $\langle \mathit{In}, \mathit{Out},
\mathit{Seq}, \mathit{Comb}, \mathit{Asgn} \rangle$,
\sjcmt{$M$ is confusing. Is it a set of first order formula
or a set of $Asgn$?}
}
%
\[ 
\begin{array}[t]{@{}lll}
\mathcal{SN} & {:}{:}{=} & \mathit{Modules} \\
\mathit{Modules} & {:}{:}{=} & \epsilon \mid \mathit{moduleName(Var_1,\dots,Var_n)} \{ Asgn \} \;\; Modules \\
\mathit{Asgn} &  {:}{:}{=} & \mathit{CAsgn} \mid \mathit{SAsgn} | moduleName(Var_1,\dots,Var_n)\\
\mathit{CAsgn} & {:}{:}{=} & (V_c := Bv) \mid (V_c := \mathit{Bool}), \quad V_c \in \mathit{Comb} \uplus \mathit{Out} \\
\mathit{SAsgn} & {:}{:}{=} & (V_s := Bv) \mid (V_s := \mathit{Bool}), \quad V_s \in \mathit{Seq} \\
\mathit{Bv} &  {:}{:}{=} & bv_{const} \mid bv_{var} \mid
	\mathit{ITE}(Bool, Bv, Bv) \mid
bv_{op}(bv_1, \ldots, bv_n), \\
& & bv_i \in Bv, \\ 
& & bv_{op} \in \{n-\text{ary operators over bitvectors} \} \\
\mathit{Bool} & {:}{:}{=} & \mathit{true} \mid \mathit{false} \mid \neg{Bool} \mid Bool \land Bool \mid 
Bool \lor Bool \mid \\ 
& & Bv\; relop\; Bv, relop \in \{<,\leq,=,>,\geq\} \\
\end{array}
\]
%
Here, $\mathit{In}$, $\mathit{Out}$, $\mathit{Seq}$, $\mathit{Comb}$
are programs variables that model \emph{input}, \emph{output}, 
\emph{sequential/state-holding} and \emph{combinational/stateless} 
signals in the circuit.  $Asgn$ is a finite set of assignments 
to $Out$, $Seq$ and $Comb$.

\Omit{
A state transition in HW can be described by a set of register updates,
defined by the next-state function, and assignment of non-deterministic 
values to external inputs. The state transition in the software netlist 
corresponds to updates to the variables in $Seq$ and explicit assignment 
of non-deterministic values to the input variables, $In$.
}

%\subsection{Generating Unified FW-HW model}
\subsection{Analyzing FW/HW interaction Patterns}
%{\bf Analyzing FW/HW interaction pattern: }
The data dependencies between FW and HW is analyzed 
to reduce the number of interleavings between them and 
generate a unified FW-HW model. 
\Omit{
Recall that a HW transaction $(\mathcal{HT})$ is in response to a FW transaction 
$(\mathcal{FT})$. Similarly, $\mathcal{FT}$ is in response to the 
inputs from $\mathcal{HT}$ or operating system or application level software. 
The specific interaction pattern between $\mathcal{FT}$ 
and $\mathcal{HT}$ is exploited to generate a 
unified FW-HW model, $\mathcal{PN}$, in C. 
}
We observe that this interaction pattern follows 
producer-consumer relationship as shown in 
Figure~\ref{fig:interleaving1}. 
\Omit{
In practice, a FW thread 
is mostly independent of the HW thread they interact with~\cite{hvc}.  
Specifically, a FW thread is only responsible for configuring the 
HW transactions by writing to memory mapped registers 
or polling the interrupt status register for data transmission or 
receiving incoming data packets. 
}
We formally define the data dependencies between $\mathcal{FT}$ 
and $\mathcal{HT}$. A communicating pair of executions of 
$\mathcal{FT}$ and $\mathcal{HT}$ is an {\em interaction}, which 
takes place through shared variables (or shared registers)
only.

\Omit{
\textbf{Producer:} 
$\mathcal{FT}$ (or $\mathcal{HT}$) is called a {\em producer} 
if it produces a data ($d$) that is independent of $\mathcal{HT}$ (or $\mathcal{FT}$). 
Thus, the interleavings between $\mathcal{FT}$ and $\mathcal{HT}$ 
can be avoided to compute $d$. 
}

\textbf{Producer-consumer Interaction:}
%
An interaction is said to exhibit {\em producer-consumer}
interaction pattern if 1) the set of variables $V$ written by 
the execution of $\mathcal{FT}$ and and the set of variables 
$V'$ written by the execution of $\mathcal{HT}$ are disjoint 
($V \cap V' = \emptyset$), (2) and the executions 
of $\mathcal{FT}$ and $\mathcal{HT}$ consumes values 
in $V'$ and $V$, respectively.

\Omit{
shared register only FT is writing 
shared register that HT is writing 
and these two sets are disjoint
$\mathcal{FT}$ and $\mathcal{HT}$ is said to exhibit   
{\em producer-consumer} interaction pattern specific 
to data $d$ if $\mathcal{FT}$ produces $d$ and $\mathcal{HT}$ 
consumes $d$. Similarly, when $\mathcal{HT}$
is a producer of $d$ and $\mathcal{FT}$ is a consumer of $d$, 
$\mathcal{HT}$ and $\mathcal{FT}$ is said to exhibit   
{\em producer-consumer} interaction pattern specific to $d$. 
A producer-consumer interaction is defined with respect 
to the data produced. 
}

Figure~\ref{fig:interleaving1} illustrates the FW-HW interaction pattern 
for the UART IP. The FW CFG is shown in the left and the 
HW RTL code snippet is shown in the right. We abuse notations and 
represent $\mathcal{HT}$ in the form of RTL and $\mathcal{FT}$ as CFG
for our illustration purpose. Here, $\mathcal{HT}$ is the producer of interrupt 
status signal, $irq\_o$, which is read by $\mathcal{FT}$ in state $s_1$. 
The signal $irq\_o$ is  triggered when transmitter buffer is 
{\em EMPTY} or receiver buffer is {\em FULL}. 
$\mathcal{HT}$ also produces interrupt status by writing to the 
memory mapped register, $UART\_IS$, which is consumed by 
$\mathcal{FT}$ in state $s_2$.  In another interaction, $\mathcal{HT}$
sends a data-packet to $UART\_TR$ which is consumed by $\mathcal{FT}$ in state $s_7$.
Similarly, $\mathcal{FT}$ is the producer of $data$, $(outb(data,UART\_TR))$, 
in state $s_6$ which is consumed by $\mathcal{HT}$. These interaction patterns 
between $\mathcal{HT}$ and $\mathcal{FT}$ is exploited to generate a 
sequential unified {\em program netlist} model which is defined next.\\ \\
%
\begin{figure}[t]
\scalebox{.55}{\import{figures/}{interleaving.pspdftex}}
\caption{Producer Consumer Interactions Pattern
\label{fig:interleaving1}}
\end{figure}
%
{\bf Unified FW-HW model:}
A {\em program netlist} $\mathcal{PN}$ is a sequential unified
model of FW and HW. $\mathcal{PN}$ is formally defined as follows.
\[ 
\begin{array}[t]{@{}lll}
\mathcal{PN} & {:}{:}{=} & \mathit{Procedure} \\
\mathit{Procedure} & {:}{:}{=} & \mathit{Statement} \mid \mathit{Procedure} \\
\mathit{Statement} & {:}{:}{=} & CStatement \mid \mathit{moduleName(Var_1,\dots,Var_n)} \\
\mathit{CStatement} & {:}{:}{=} & x {:}{=} exp \mid \mathit{ITE}(b, s_1,s_2) \mid \mathit{s_1;s_2} \mid loop\{s\} \\ 
\end{array}
\]
Consider sets of expressions $Exp$ and Boolean expressions $BExp$ 
over variables $Var$ of $\mathcal{PN}$ such that $(exp \in Exp)$ and 
$(b \in BExp)$. A $\mathit{CStatement}$ is an assignment,
conditional, sequential concatenation or a loop.
$\mathit{moduleName(Var_1,\dots,Var_n)}$ invokes the top level 
procedure of the $\mathcal{SN}$. Recall that $\mathcal{SN}$ is a
software netlist representation of HW RTL models.
The interface variables $\{Var\_1,\dots,Var\_n\}$ 
(input, output and inout ports) are declared inside the 
FW to communicate with $\mathcal{SN}$. \\ 
\Omit{
$\mathcal{PN}$ is verification equivalent 
to the concurrent execution of FW and $\mathcal{SN}$.
}
\textbf{Property Driven Slicing of Program Netlist:}
A property-driven slicing is performed on the unified model, $\mathcal{PN}$.  
This step is purely syntactic, meaning that we perform a backward dependency 
analysis starting from the property which only preserve those 
program fragments that are relevant to a given property. The sliced program 
is then passed to the symbolic execution engine for path-based exploration. 
\Omit{
\section{Extracting relevant FW/HW interactions using}
Our unified FW-HW model, $\mathcal{PN}$, is composed of a set of 
FW scenarios, $\{\mathcal{S}\}$, and a set of HW transactions, $\{\mathcal{T}\}$ 
that $\{\mathcal{S}\}$ depends on. However, only a subset of $\{\mathcal{T}\}$ is 
relevant for a particular $\mathcal{S}_i \in \mathcal{S}$. In this section, 
we present a path-based exploration algorithm to automatically infer 
interacting $\mathcal{S}/\mathcal{T}$ pairs from $\mathcal{PN}$. 
}
%=======================================================================================
%\subsection{\verifox: Path-wise Symbolic Execution Tool} 
%=======================================================================================
%\Omit{
%\begin{figure}[tp]
%\centering
%\vspace*{0.3cm}
%\scalebox{.50}{\import{figures/}{work-flow.pspdftex}}
%\caption{Automated Slicing and Trace partitioning\label{fig:desc}}
%\end{figure}
%}
\Omit{
\begin{figure}[t]
\tikzstyle{rblock}=[rounded corners,draw=black]
\tikzstyle{block}=[draw=black]
\begin{tikzpicture}

\node (v2c) [rblock] {\scs{\emph{v2c}}};
\node (snl) [block,below of=v2c] {\scs{Software-netlist}};
\draw[->] (v2c) -- (snl);

\node (HD) [above left=.3cm and .3cm of v2c] {\scs{\parbox{8em}{Hardware Design \\ (in Verilog)}}};
\draw[->] (HD) -- (v2c);

\node (prop) [above right=.3cm and .3cm of v2c] {\scs{\parbox{8em}{Property \\ (in SVA)}}};
\draw[->] (prop) -- (v2c);

\node (cmm) [block,below of=snl] {\scs{\parbox{9em}{Composite Monolithic Model}}};
\draw[->] (snl) -- (cmm);

\node (dcmm) [left=1cm of cmm] {};
\node (fw) [above=.1cm of dcmm  ] {\scs{Firmware}};
\node (as) [below=.1cm of dcmm] {\scs{Assumptions}};
\draw[->] (fw) -- (cmm);
\draw[->] (as) -- (cmm);

\node (pds) [block,below of=cmm] {\scs{\parbox{8em}{Property-driven slicing}}};
\draw[->] (cmm) -- (pds);

\node (tp) [block,below=.8cm of pds] {\scs{Trace partitioning}};
\node (iss) [block,below right=.5cm  and .05cm of tp.east] {\scs{\parbox{6em}{Incremental SAT solving}}};
\node (sat) [rblock,below=1.5cm of tp] {\scs{SAT solver}};
\node (ipp) [block,left=2cm of iss] {\scs{\parbox{6em}{Infeasible path pruning}}};

\draw [<->] (tp) -- (iss);
\draw [<->] (tp) -- (ipp);
\draw [<->] (sat) -- (iss);
\draw [<->] (sat) -- (ipp);

\node (vfbox) [rblock,fit={(tp) (iss) (sat) (ipp)}] {};
\draw[->] (pds) -- (vfbox);

\node (verifox) [right=.2cm of tp] {\scs{{\bf \verifox}}};

\node (safe) [above right=.2cm and .2cm of vfbox.east] {\scs{Verification Successful}};
\node (unsafe) [below right=.2cm and .2cm of vfbox.east] {\scs{\parbox{8em}{Verification Failed (Counterexample)}}};

\draw[->] (vfbox.9) -- (safe);
\draw[->] (vfbox.-12) -- (unsafe);

\end{tikzpicture}
\caption{Automated Slicing and Trace partitioning\label{fig:desc}}
\end{figure}
}

\input{verifox}
\Omit{
\rmcmt{
The hardware and firmware run independently of each other. 
The communication between them takes place through interrupts. 
The interrupts are modelled by function calls. 
}
}
%
\section{The Conventional Approach to Co-verification}
%
\begin{figure}[t]
\begin{center}
\includegraphics[scale=0.6]{figures/traditional_flow.pdf}
\caption{Conventional HW/SW Co-verification Flow}
\label{fig:conventional}
\end{center}
\end{figure}

Figure~\ref{fig:conventional} illustrates the conventional approach to HW/SW
co-veri\-fi\-cation, as implemented in the state-of-the-art co-verification
tool, \hwcbmcv~\cite{CKY03,vlsid13}.  \hwcbmcv is the only open-source
formal co-verification tool that supports Verilog RTL (System Verilog 2009
standard) and C/C++ firmware.  In contrast to our proposed approach,
\hwcbmcv maintains two separate flows for HW and FW.  The top flow in
Figure~\ref{fig:conventional} uses synthesis to obtain either a bit-level or
a word-level netlist from Verilog RTL.  The bottom flow illustrates the
translation of the C program into static single assignment (SSA) form. 
These two flows meet only at the solver.  Thus, \hwcbmcv generates a
monolithic formula from the C and RTL description, which is then checked
with SAT/SMT solvers.  \hwcbmcv provides specific handshake primitives such
as $next\_timeframe()$ and $set\_inputs()$ to model FW-HW communications.
%
\Omit{
The hardware and firmware run independently of each other. 
The communication between them takes place through these function calls. 
}

%===============================================================================
\section{Experimental Results}
%===============================================================================

We report experimental results for FW-HW co-verification of a UART IP and a
SoC design.  All our experiments were performed on an Intel Xeon 3.07\,GHz
machine with 48\,GB RAM.  We use a state-of-the-art hardware/software
co-verification tool, \hwcbmcv, and compare it against \verifox. 
MiniSAT-2.2.0~\cite{DBLP:conf/sat/EenB05} was used as underlying SAT solver
with \verifoxver, CBMC-5.0~\cite{DBLP:conf/tacas/ClarkeKL04} and
\hwcbmcver~\cite{CK03}.  We also used other path-based symbolic execution
tools, such as, \kleever and \symbioticver for our experiments and presented
a comparison with \verifoxver.  All times reported are in seconds.  The
timeout for all our experiments was set to 2~hours.  The UART IP, SoC
benchmark (Verilog RTL and Firmware in C) and our co-verification
tools,\hwcbmcv and \verifox, are available for
download~\footnote{https://drive.google.com/folderview?id=0BynC6sd-wTYgWVQ4bXNtRDB5a2c\&usp=sharing}.

\Omit{
Even though \verifox supports SMT solvers such as
Z3~\cite{z32008} as backend solvers, the current implementation communicates
with these solvers using files rather than APIs.  Since a new solver
instance is generated for every query, incremental encoding cannot be used. 
Due to this, the runtimes of \verifox with SMT solvers on benchmarks are
significantly higher.  As the current implementation does not support
incremental encoding with SMT solvers, the runtimes would not provide a fair
comparison of \verifox with SMT versus \verifox with SAT solvers. 
Therefore, we are omitting the results obtained using SMT solvers.

All the benchmarks in
Verilog (excluding commercial ARM IP), software-netlist models in C,
firmware models, our tool \textsc{Verifox} and scripts for running \hwcbmcv,
\cbmc, \textsc{klee} and \textsc{Symbiotic} are available
here~\footnote{https://drive.google.com/file/d/0BynC6sd-wTYgSEU5eEswbnRqWUE/view?usp=sharing}
}

%-------------------------------------------------------------------------------
\subsection{FW-HW co-verification of UART}
%-------------------------------------------------------------------------------

\textbf{\emph{About UART:}} A UART IP core is used for asynchronous
transmission and reception of data which provides serial communication
capabilities with a modem or other external devices.  The UART IP is
compliant with industry standards for UART and interfaces with the wishbone
bus.  The core supports single transmission/reception format which is
1~start bit, 1~stop bit and 8~data bits without parity.  It also contains a
single transmit/receive buffer.  The UART IP implements a baud rate
generation circuit based on a harmonic frequency synthesizer that support a
wide variety of clock frequencies.  The UART IP core is implemented in
approximately 1000 lines of Verilog RTL, generating several thousand gates. 
The UART is obtained from~\url{http://www.opencores.org}.  A software
netlist model (in C) is synthesized from the UART RTL using \emph{v2c}.  The
software netlist model is approximately 1100 LOC.

\textbf{\emph{UART Configuration:}} The UART IP core is configured in
different operating modes, namely--{\em transmission without interrupt
enabled} (Scenario A), {\em transmission with interrupt enabled} (Scenario
B) and {\em loopback mode with interrupt enabled} (Scenario C).  The
data-width varies in each mode, ranging from 8~bits to 64~bits.  Scenario A
and Scenario B exercises only the transmitter module to transmit
non-deterministic data through the serial output.  The receiver module is
inactive in Scenario A and Scenario B.  By contrast, in Scenario C we
configure the UART in loopback mode with interrupt logic enabled.  Thus,
both the transmitter and the receiver are active in this mode.  The firmware
can receive interrupt from the transmitter or receiver module depending on
whether the transmitter buffer is empty or the receiver buffer is full
respectively, hence the control is non-deterministic in this mode.

\textbf{\emph{Discussion:}}
Table~\ref{table:safe} reports the run times for bounded safety proofs of
FW-HW interaction properties of the UART IP core.  Column~1 in
Table~\ref{table:safe} gives the name of the scenario -- transmission
without interrupt (transmit), transmission with interrupt (trans\_intr) and
loopback mode (loopback).  Column~2 gives the maximum loop bound in the
firmware.  Column~3~and~4 present the co-verification times using \hwcbmcv
at the bit-level and word-level.  Column~5,6,7~and~10 give the verification
times for the corresponding unified program netlist model using \cbmcv,
\klee, \textsc{symbiotic} and \verifox, respectively.  Column~8~and~9 report
the total/feasible path counts and the percentage of infeasible paths pruned
for each mode.  The focus of our experiment is to demonstrate the
scalability of path-based techniques over monolithic BMC instances for
effectively pruning infeasible FW-HW interactions with respect to a
scenario.  This is demonstrated by the \%-age of pruned paths (reported in
column~9) for each scenario.

\textbf{\emph{Safety properties:}}
We verify several properties of the FW-HW interactions of UART IP. 
In Scenario~A and scenario~B, we verified whether
the transmitted data (32-bit or 64-bit) is available through the serial
output port after a pre-determined number of clock cycles.
In both of the
configurations, \verifox is able to prune the receiver logic since the
FW only exercises the transmitter module by appropriately configuring
the memory-mapped registers.  In Scenario~C, we verified whether the transmitted
data matches the data received when the UART is configured in loopback
mode.\\ 
\textbf{\emph{Detecting UART bugs:}}
We found several bugs in the open source UART IP. 
The bug in the UART data-path is manifested in the transmission mode when no
interrupt is enabled.  The bug occurs when the transmitted data overlaps
with the start and stop bits resulting in incorrect bit pattern in the
serial output of the transmitter.  However, when the interrupt is enabled
during transmission mode, the bug in the control-path of the transmitter
module is triggered which deactivates the transmitter $empty$ signal.  This
illegally prevents any transmitter interrupt to occur even when the
transmitter buffer is empty, thereby violating the data transfer protocol. 
On the other hand, the control bug occurs in the loopback mode only when the
data is present at the receiver buffer but the $data\_present$ signal is
never asserted, as a result of which the receiver interrupt is never issued
in the FW. Thus, the transmitted data is not the same as the received
data in loopback mode leading to a control bug.

Table~\ref{table:safe} shows that path-based symbolic execution dominates
monolithic BMC in all scenarios (marked bold).  The average speedup for
proving safety properties is on average $21\times$ for \verifox over
\hwcbmcv.  \verifox also outperforms \klee for most configurations in
Scenario~A and Scenario~C.  In Scenario~B, \klee marginally wins over
\verifox by a fraction of a second.  \cbmcv performs poorly for most
scenarios, which is mostly attributed to higher loop bound ($>500$) in the
FW, thereby causing \cbmcv to get stuck in unwinding the program netlist
model.  The bottom part of Table~\ref{table:safe} reports the verification
times for detecting data-path and control-path bugs in UART IP.  The result
shows that \verifox is the fastest in detecting both the data-path and
control-flow bugs for all scenarios.  The average speedup for detecting bugs
is $48\times$ on average for \verifox over \hwcbmcv.

Note that both \klee and \verifox were run with the same configurations --
depth-first exploration strategy, eager infeasibility check, and incremental
solving.  \klee uses the STP theorem prover, whereas \verifox uses
MiniSAT~2.2.0 in the backend.

\Omit
{Besides SAT backend, \verifox also have a SMT backend. We ran our 
experiments with Z3 and observe higher verification times for Z3 compared 
to MiniSAT. So, we do not report the verification with SMT solvers.   }

\begin{table*}
\begin{center}
{
\begin{scriptsize}
\begin{tabular}{|l|l|l|l|l|l|l|l|l|l|}
\hline
  & Bound & \multicolumn{3}{c|}{Monolithic} & \multicolumn{5}{c|}{Path-based} \\ 
\cline{3-10}
 Scenario &  & \multicolumn{2}{c|}{HW-CBMC} & CBMC & Klee & Symbiotic & \multicolumn{3}{c|}{VerifOx} \\ 
\cline{3-10}
      &       &  Bit-level & Word-level & $\mathcal{PN}$ & $\mathcal{PN}$ & $\mathcal{PN}$ & Total/Feasible & \%-age & SAT \\
\cline{1-7}
      &       &   Time     &   Time      & Time  &  Time & Time & Paths & Pruning & Time \\
\cline{1-10}      
\multicolumn{10}{|c|}{non-deterministic data but deterministic control (Scenario A)} \\ \hline
transmit (32) & 250 & 15.02 & 15.78 & 108.25 & \textbf{0}.\textbf{98} & 29.36 & 247104/224 & 99.90 & 1.13 \\ 
transmit (64) & 500 & 23.87 & 23.29 & 206.89 & 1.68 & 29.90 & 247104/324 & 99.86 & \textbf{1}.\textbf{61}  \\ \hline 
\multicolumn{10}{|c|}{non-deterministic data and non-deterministic control
(Scenario B)} \\ \hline
trans\_intr (32) & 250 & 14.86 & 15.98 & 69.19 & \textbf{1}.\textbf{15} & 29.53 & 247104/295 & 99.88 & 1.49 \\
trans\_intr (64) & 500 & 24.14 & 26.42 & 117.73 & \textbf{1}.\textbf{27} & 29.58 & 247104/362 & 99.85 & 1.81 \\ \hline
\multicolumn{10}{|c|}{non-deterministic data and non-deterministic control
(scenario C)} \\ \hline
loopback (8)  & 230 & 52.06 & 55.71 & 1289.85 & 10.76 & 29.01 & 247104/354 & 99.85 & \textbf{3}.\textbf{95} \\ 
loopback (16) & 500 & 122.12 & 147.65 & 5410.18 & 32.24 & 29.04 & 247104/690 & 99.72 & \textbf{12}.\textbf{89} \\ 
loopback (32) & 650 & 170.62 & 192.35 & TO & 112.32 & 28.27 & 247104/1282 & 99.48 & \textbf{21}.\textbf{85}   \\ 
loopback (64) & 1300 & 409.71 & 445.66 & TO & 494.25 & 56.71 & 247104/2566 & 98.96 & \textbf{62}.\textbf{31}  \\ \hline
\multicolumn{10}{|c|}{detecting data-path bugs in transmission mode w/o interrupt} \\ \hline
transmit (64) & 520 & 28.43 & 28.14 & 186.99 & \textbf{0}.\textbf{96} & 26.67 &
247104/324 & 99.86 & 1.12 \\ \hline
\multicolumn{10}{|c|}{detecting control bugs with interrupt enabled} \\ \hline
transmit (64) & 520 & 31.35 & 29.70 & 113.57 & 1.18 & 27.13 & 247104/362 & 99.85 & \textbf{1}.\textbf{05} \\ \hline
\multicolumn{10}{|c|}{detecting control bugs in loopback mode} \\ \hline
loopback (64) & 1300 & 443.15 & 427.68 & TO & 492.59 & 54.23 & 247104/2566 &
98.96 & \textbf{62}.\textbf{34} \\ \hline
\end{tabular}
\end{scriptsize}
}
\end{center}
\vspace{-1.3mm}
\caption{Bounded safety proof times for HW/SW co-verification of UART 
\label{table:safe}}
\end{table*}

%-------------------------------------------------------------------------------
\subsection{FW-HW Co-verification of System-on-Chip}
%-------------------------------------------------------------------------------

\textbf{\emph{About the SoC:}}
%
We obtained an open source SoC design
from~\cite{DBLP:conf/fmcad/SubramanyanVRM15}.  It consists of an 8051
micro-controller, a memory arbiter, an external memory (XRAM) and
cryptographic accelerators.  The SoC is implemented in approximately~3000
lines of Verilog RTL, which generate several thousand gates.  The
accelerator implements encryption/decryption using the Advanced Encryption
Standard (AES) and is obtained
from~\href{http://www.opencores.org}{http://www.opencores.org}.  There is a
separate module that interfaces the AES to the 8051 micro-controller using a
memory-mapped I/O interface.  The micro-con\-tro\-ller communicates with the
accelerators and the XRAM by reading or writing to XRAM addresses.  The
arbitration of these module is done by the memory arbiter module.  We
synthesized the SoC to a software netlist (in C) using {\em v2c}.  The
generated model is bit-precise as well as cycle accurate.  The size of the
software netlist is approximately~3200 LOC.  The combinatorial exchanges
between the memory arbiter, XRAM and the AES module is modelled
appropriately in the software netlist.  \\

\textbf{\emph{About the firmware:}}
%
The firmware initiates the operation in the SoC by first writing to an
initial memory-mapped register.  The firmware implements Linux-style $inb()$
and $outb()$ functions calls, which are used to communicate with the HW
ports.  The firmware writes a sequence of non-deterministic data to the XRAM
port and then reads the data from the same port.  The cryptographic
accelerators use direct memory access to fetch the data from the external
memory.  The completion of the operation is determined by polling the
appropriate memory-mapped registers in the FW.

\begin{table*}
\begin{center}
{
\begin{scriptsize}
\begin{tabular}{|l|l|l|l|l|l|l|l|}
\hline
  & Bound & \multicolumn{3}{c|}{Monolithic} & \multicolumn{3}{c|}{Path-based} \\ 
\cline{3-8}
 Scenario &  & \multicolumn{2}{c|}{HW-CBMC} & CBMC & Klee & Symbiotic & VerifOx \\ 
\cline{3-8}
      &       &  Bit-level & Word-level & $\mathcal{PN}$ & $\mathcal{PN}$ & $\mathcal{PN}$ & $\mathcal{PN}$ \\
\cline{1-8}
      &       &   Time     &   Time      & Time  &  Time & Time & Time \\
\cline{1-8}      
\multicolumn{8}{|c|}{non-deterministic data and non-deterministic control (safe)} \\ \hline
data\_transfer & 20 & 86.92 & 86.23 & 104.25 & 25.98 & 29.36 &
\textbf{17}.\textbf{42} \\ 
\hline
\multicolumn{8}{|c|}{non-deterministic data and non-deterministic control
(unsafe)} \\ \hline
data\_transfer & 20 & 92.63 & 91.28 & 95.76 & 5.68 & 28.14 &
\textbf{1}.\textbf{27} \\ 
\hline
\end{tabular}
\end{scriptsize}
}
\end{center}
\vspace{-1.3mm}
\caption{Bounded safety proof times for HW/SW co-verification of a SoC 
\label{table:SoC}}
\end{table*}

\textbf{\emph{Discussion of the result:}}
%
Table~\ref{table:SoC} gives the runtimes for bounded safety proofs of 
FW-HW interaction properties of the SoC.  Column~1 in
Table~\ref{table:SoC} gives the name of the scenario -- transmission with
interrupt (data\_transfer).  Column~2 report the maximum loop bound in the
firmware.  Column~3~and~4 present the co-verification times using \hwcbmcv
at the bit-level and word-level.  Columns~[5-8] report the
verification times for the corresponding unified program netlist model using
\cbmcv, \klee, \textsc{symbiotic} and \verifox, respectively.

\textbf{\emph{Safety properties:}}
%
We verify several safety properties for the FW-HW interactions.  We check
whether the acknowledgment for data transmission and data reception arrives
from the micro-controller in the correct cycle.  We verify whether the
non-deterministic data transmitted through $outb()$ is the same
the data received through $inb()$.  We also verify that
reading/writing to the appropriate memory-mapped registers produce the
correct result during the data transmission phase.\\ \textbf{\emph{Detecting
SoC bugs:}} We found a control-path bug in the SoC design.  The bug is
manifested when memory arbiter hardware wrongly arbitrates the port
selection thereby forcing the write strobe for the external RAM to be LOW. 
This violates the data transfer protocol in the SoC design.

The result in Table~\ref{table:SoC} shows that \verifox is approximately
$5\times$ faster than \hwcbmcv and $6\times$ faster than \cbmcv for proving
safety.  For detecting bugs, the speedup is $72\times$ and $75\times$ for
\verifox over \hwcbmcv and \cbmcv.  However, \verifox marginally wins over
other path-based tools such as \symbiotic and \klee for safety proofs as
well as finding bugs. The result shows that the verification times for all
path-based techniques are comparable.  The reason for better scalability for
symbolic execution tools compared to \hwcbmcv is attributed to the path-based 
exploration strategy combined with eager path pruning and incremental SAT
solving. The FW exercises only the micro-controller
and transfer sequence of bytes to the XRAM port bypassing peripherals
connected to other ports such as hardware accelerator.  This scenario
allows path-based tools to prune the logic for accelerator which otherwise
could not have been removed by simple property-driven slicing of the
program netlist.  It is important to note that forward symbolic execution without
these optimizations timeout for all the benchmarks.

By contrast, \hwcbmcv is not able to prune the FW-HW transactions with
respect to a scenario due to monolithic BMC based approach.  Hence, \hwcbmcv
passes extremely complex formulas to the underlying solver, which often
contain irrelevant logic with respect to a particular scenario and are
therefore difficult to solve.

% ===============================================================================
\section{Related work}
% ===============================================================================

Previous work~\cite{codes14,codes15,fmcad13,memocode06} for 
co-verification have addressed the problem at the pre-RTL phase. 
However, we address the co-veri\-fi\-cation problem at the post-RTL
phase~\cite{fase10,vlsid13} where a key risk is divergence of the 
HW RTL from the behavior expected by the SW. In pre-RTL phase, 
there exists several notions of transaction, depending on the level 
of HW design granularity -- micro-architecture~\cite{mcbmq},
architecture~\cite{mcbmq}, TLM~\cite{tlm-book,hvc}. In this paper, 
we introduce a notion of transaction in RTL and FW models.

A system is comprised of a set of concurrent FW and HW models, which
interleave asynchronously.  However, we observe a specific interaction
pattern, which resembles a producer-consumer relationship.  We conjecture
that this producer-consumer interaction pattern is not specific to the UART
IP or SoC designs used as exemplars in this paper.  Malik et
al.~in~\cite{hvc} showed that these patterns are meaningful in further
settings -- a Linux device driver interacting with x86 QEMU emulator code or
a Rockbox firmware interacting with an iAudio X5 device.

The concept of symbolic execution~\cite{DBLP:journals/tse/Clarke76,
DBLP:conf/pldi/GodefroidKS05, DBLP:conf/osdi/CadarDE08} is prevalent in the
software domain for automated test generation as well as bug finding.  This
technique is different from the symbolic simulation techniques that are used
in the hardware domain.  In this paper, a unified program netlist
representation (in C) for FW-HW models enables us to apply symbolic
execution for scalable HW/SW co-verification.

%===============================================================================
\section{Concluding Remarks}
%===============================================================================

In this paper, we presented a novel HW/SW co-verification tool, \verifox,
for C-based FW and hardware models given in Verilog RTL.  We presented a
notion of transaction in joint RTL and FW models.  We showed that the
interaction pattern between FW and HW transactions can be exploited to
generate a unified program netlist model.  To this end, we presented a
path-based symbolic execution technique to automatically infer
scenario/transaction pairs from a program netlist.  Our general observation
is that monolithic BMC based approaches cannot exploit these interactions
and thus generate very complex formulas, which are difficult to solve. 
Owing to specific optimizations in \verifox such as eager path pruning
combined with incremental SAT solving, we experimentally show that \verifox
is an order of magnitude faster than the state-of-the-art HW/SW
co-verification tool, \hwcbmcv.  We demonstrate applicability of our
approach for proving safety as well as finding FW-HW bugs for a UART IP and
a SoC design.  In the future, we plan to extend our framework to FW-HW
models that exhibit further interaction patterns.

\bibliographystyle{ACM-Reference-Format}
\bibliography{biblio}

\end{document}

### 2017-04-01 verifox.tex
source commit

\subsection{Path-based Symbolic Execution}
We have developed a symbolic execution tool, \verifox, 
for FW-HW co-verification of IP level and SoC level designs. 
Given a program netlist model, $\mathcal{PN}$, a scenario, 
$\mathcal{S}$, and a property expressed as $\mathit{assert}(c)$ 
(where $c$ is a condition stated in terms of variables in $\mathcal{PN}$)
as input, \verifox performs path-based exploration of $\mathcal{PN}$ 
to automatically infer {\em scencario/transaction} pairs and check their validity 
using backend solvers. If the condition $c$ does not hold, 
then $\mathcal{PN}$ is said to have violated the property.

\Omit{
explores only those FW-HW interactions
that are relevant to $\mathcal{S}$. \verifox

\verifox takes a C program as an input, where 
the properties of interest are specified using 
statements in the code. Here, $c$ is a condition 
stated in terms of program variables that we 
want to hold at the point where the assertion occurs. 
}

\Omit{
 that performs 
path-based exploration of a unified FW-HW model, 
$\mathcal{PN}$ to automatically check the validity of the 
relevant {\em scencario/transaction} pairs of the FW-HW interactions.
}
\Omit {
\verifox performs depth-first exploration 
of program paths with aggressive pruning strategy  
with certain optimizations
that makes it suitable for verifying hardware designs. 
A hardware circuit having its 
behaviour specified in a manner similar to state machine, would usually
be translated into a program that has a large number of control-flow paths with
only tiny fractions of them being feasible. 
}
A typical path-based symbolic execution engine might explore 
a path until it come to an $\mathit{assert}(c)$ statement.
This whole path can then be posed as a query to a SAT solver to see if the 
assertion is violated at that point. If the path is infeasible, the assertion
holds trivially. If a large number of paths are infeasible, symbolic 
execution may waste time exploring them. \verifox employs 
an eager infeasibility check to prune infeasible paths, 
as well as incremental encoding that makes
it easier for the underlying SAT solver. 
\begin{algorithm2e}[t]
\DontPrintSemicolon
\SetKwFunction{symex}{Symex}
%\SetKwFunction{assert}{assert}
\SetKwFunction{put}{put}
\SetKwFunction{get}{get}
\SetKwFunction{print}{print}
\SetKwFunction{return}{return}
%\SetKwFunction{assume}{assume}
%\SetKwFunction{isf}{isFeasible}
\SetKwData{safe}{Safe}
\SetKwData{unsafe}{Unsafe}
\SetKwInOut{Input}{input}
\SetKwInOut{Output}{output}
\SetKw{KwNot}{not}
\begin{small}
\Input{Program Netlist $\mathcal{PN}$ with properties specified with $assert(c)$, scenario specified with $assume(c)$}
\Output{The status (\safe or \unsafe) and a counterexample if \unsafe}
\tcc{The initial state}
$S_0 \leftarrow I(x)$ \nllabel{algline:init}\;
$stmt \leftarrow $ first statement \;
$worklist.put(\tuple{S_0,stmt})$ \;
\While{\KwNot $worklist.empty()$}
{
	$\tuple{S,stmt} \leftarrow worklist.get()$ \;
	\uIf{$stmt$ is an $assume(c)$ \nllabel{algline:assume}}
           {
			$stmt \leftarrow $ statement after $assume(c)$ \;
			\lIf{$isFeasible(S\wedge c)$}{$worklist.put(\tuple{S\wedge c,stmt})$}

       		}
	\uElseIf{$stmt$ is a branch with condition $c$ \nllabel{algline:branch}}
	{
		$stmt_f \leftarrow$ first statement after $stmt$ if branch is not taken\;
		$stmt_t \leftarrow$ first statement after $stmt$ if branch is taken \;
		\lIf{$isFeasible(S\wedge c)$}{$worklist.put(\tuple{S\wedge c,stmt_t})$}
		\lIf{$isFeasible(S\wedge \neg c)$}{$worklist.put(\tuple{S\wedge \neg c,stmt_f})$}

	}
	\uElseIf{$stmt$ is an $assert(c)$ \nllabel{algline:assert}}
	{
		$stmt \leftarrow $ statement after $assert(c)$ \;
		\If{$isFeasible(S \wedge \neg c)$}{
		\print \unsafe \;
		\return Counterexample}
		\lElse{ $worklist.put(\tuple{S \wedge c,stmt})$}
	}
	\Else
	{
		$S \leftarrow symex(S,stmt)$\; \nllabel{algline:symex}
		$stmt \leftarrow $ the next statement in control flow after $stmt$ \;
		\lIf{$stmt \neq \bot$ \nllabel{algline:nullstmt}} {$worklist.put(\tuple{S,stmt})$} \;

	}
	\return \safe \;
}
\end{small}
\caption{Working of \textsc{verifox}\label{Alg:verifox}}
\end{algorithm2e}

\Omit{
, in which every time a branch or an assumption
is encountered, a feasibility check is made to prune away infeasible 
paths as early as possible. }
\vspace{-4mm}
\algref{verifox} shows the overall algorithm of \verifox. States mentioned
in the algorithm are all symbolic states, which are quantifier-free predicates characterizing
a set of program states. 
Symbolic execution starts with an initial symbolic state $I(x)$, is a quantifier-free predicate
over program variables $x$, and the first statement $\mathit{stmt}$ to be executed.  Note that we assume all program variables
have finite bit-width and thus can be represented as bit-vectors.
Every statement acts as a state transformer during the symbolic execution. $\mathit{worklist}$ 
maintains the set of symbolic states, along with the corresponding
$\mathit{stmt}$ that should execute next. Assumptions can be specified in the program 
using $\mathit{assume}(c)$ statements, where $c$ is the condition expressed in terms 
of program variables. Assumptions restrict the search to only those
states for which the condition $c$ holds at the program point where $\mathit{assume}(c)$ is encountered.
For example, suppose $(x!=0)$ characterizes the set of states that has been discovered to be
reachable so far by a verification tool. Here, $x$ is a program variable.
Upon encountering $\mathit{assume}(x>0)$, the 
set of states reachable at the point of assumption is shrunk to only those that
satisfy $(x>0)$. A user can specify assumptions to restrict
the verification to only certain regions of the program's state space.

\verifox performs a feasibility check at an $\mathit{assume}$ statement 
or a branch \algtwolines{algline:assume}{algline:branch} to ensure that
only feasible symbolic states are kept in the $\mathit{worklist}$. This ensures that the
infeasibility is detected as early as possible. 
If an assertion is violated, then a counterexample is detected and \algref{verifox}
terminates \algline{algline:assert}. In all other cases, $\mathit{symex}(S,\mathit{stmt})$ performs
one step of symbolic execution by executing $\mathit{stmt}$ from the symbolic state $S$ \algline{algline:symex}.
If no further statement remains to be executed along the path that is being explored,
then $\mathit{stmt}$ is assigned the value $\bot$. The symbolic state is put in the worklist only 
if there are further statements remaining \algline{algline:nullstmt}.

The feasibility checks shown as $\mathit{isFeasible}$ pose a query to the underlying SAT solver.
Note that \algref{verifox} does not refer to how the methods $\mathit{worklist.put}$ and $\mathit{worklist.get}$
work. In principle, one can use any search heuristic to select which symbolic state to explore 
further from the $\mathit{worklist}$. In the current version \verifox employs a depth first strategy of exploration.

Apart from the eager infeasibility check, another crucial optimization is the
use of incremental SAT solving during the symbolic execution. 
%\verifox can use incremental SAT-solving capabilities in two ways.
During the symbolic execution, only one solver instance is maintained 
while going down
a single path. Thus, when making a feasibility
check from one branch $b_1$ to another branch $b_2$ along a single path, only the program
segment from $b_1$ to $b_2$ is encoded as a constraint and added to the existing solver
instance. 
\Omit{
Internal solver states and the information that it gathers during the search
remains valid as long as all the queries that are posed to the solver in succession are
monotonically stronger. If the solver solves a formula $\phi$, posing $\phi \wedge \psi$ as 
a query to the same solver instance allows one to reuse the solver knowledge that
it has acquired in the previous query, because any assignment that falsifies $\phi$ also
falsifies $\phi \wedge \psi$. Thus the solver need not revisit the assignments that it has already
ruled out.}
This results in speeding up the process of feasibility check of the symbolic state at $b_2$ as
the feasibility check at $b_1$ was $\mathit{true}$. A new
solver instance is used to explore a different path, after the current path is detected as infeasible.

\Omit{
In the full incremental mode, only one solver instance is maintained throughout the whole
 symbolic execution. Let $\phi_{b_1b_2}$ denote the encoding of the path fragment
from $b_1$ to $b_2$. It is added in the solver as $(B_{b_1b_2} \implies \phi_{b_1b_2})$.
Then, $B_{b_1b_2}$ is added as a \textit{blocking variable}, which is also usually known as {\em solver assumption}.\footnote{The SAT community uses the term \textit{assumption variables} or \textit{assumptions}, but we will use the term blocking variable to avoid ambiguity with assumptions in the program.} to enforce constraints specified by $\phi_{b_1b_2}$. Blocking variables are treated specially inside the solvers: unlike regular variables or clauses, the blocking can be removed in subsequent queries without invalidating the solver instance.
When one wants to back-track the symbolic execution, the blocking $B_{b_1b_2}$ is removed 
and a unit clause $\neg B_{b_1b_2}$ is added to the solver, thus effectively removing $\phi_{b_1b_2}$.
}

Eager infeasibility check restrict the search to explore
only those FW/HW interations which are feasible under a
given scenario.
%Eager infeasibility check may save the engine from exploring multiple paths
%that emerge through branches encountered after the first point of infeasibility.
In our experiments, we find this optimization has a large effect on runtimes.
Though \verifox poses many queries to the SAT solver, each query is relatively simple due to
two reasons: the resultant formula encodes only a single path, 
and exploration along a path only needs to encode and solve for the path segment (along with the existing
constraints) from the last point of query.

### 2017-04-01 paper.tex
updated compiling with ACM class
intro

@@
-\documentclass[format=acmsmall, review=false, screen=true]{acmart}
+\documentclass[sigconf]{acmart}
 
@@
 
-\begin{document}
-
 \title{Mining Scenario/Transaction Pairs HW/SW Co-verification Using Symbolic Execution}
-
-\maketitle
-
-%
 %===============================================================================
@@
 
+\begin{document}
+\settopmatter{printacmref=false} % Removes citation information below abstract
+\renewcommand\footnotetextcopyrightpermission[1]{} % removes footnote with conference information in first column
+\pagestyle{plain} % removes running headers
+\setcopyright{none}
+
+\maketitle
+
+%
 %===============================================================================
@@
 
-Note that whenever we refer to ``hardware'' from this point onwards, we mean
-an RTL implementation and not a TLM.  A firmware services the requests from
-the application software layer or its interacting hardware components. 
+A firmware only exercise some fragment of hardware state-space in a typical hardware/software co-design~\cite{dac17,taa,ibm-other}.
+However, there is no automatic hardware/software co-verification tool that can exploit this interaction behavior.
+For building effective and scalable formal co-verification tool, it is therefore imperative to automatically mine only relevant scenario/transaction pairs that occurs in practical co-designs.
+In this paper, we attempt to bridge this gap by presenting a technique that automatically mine relevant HW/SW interaction behavior using symbolic execution.
+A firmware services the requests from
+the application software layer or its interacting hardware~\footnotesize{Note that whenever we refer to ``hardware'' from this point onwards, we mean
+an RTL implementation and not a TLM.}  components. 
 Similarly, the hardware services the requests from the firmware or the
@@
 transactions in TLM~\cite{codes14}.  A~{\em scenario} $(\mathcal{S})$ in a
-co-verification environment typically configures the hardware in a way that
+co-design typically configures the co-verification environment in a way that
 restricts the interaction between $\mathcal{FT}$ and $\mathcal{HT}$.  In
-other words, given a $\mathcal{S}$, the firmware only exercises a fragment
+other words, given a scenario $\mathcal{S}$, the FW only exercises a fragment
 of the HW state-space.  This renders many interactions between
-$\mathcal{HT}$ and $\mathcal{FT}$ infeasible.  A {\em Scenario/Transaction}
+$\mathcal{HT}$ and $\mathcal{FT}$ infeasible.
+For example, a scenario in \emph{Universal Asynchronous Receiver Transmitter} (UART) IP can configure the UART in \emph{transmitter} mode which restricts the communication between the FW and HW to set of services that only transfers data from the FW to the serial output port of the transmitter HW while completely bypassing the receiver HW.
+A {\em Scenario/Transaction}
 pair is a set of valid interactions between $\mathcal{HT}$ and
-$\mathcal{FT}$ for a particular~$\mathcal{S}$.  Thus, it is necessary to
-automatically mine Scenario/Transaction pairs to scale HW/SW co-verification
-to SoC level designs.  A conventional, monolithic approach, e.g., an
+$\mathcal{FT}$ for a particular scenario~$\mathcal{S}$.  
+It is necessary to automatically mine Scenario/Transaction pairs for scalable and effective co-verification.
+
+A conventional, monolithic approach, e.g., an
 approach based on BMC~\cite{CKY03}, cannot exploit this infeasibility.  The
@@
 \begin{enumerate}
+\item Translating Hardware/Software Co-designs to an unified 
+sequential software model, represented in C.  
+verification using Software Model Checkers.
 \item {\em Co-verification using Symbolic Execution:} 

### 2017-04-02 paper.tex
contribution

@@
 \newcommand{\verifoxver}{\tool{VerifOx 0.1}}
-\newcommand{\verifox}{\tool{VerifOx}}
+\newcommand{\verifox}{\tool{CoVeriIf}}
 \newcommand{\iimc}{\tool{iimc}}
@@
 
-A firmware only exercise some fragment of hardware state-space in a typical hardware/software co-design~\cite{dac17,taa,ibm-other}.
-However, there is no automatic hardware/software co-verification tool that can exploit this interaction behavior.
-For building effective and scalable formal co-verification tool, it is therefore imperative to automatically mine only relevant scenario/transaction pairs that occurs in practical co-designs.
-In this paper, we attempt to bridge this gap by presenting a technique that automatically mine relevant HW/SW interaction behavior using symbolic execution.
-A firmware services the requests from
-the application software layer or its interacting hardware~\footnotesize{Note that whenever we refer to ``hardware'' from this point onwards, we mean
-an RTL implementation and not a TLM.}  components. 
+A firmware only exercise some fragment of hardware state-space in a typical 
+hardware/software co-design~\cite{dac17,taa,ibm-other}.  However, there is no 
+automatic hardware/software co-verification tool that can exploit this interaction 
+behavior.  For building effective and scalable formal co-verification tool, it is 
+therefore imperative to automatically mine only relevant scenario/transaction pairs 
+that occurs in practical co-designs.  In this paper, we attempt to bridge this gap by 
+presenting a technique that automatically mine relevant HW/SW interaction behavior 
+using symbolic execution.  A firmware services the requests from
+the application software layer or its interacting hardware~\footnote{Note that whenever 
+we refer to ``hardware'' from this point onwards, we mean an RTL implementation 
+and not a TLM.}  components. 
 Similarly, the hardware services the requests from the firmware or the
@@
 \begin{enumerate}
-\item Translating Hardware/Software Co-designs to an unified 
-sequential software model, represented in C.  
-verification using Software Model Checkers.
-\item {\em Co-verification using Symbolic Execution:} 
-In this paper, we introduce a notion of {\em transaction} 
-in HW RTL and FW models. We present a unified FW-HW model, 
-called {\em Program Netlist}, in C, for the co-verification task. 
-To this end, we present a path-based symbolic execution algorithm that is 
-able to automatically find scenario/transaction pairs from a 
-program netlist and check their validity. 
-To the best of our knowledge, this is the first attempt to 
-perform path-based symbolic execution of 
-C (FW) and Verilog RTL (HW) models by synthesizing 
-them to a unified program netlist model.
-
-\item {\em {\verifox} -- A tool for HW/SW co-verification:} We address the
-co-verification problem at post-RTL phase and present a tool, \verifox, for
-bounded HW/SW co-verification of IP level and SoC level design.  \verifox
-supports IEEE 1364-2005 System Verilog standards and the C89, C99 standards. 
-\verifox also supports SAT and SMT backends for constraint solving.  We
-distribute the HW/SW co-verification tools, \hwcbmcv and \verifox, along
-with hardware benchmarks in Verilog RTL and firmware C models
+
+  \item We present two approaches for formal hardware/software co-verification
+    -- 1) A \emph{monolithic} approach that clearly separates the symbolic
+    execution of hardware and firmware model and generates a monolithic SAT
+    formula for verification, 2) A \emph{path-based} approach that constructs a
+    unified co-verification model by sequentializing the hardware and firmware
+    models and generates multiple SAT formulas through combined symbolic
+    execution of the unified model.
+
+  \item We present an automatic HW/SW co-verifcation tool called, \hwcbmcv,
+    which follows the monolithic verification technique.  Our path-based 
+    approach is implemented in a tool called, \verifox. Both tools can handle
+    co-designs where the hardware is implemented in Verilog RTL and firmware is  
+    specified in ANSI-C.  We distribute the HW/SW co-verification tools, \hwcbmcv and 
+    \verifox, along with our co-design benchmarks in Verilog RTL and C models
 here~\footnote{https://drive.google.com/folderview?id=0BynC6sd-wTYgWVQ4bXNtRDB5a2c\&usp=sharing}.
+
+  \item We show that the proposed path-based approach translates the HW/SW co-verification problem
+     into a purely software verification problem.  Our experiments show that the representation
+     of the sequentialized unified co-verification model in software languages allows us to 
+     mine relevant transaction/snecario pairs for effective co-verification.  To the 
+     best of our knowledge, this is the first attempt to synthesize a pure
+     software model for co-verification purpose.
+
+   \item We present an unified property specification language in \hwcbmcv and 
+     \verifox that allows designers to write meaningful formal co-specification 
+     over hardware and firmware events. We believe that the formal
+     co-specification model will significantly ease the adoption of formal tools 
+     for co-verification of industrial strength co-designs.
+
 \end{enumerate}
@@
 
+\Omit{
+\item {\em {\verifox} -- A tool for HW/SW co-verification:} We address the
+co-verification problem at post-RTL phase and present a tool, \verifox, for
+bounded HW/SW co-verification of IP level and SoC level design.  \verifox
+supports IEEE 1364-2005 System Verilog standards and the C89, C99 standards. 
+\verifox also supports SAT and SMT backends for constraint solving.  
+}
 \Omit{

### 2017-04-02 paper.tex
intro revise

@@
 %===============================================================================
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+ %                    Pre-RTL versus Post-RTL
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 Hardware/software co-verification is broadly performed at two different
@@
 timing.  Verification is mandatory to assert that the driver or firmware (FW) 
-is executed correctly together with the RTL.  However, the verification of
-FW given in C/C++ together with the RTL given in a hardware
+is executed correctly together with the RTL.  The effectiveness of testing 
+is thus severely limited in post-RTL co-verification.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+ %                    Challenges in Co-verification 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+However, the verification of FW given in C/C++ together with the RTL given in a hardware
 description language (HDL) such as Verilog/VHDL is a challenging task due to 
-the timing and semantic mismatch between the two models -- for example,
+few reasons -- 1) the timing and semantic mismatch between the synchronous
+clock-driven HW model and asynchronous event-driven SW model -- for example,
 FW running on a processor could be much faster than the HW
-model it interacts with.  The effectiveness of testing is
-thus severely limited in post-RTL co-verification.
-
-Common practice in industry for system-level co-verification is to 
-either use emulators/accelerators or Instruction Set Simulators (ISS). 
-However, no rigorous formal verification effort is
-performed at the post-RTL phase to ensure the validity of the
-FW-HW interactions~\cite{vlsid13}.  With this aim in mind, the
-primary contribution of this paper is to develop an automated and scalable
-hardware/software co-verification methodology that detects FW-HW bugs in the 
-presence of an RTL implementation.
-
+model it interacts with, 2) lack of co-specification model that precisely
+captures the design intent of the interaction behavior, 3) lack of automated
+formal tools that support co-designs that are mostly implemented in C and 
+Verilog/VHDL.   In this paper, we address some of these issues to facilitate 
+wider adoption of formal techniques in hardware/software co-verification.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+ %                     Handling Semantic Gap  
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Generating a unified FW-HW model~\cite{fmsd02,emsoft07,fase10} for 
+co-verification is a well-known phenomenon to handle the semantic mismatch 
+between the HW~\footnote{Note that whenever we refer to ``hardware'' from this point onwards, we mean an RTL implementation 
+and not a TLM.}  and FW models.  Most of the existing techniques are not 
+useful in practise for three reasons -- 1) use of abstract HW models 
+instead of register-transfer level implementation, 2) the HW-FW model
+construction is agnostic to the underlying reasoning engine, 3) does not
+leverage the co-specification model, hence ineffective for practical
+co-verification.  We will call the unified FW-HW model as \emph{co-verification model}.
+
+In this paper, we present two different approaches for automatic formal
+verification of HW/SW co-designs -- \emph{monolithic} and \emph{path-based}.  
+We embody these techniques in our tools, \hwcbmcv and \verifox, respectively. 
+A desirable characteristic of a co-verification model is the ability to exploit 
+the expressivity of the underlying reasoning engines, for example, constructing 
+a bit-level co-verification model for SAT solvers or a word-level model for SMT 
+solvers.  \hwcbmcv constructs a co-verification model through 
+in tandem symbolic execution of the HW and SW models.  To this end, a bit-level 
+netlist (typically represented as And Inverter Graph) or word-level netlist 
+(represented in tool specific format) is synthesized from a HW Register Transfer 
+Level (RTL) implementation. Similarly, the SW, given in C, is automatically 
+translated into a Static Single Assignment (SSA) form.  A monolithic verification 
+condition is generated from these two models which is then solved using a 
+satisfiability solver.  Whereas, a co-verification model in \verifox is constructed 
+by first translating the RTL description into a software representation in C followed 
+by sequentializing the hardware and firmware models.  This results in a single
+threaded sequential co-verification model which is represented in C. A path-wise 
+symbolic execution is then performed over the co-verification model to
+effectively mine only relevant interaction behaviors between the SW and HW
+models.
+
+%A key to building an effective co-verification tool is to translate the HW
+%and SW models to a common formal semantics called, 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+ %                     Co-specification Model  
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+A co-verification models must leverage the specification of system-level 
+properties across HW/SW boundaries for uncovering critical co-design bugs 
+and for effective co-verification.  Our co-specification models are 
+specified in C with the support of special primitive, called {\em next\_timeframe()}, 
+that can express temporal correlation between HW and FW events. Our
+co-verification models in \hwcbmcv and \verifox can be easily verified against 
+these co-specification models. The co-design properties expressed by 
+co-specification models are sufficiently expressive, amenable to 
+verification reuse and can be readily used in assertion-based verification.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+ %       Scenario, Transaction and Scenario/Transaction Pair
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 A firmware only exercise some fragment of hardware state-space in a typical 
-hardware/software co-design~\cite{dac17,taa,ibm-other}.  However, there is no 
-automatic hardware/software co-verification tool that can exploit this interaction 
-behavior.  For building effective and scalable formal co-verification tool, it is 
-therefore imperative to automatically mine only relevant scenario/transaction pairs 
-that occurs in practical co-designs.  In this paper, we attempt to bridge this gap by 
-presenting a technique that automatically mine relevant HW/SW interaction behavior 
-using symbolic execution.  A firmware services the requests from
-the application software layer or its interacting hardware~\footnote{Note that whenever 
-we refer to ``hardware'' from this point onwards, we mean an RTL implementation 
-and not a TLM.}  components. 
-Similarly, the hardware services the requests from the firmware or the
+hardware/software co-design~\cite{dac17,taa,ibm-other}.  
+A firmware services the requests from the application software 
+layer or its interacting hardware.  Similarly, the hardware services 
+the requests from the firmware or the
 physical environment.  Thus, the firmware and its interacting hardware
@@
 of the HW state-space.  This renders many interactions between
-$\mathcal{HT}$ and $\mathcal{FT}$ infeasible.
-For example, a scenario in \emph{Universal Asynchronous Receiver Transmitter} (UART) IP can configure the UART in \emph{transmitter} mode which restricts the communication between the FW and HW to set of services that only transfers data from the FW to the serial output port of the transmitter HW while completely bypassing the receiver HW.
-A {\em Scenario/Transaction}
-pair is a set of valid interactions between $\mathcal{HT}$ and
-$\mathcal{FT}$ for a particular scenario~$\mathcal{S}$.  
-It is necessary to automatically mine Scenario/Transaction pairs for scalable and effective co-verification.
-
-A conventional, monolithic approach, e.g., an
-approach based on BMC~\cite{CKY03}, cannot exploit this infeasibility.  The
-key idea in this paper is to use path-based symbolic execution to
-automatically infer such Scenario/Transaction pairs and check their validity
-using backend solvers.
+$\mathcal{HT}$ and $\mathcal{FT}$ infeasible. For example, a scenario in 
+\emph{Universal Asynchronous Receiver Transmitter} (UART) IP can configure the 
+UART in \emph{transmitter} mode which restricts the communication between the FW 
+and HW to set of services that only transfers data from the FW to the serial output 
+port of the transmitter HW while completely bypassing the receiver HW.  
+A {\em Scenario/Transaction} pair is a set of valid interactions between 
+$\mathcal{HT}$ and $\mathcal{FT}$ for a particular scenario~$\mathcal{S}$.  
+It is necessary to automatically mine Scenario/Transaction pairs for scalable 
+and effective co-verification.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+ %        Difference between Monolithic and Path-wise Approach
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+A monolithic approach in \hwcbmcv based on Bounded Model Checking~\cite{CKY03}, 
+cannot exploit this infeasibility.  Whereas, a path-based symbolic execution in 
+\verifox can automatically infer such Scenario/Transaction pairs and check their 
+validity using backend solvers.  For building effective and scalable formal 
+co-verification tool, it is therefore imperative to automatically mine only 
+relevant scenario/transaction pairs that occurs in practical co-designs.
 
@@
 and HW threads can be large, which can become a bottleneck in the
-verification process. }
+verification process.
 
@@
 patterns.
-
-Generating a unified FW-HW model for co-verification is a well-known 
-technique. Notably, Kurshan et al.~modeled HW and 
-SW using finite state machines~\cite{fmsd02}, Monniaux in~\cite{emsoft07} modeled
-HW and SW as C programs which are formally pushdown systems (PDS), 
-Li et al.~in~\cite{fase10} used Buchi Automata to abstractly
-model a hardware and PDS to abstractly model a software to generate a unified SW-HW model, 
-called Buchi Pushdown System ({\em BPDS}). In this paper, we propose an 
-orthogonal approach for co-verification.  
-The HW RTL model in Verilog is automatically synthesized to a 
-word-level cycle-accurate representation, called, 
-{\em software netlist} $(\mathcal{SN})$, in ANSI-C~\cite{mtk2016}. 
-The FW model is then instrumented with the call to the 
-top level procedure of $\mathcal{SN}$ following specific FW-HW interaction 
-patterns. Note that the top level procedure in $\mathcal{SN}$
-is the same as the top level module in HW, since the 
-synthesis step from RTL to $\mathcal{SN}$ preserves the 
-RTL module hierarchy. This results in a unified single-threaded software model, 
-that contains both FW and $\mathcal{SN}$ 
-(synthesized hardware RTL). We call this 
-unified FW-HW model, a {\em program netlist} (${\mathcal{PN}}$). 
-This representation enables us to apply
-broad range of verification techniques which have 
-been less commonly explored in formal hardware/software 
-co-verification based on netlists. In particular, we 
-apply path-based symbolic execution and bounded model checking (BMC). 
-In this paper, we present a path-based symbolic execution tool, 
-\verifox, to uncover FW-HW design bugs in ${\mathcal{PN}}$. 
-We compare our tool with the state-of-the-art BMC based 
-co-verification tool, \hwcbmcv. Our experimental results show 
-that path-based symbolic execution is order of magnitude 
-faster than the BMC based approaches.
+}
 
@@
 \end{enumerate}
-
-\section{Scenarios and Transaction}
-%\section{Preliminaries}
-In this section, we start by presenting a running example of FW, followed
-by some definitions and notations.\\    
+%
 %===============================================================================
-\subsection{Running Example}
-{\bf Running example: }
+\section{Working Example}
+%{\bf Running example: }
 %===============================================================================
-Figure~\ref{firmware} gives a fragment of a FW model for a Universal 
+In this section, we present an working example of FW and HW model to explain our 
+co-verification methodologies.
+
+\textbf{Firmware Model} Figure~\ref{firmware} gives a fragment of a FW model for a Universal 
 Asynchronous Transmitter/ Receiver (UART) IP.  The
@@
 interface.  The FW implements Linux style inb() and outb() functions which
-invokes the $wb$ functions to communicate with the UART.  Due to space
-limitation, we could not accommodate all $wb$ functions.  The FW begins by
-resetting the UART IP which is followed by a $wb\_idle()$ function.  The 
+invokes the $wb$ functions to communicate with the UART.  The FW begins 
+by resetting the UART IP which is followed by a $wb\_idle()$ function.  The 
 FW then configures the UART in {\em loopback} mode using $outb$ function calls. 
@@
 Depending on the type of interrupt, the firmware either receives a data packet 
-or sends a data packet over the serial output. We verify that the transmitted 
-data is the same as the received data in the {\em loopback} mode using an 
-assertion in the firmware model. Note that $set\_inputs()$ and
+or sends a data packet over the serial output.
+
+\rmcmt{The $set\_inputs()$ and
 $next\_timeframe()$ functions, used in $wb$ functions, are 
 primitives in \textsc{HW-CBMC} that direct the tool to set the 
-inputs to the HW signals and advance the HW clock, respectively.
-
-\Omit{
-The $set\_inputs()$ and the $next\_timeframe()$ functions are primitives
-in \textsc{HW-CBMC} that direct the tool to set the inputs to the HW
-signals and advance the HW clock, respectively.  Recall that $\mathcal{SN}$
-is the synthesized word-level representation of HW RTL. In the unified
-FW-HW model, $\mathcal{PN}$, these primitives are implemented by invoking
-the top level module of $\mathcal{SN}$ which is the top module of the UART
-RTL IP core.
-}
-
-\Omit{ 
-In Figure~\ref{firmware}, the firmware executes scenario, $\mathcal{S}$, 
-to configure the UART IP in {\em loopback} mode. A property $\psi$ can be as follows: \\
-{\em If the content of memory mapped registers (mode configuration and interrupt 
-enable) is, $UART\_MC = 0x13$ and $UART\_IE = 0x03$,  then the serial output of 
-the transmitter, $UART\_TX$, should not be in high-impedance $(Z)$ state and 
-the transmitter buffer must not be EMPTY.}  \\
-Note that the antecedent of the property (configuring the UART in 
-loopback with interrupt enabled) defines a scenario and the 
-consequent defines the condition on the HW transaction. 
-In this example, $\mathcal{T}$ \sjcmt{Where did
-$\mathcal{T}$ come from?} is a finite-duration service 
-through the UART state machine, $(UART\_TX and UART\_RX)$, that 
-is spread over multiple clock cycles. 
-}
-
+inputs to the HW signals and advance the HW clock, respectively.}
+
+\textbf{Hardware Model} Figure~\ref{fig:interleaving2} shows a fragment of the state machine 
+implementation of the UART hardware RTL.  The UART IP contains a
+\emph{transmitter} module, a \emph{receiver} module and a \emph{clock
+generator}.  The update of state elements (\emph{registers}) and 
+\emph{wires} are shown in rectangular boxes and rounded boxes respectively.
+
+\textbf{Co-specification Model} We verify that the transmitted data is the same as the 
+received data in the {\em loopback} mode.  To do so, we annotate the FW model 
+with an assertion $assert()$, as shown in Figure~\ref{firmware}.  Note that the 
+array containers $rx\_b$ and $tx\_b$ stores the data obtained through the $inb$
+and $outb$ function calls which directly reads and writes the UART IP ports
+respectively. 
+\[
+  for(i=0; i<=N; i++) 
+   \quad assert(rx\_b[i] == tx\_b[i]);
+\]
+%
+We formally describe the notion of \emph{transaction} and \emph{scenario} with the
+help of our working example. \\
+%
 \begin{figure}[t]
@@
 constraints $\mathcal{S}$ that restrict the system behaviors
-to $B' \subseteq B$. For example, the left hand side of Figure~\ref{fig:st}. 
+to $B' \subseteq B$. For example, the left hand side of Figure~\ref{fig:st} 
 gives an example scenario for the UART FW shown in Figure~\ref{firmware}. 
@@
 predicates in $\Delta_{\varphi}$ may be computed.
-Figure~\ref{fig:interleaving2} gives a fragment of $\mathcal{HT}$
+
+Figure~\ref{fig:interleaving2} shows a fragment of $\mathcal{HT}$
 corresponding to the top module of UART IP.  Let us consider a possible
@@
 inside the rounded boxes.  The blue arrows point to the state updates or
-predicate evaluation at a particular~$\varphi$.
-
+predicate evaluation at a particular~$\varphi$. \\
+%
 \begin{figure}[t]
@@
 \end{figure}
-
+%
 \textbf{Scenario/Transaction Pairs}
@@
 
-This constrained interactions can be exploited 
+\rmcmt{This constrained interactions can be exploited 
 to decompose the verification state-space. 
@@
 pairs using path-based symbolic execution techniques. The details 
-of our technique are explained in the next section.
+of our technique are explained in the next section.}
 %
@@
 \section{Proposed Methodology}
+
+\subsection{Monolithic Co-verification Approach}
+
+\subsection{Path-based Co-verification Approach}
+%
 Figure~\ref{proposed-flow} describes our overall tool framework. In the
@@
 %
-{\bf Unified FW-HW model:}
+{\bf Unified Co-verification model:}
 A {\em program netlist} $\mathcal{PN}$ is a sequential unified
@@
 
+Generating a unified FW-HW model for co-verification is a well-known 
+technique. Notably, Kurshan et al.~modeled HW and 
+SW using finite state machines~\cite{fmsd02}, Monniaux in~\cite{emsoft07} modeled
+HW and SW as C programs which are formally pushdown systems (PDS), 
+Li et al.~in~\cite{fase10} used Buchi Automata to abstractly
+model a hardware and PDS to abstractly model a software to generate a unified SW-HW model, 
+called Buchi Pushdown System ({\em BPDS}).
+
 A system is comprised of a set of concurrent FW and HW models, which
@@
 
+Common practice in industry for system-level co-verification is to 
+either use emulators/accelerators or Instruction Set Simulators 
+(ISS)~\cite{coverif-book}.  However, no rigorous formal verification 
+effort is performed at the post-RTL phase to ensure the validity of the
+FW-HW interactions.
+
 The concept of symbolic execution~\cite{DBLP:journals/tse/Clarke76,
@@
 technique is different from the symbolic simulation techniques that are used
-in the hardware domain.  In this paper, a unified program netlist
-representation (in C) for FW-HW models enables us to apply symbolic
-execution for scalable HW/SW co-verification.
+in the hardware domain.  In this paper, we apply path-wise symbolic execution
+to mine relevant scenario/transaction pairs for effective co-verification of 
+a unified co-verification model.
 

### 2017-04-03 paper.tex
Approach 1 description complete

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
 Hardware/software co-verification is broadly performed at two different
-phases in the design cycle: pre-RTL and post-RTL.  In the pre-RTL phase,
+phases in the design cycle: pre-Register Transfer Level (pre-RTL) and 
+post-RTL.  In the pre-RTL phase,
 engineers write high-level software (SW) models for Intellectual Property (IP), 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-However, the verification of FW given in C/C++ together with the RTL given in a hardware
+The verification of FW given in C/C++ together with the RTL given in a hardware
 description language (HDL) such as Verilog/VHDL is a challenging task due to 
@@
 model it interacts with, 2) lack of co-specification model that precisely
-captures the design intent of the interaction behavior, 3) lack of automated
-formal tools that support co-designs that are mostly implemented in C and 
-Verilog/VHDL.   In this paper, we address some of these issues to facilitate 
-wider adoption of formal techniques in hardware/software co-verification.
+captures the design intent of the communication between HW and FW, 3) lack 
+of automated formal tools that support co-designs implemented in C/C++ and 
+Verilog/VHDL.   In this paper, we address some of these challenges to enable
+seamless adoption of formal techniques in hardware/software co-verification.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Generating a unified FW-HW model~\cite{fmsd02,emsoft07,fase10} for 
-co-verification is a well-known phenomenon to handle the semantic mismatch 
-between the HW~\footnote{Note that whenever we refer to ``hardware'' from this point onwards, we mean an RTL implementation 
-and not a TLM.}  and FW models.  Most of the existing techniques are not 
+Generating a unified FW-HW model for co-verification is a 
+well-known phenomenon to handle the semantic mismatch between the 
+HW~\footnote{Note that whenever we refer to ``hardware'' 
+from this point onwards, we mean an RTL implementation 
+and not a TLM.}  and FW models.  Most of the existing techniques 
+in~\cite{fmsd02,emsoft07,fase10} for constructing a unified FW-HW model are not 
 useful in practise for three reasons -- 1) use of abstract HW models 
@@
 a bit-level co-verification model for SAT solvers or a word-level model for SMT 
-solvers.  \hwcbmcv constructs a co-verification model through 
-in tandem symbolic execution of the HW and SW models.  To this end, a bit-level 
-netlist (typically represented as And Inverter Graph) or word-level netlist 
-(represented in tool specific format) is synthesized from a HW Register Transfer 
+solvers.  To this end, \hwcbmcv constructs a co-verification model through 
+in tandem symbolic execution of the HW and FW models.  A bit-level 
+netlist representation in And Inverter Graph (AIG) format or word-level netlist in
+format similar to SMT-LIB standards is synthesized from a HW Register Transfer 
 Level (RTL) implementation. Similarly, the SW, given in C, is automatically 
@@
 symbolic execution is then performed over the co-verification model to
-effectively mine only relevant interaction behaviors between the SW and HW
-models.
+automatically mine relevant interaction behaviors between the FW and HW models.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-A co-verification models must leverage the specification of system-level 
+A co-verification models must enable the specification of system-level 
 properties across HW/SW boundaries for uncovering critical co-design bugs 
@@
 specified in C with the support of special primitive, called {\em next\_timeframe()}, 
-that can express temporal correlation between HW and FW events. Our
+that can express temporal correlation between HW and FW events. The
 co-verification models in \hwcbmcv and \verifox can be easily verified against 
-these co-specification models. The co-design properties expressed by 
+the co-specification models.  The co-design properties expressed by 
 co-specification models are sufficiently expressive, amenable to 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-A monolithic approach in \hwcbmcv based on Bounded Model Checking~\cite{CKY03}, 
-cannot exploit this infeasibility.  Whereas, a path-based symbolic execution in 
+A monolithic approach in \hwcbmcv is based on Bounded Model Checking~\cite{CKY03}, 
+hence it cannot exploit the infeasibility arising from scenario driven constrained 
+interaction behaviors.  Whereas, a path-based symbolic execution in 
 \verifox can automatically infer such Scenario/Transaction pairs and check their 
-validity using backend solvers.  For building effective and scalable formal 
-co-verification tool, it is therefore imperative to automatically mine only 
-relevant scenario/transaction pairs that occurs in practical co-designs.
+validity using backend solvers.  We experimentally show that for building 
+effective and scalable formal co-verification tool, it is imperative to 
+automatically mine only relevant scenario/transaction pairs that occurs in 
+practical co-design environment.
 
@@
 
-\subsection{Monolithic Co-verification Approach}
-
-\subsection{Path-based Co-verification Approach}
+\subsection{Approach 1: Path-based Co-verification Technique}
 %
 Figure~\ref{proposed-flow} describes our overall tool framework. In the
-subsequent section, we describe each step in details.
-
+subsequent section, we describe each step in details.\\ 
+%
 \begin{figure}[t]
@@
 \end{figure}
-
-%\subsection{Software netlist}
-{\bf Software netlist:}
-The hardware circuits in Verilog RTL is automatically 
-synthesized to a word level C program, called a 
-\textit{software netlist}~\cite{mtk2016,mskm2016} using the 
-tool {\em v2c}~\cite{mtk2016}. {\em v2c} follows synthesis semantics and not 
-simulation semantics. The generated code is cycle-accurate as well as 
-bit-precise. {\em v2c} automatically translates concurrent statements 
-in Verilog such as procedural blocks and continuous assignments to 
-a semantically equivalent C program.
-
+%
+\textbf{Step 1: RTL to Software}
+A hardware circuit in Verilog RTL is automatically 
+translated into a word level C program, called a 
+\textit{software netlist}~\cite{mtk2016,mskm2016,mkm2015} following synthesis 
+semantics. The software netlist model is cycle-accurate as well as 
+bit-precise~\footnote{http://www.cprover.org/hardware/v2c/}. The 
+translation automatically handles concurrent statements 
+in Verilog such as procedural blocks and continuous assignments, multiple always
+blocks, multiple modules and translates them into an equivalent C program.  This
+is a radically new but promising approach for synthesizing software 
+models from RTL description, mainly targeted for word-level formal hardware 
+verification using software verification techniques such as abstract 
+satisfaction~\cite{leo-thesis}.  To the best of our knowledge, this is the first 
+attempt that demonstrate the efficacy of such translation in the context of 
+hardware/software co-verification. 
+% 
 A \textit{software netlist} $\mathcal{SN}$ is defined as follows:
-\Omit{
-a four-tuple $\langle L, A, l_0, l_e
-\rangle$, where $L$ is a finite set of locations, modelling the values of
-the program counter in the corresponding sequential code, $l_0 \in L$ is the initial
-location, $l_e \in L$ is the error location, and $A \subseteq L \times M
-\times L$ is the control flow automaton.  The edges in $A$ are labelled
-with a quantifier-free first-order formula over program variables drawn from
-the set $M$. These formulas encode an assignment and
-take the form $\langle \mathit{In}, \mathit{Out},
-\mathit{Seq}, \mathit{Comb}, \mathit{Asgn} \rangle$,
-\sjcmt{$M$ is confusing. Is it a set of first order formula
-or a set of $Asgn$?}
-}
 %
@@
 to $Out$, $Seq$ and $Comb$. 
-
-\Omit{
-A state transition in HW can be described by a set of register updates,
-defined by the next-state function, and assignment of non-deterministic 
-values to external inputs. The state transition in the software netlist 
-corresponds to updates to the variables in $Seq$ and explicit assignment 
-of non-deterministic values to the input variables, $In$.
-}
-
-%\subsection{Generating Unified FW-HW model}
-\subsection{Analyzing FW/HW interaction Patterns}
-%{\bf Analyzing FW/HW interaction pattern: }
-The data dependencies between FW and HW is analyzed 
-to reduce the number of interleavings between them and 
-generate a unified FW-HW model. 
-\Omit{
-Recall that a HW transaction $(\mathcal{HT})$ is in response to a FW transaction 
-$(\mathcal{FT})$. Similarly, $\mathcal{FT}$ is in response to the 
-inputs from $\mathcal{HT}$ or operating system or application level software. 
-The specific interaction pattern between $\mathcal{FT}$ 
-and $\mathcal{HT}$ is exploited to generate a 
-unified FW-HW model, $\mathcal{PN}$, in C. 
-}
-We observe that this interaction pattern follows 
-producer-consumer relationship as shown in 
+%
+\textbf{Step 2: Constructing Co-verification Model}
+An unified co-verification model is constructed by sequentializing 
+HW and its interacting FW threads, thereby generating a sequential 
+single-threaded co-verification model in C.  The motivation behind
+sequentialization is based on our observation that practical industrial
+co-designs exhibit producer-consumer interaction behavior.  We observe 
+that in practise, a FW thread is mostly independent of the HW thread they interact 
+with~\cite{hvc,codes14}.  This behavior is also prevelant in industrial co-designs, 
+such as IBM Text Accelerator co-design~\cite{polig2014micro,polig2014fpl}
+and IBM coherent FFT coprocessor~\cite{giefers2015accelerating}.
+Specifically, a FW thread is only responsible for configuring the 
+HW transactions by writing to memory mapped registers or polling 
+the interrupt status register for data transmission or receiving 
+incoming data packets. This interaction pattern exhibits producer-consumer 
+relationship, which is also evident in case of our UART example in 
 Figure~\ref{fig:interleaving1}.  
-\Omit{
-In practice, a FW thread 
-is mostly independent of the HW thread they interact with~\cite{hvc}.  
-Specifically, a FW thread is only responsible for configuring the 
-HW transactions by writing to memory mapped registers 
-or polling the interrupt status register for data transmission or 
-receiving incoming data packets. 
-}
-We formally define the data dependencies between $\mathcal{FT}$ 
-and $\mathcal{HT}$. A communicating pair of executions of 
+%
+We formally define a single-threaded sequential unified co-verification model, 
+denoted by $\mathcal{M}_{seq}$. 
+\[ 
+\begin{array}[t]{@{}lll}
+  \mathcal{M}_{seq} & {:}{:}{=} & \mathit{Procedure} \\
+\mathit{Procedure} & {:}{:}{=} & \mathit{Statement} \mid \mathit{Procedure} \\
+\mathit{Statement} & {:}{:}{=} & CStatement \mid \mathit{moduleName(Var_1,\dots,Var_n)} \\
+\mathit{CStatement} & {:}{:}{=} & x {:}{=} exp \mid \mathit{ITE}(b, s_1,s_2) \mid \mathit{s_1;s_2} \mid loop\{s\} \\ 
+\end{array}
+\]
+%
+Consider sets of expressions $Exp$ and Boolean expressions $BExp$ 
+over variables $Var$ of $\mathcal{M}_{seq}$ such that $(exp \in Exp)$ and 
+$(b \in BExp)$. A $\mathit{CStatement}$ is an assignment,
+conditional, sequential concatenation or a loop.
+$\mathit{moduleName(Var_1,\dots,Var_n)}$ invokes the top level 
+procedure of the $\mathcal{SN}$. Recall that $\mathcal{SN}$ is a
+software netlist representation of HW RTL models.
+The interface variables $\{Var\_1,\dots,Var\_n\}$ 
+(input, output and inout ports) are declared inside the 
+FW to communicate with $\mathcal{SN}$. \\ 
+%
+%\textbf{Producer-consumer Interaction:}
+%
+A communicating pair of executions of 
 $\mathcal{FT}$ and $\mathcal{HT}$ is an {\em interaction}, which 
 takes place through shared variables (or shared registers)
-only.
-
-\Omit{
-\textbf{Producer:} 
-$\mathcal{FT}$ (or $\mathcal{HT}$) is called a {\em producer} 
-if it produces a data ($d$) that is independent of $\mathcal{HT}$ (or $\mathcal{FT}$). 
-Thus, the interleavings between $\mathcal{FT}$ and $\mathcal{HT}$ 
-can be avoided to compute $d$. 
-}
-
-\textbf{Producer-consumer Interaction:}
-%
-An interaction is said to exhibit {\em producer-consumer}
+only.  An interaction is said to exhibit {\em producer-consumer}
 interaction pattern if 1) the set of variables $V$ written by 
@@
 in $V'$ and $V$, respectively.
-
-\Omit{
-shared register only FT is writing 
-shared register that HT is writing 
-and these two sets are disjoint
-$\mathcal{FT}$ and $\mathcal{HT}$ is said to exhibit   
-{\em producer-consumer} interaction pattern specific 
-to data $d$ if $\mathcal{FT}$ produces $d$ and $\mathcal{HT}$ 
-consumes $d$. Similarly, when $\mathcal{HT}$
-is a producer of $d$ and $\mathcal{FT}$ is a consumer of $d$, 
-$\mathcal{HT}$ and $\mathcal{FT}$ is said to exhibit   
-{\em producer-consumer} interaction pattern specific to $d$. 
-A producer-consumer interaction is defined with respect 
-to the data produced. 
-}
 
@@
 %
-{\bf Unified Co-verification model:}
-A {\em program netlist} $\mathcal{PN}$ is a sequential unified
-model of FW and HW. $\mathcal{PN}$ is formally defined as follows.
-\[ 
-\begin{array}[t]{@{}lll}
-\mathcal{PN} & {:}{:}{=} & \mathit{Procedure} \\
-\mathit{Procedure} & {:}{:}{=} & \mathit{Statement} \mid \mathit{Procedure} \\
-\mathit{Statement} & {:}{:}{=} & CStatement \mid \mathit{moduleName(Var_1,\dots,Var_n)} \\
-\mathit{CStatement} & {:}{:}{=} & x {:}{=} exp \mid \mathit{ITE}(b, s_1,s_2) \mid \mathit{s_1;s_2} \mid loop\{s\} \\ 
-\end{array}
-\]
-Consider sets of expressions $Exp$ and Boolean expressions $BExp$ 
-over variables $Var$ of $\mathcal{PN}$ such that $(exp \in Exp)$ and 
-$(b \in BExp)$. A $\mathit{CStatement}$ is an assignment,
-conditional, sequential concatenation or a loop.
-$\mathit{moduleName(Var_1,\dots,Var_n)}$ invokes the top level 
-procedure of the $\mathcal{SN}$. Recall that $\mathcal{SN}$ is a
-software netlist representation of HW RTL models.
-The interface variables $\{Var\_1,\dots,Var\_n\}$ 
-(input, output and inout ports) are declared inside the 
-FW to communicate with $\mathcal{SN}$. \\ 
-\Omit{
-$\mathcal{PN}$ is verification equivalent 
-to the concurrent execution of FW and $\mathcal{SN}$.
-}
-\textbf{Property Driven Slicing of Program Netlist:}
-A property-driven slicing is performed on the unified model, $\mathcal{PN}$.  
+\textbf{Step 3: Property Driven Slicing of Co-verification Model}
+A property-driven slicing is performed on the unified model, $\mathcal{M}_{seq}$.  
 This step is purely syntactic, meaning that we perform a backward dependency 
@@
 is then passed to the symbolic execution engine for path-based exploration.
-\Omit{
-\section{Extracting relevant FW/HW interactions using}
-Our unified FW-HW model, $\mathcal{PN}$, is composed of a set of 
-FW scenarios, $\{\mathcal{S}\}$, and a set of HW transactions, $\{\mathcal{T}\}$ 
-that $\{\mathcal{S}\}$ depends on. However, only a subset of $\{\mathcal{T}\}$ is 
-relevant for a particular $\mathcal{S}_i \in \mathcal{S}$. In this section, 
-we present a path-based exploration algorithm to automatically infer 
-interacting $\mathcal{S}/\mathcal{T}$ pairs from $\mathcal{PN}$. 
-}
+
 %=======================================================================================
@@
 }
-
+%
 \input{verifox}
-\Omit{
-\rmcmt{
-The hardware and firmware run independently of each other. 
-The communication between them takes place through interrupts. 
-The interrupts are modelled by function calls. 
-}
-}
-%
-\section{The Conventional Approach to Co-verification}
+%
+\subsection{Approach 2: Monolithic Co-verification Technique}
 %
@@
 }
-
 %===============================================================================

### 2017-04-03 verifox.tex
Approach 1 description complete

@@
-\subsection{Path-based Symbolic Execution}
-We have developed a symbolic execution tool, \verifox, 
-for FW-HW co-verification of IP level and SoC level designs. 
-Given a program netlist model, $\mathcal{PN}$, a scenario, 
+\textbf{Step 4: Mining Scenario/Transaction Pairs Using Symbolic Execution}
+Given a co-verification model, $\mathcal{M}_{seq}$, a scenario, 
 $\mathcal{S}$, and a property expressed as $\mathit{assert}(c)$ 
-(where $c$ is a condition stated in terms of variables in $\mathcal{PN}$)
-as input, \verifox performs path-based exploration of $\mathcal{PN}$ 
+(where $c$ is a condition stated in terms of variables in $\mathcal{M}_{seq}$)
+as input, \verifox performs path-based exploration of $\mathcal{M}_{seq}$ 
 to automatically infer {\em scencario/transaction} pairs and check their validity 
 using backend solvers. If the condition $c$ does not hold, 
-then $\mathcal{PN}$ is said to have violated the property.
+then $\mathcal{M}_{seq}$ is said to have violated the property.
 
-\Omit{
-explores only those FW-HW interactions
-that are relevant to $\mathcal{S}$. \verifox
-
-\verifox takes a C program as an input, where 
-the properties of interest are specified using 
-statements in the code. Here, $c$ is a condition 
-stated in terms of program variables that we 
-want to hold at the point where the assertion occurs. 
-}
-
-\Omit{
- that performs 
-path-based exploration of a unified FW-HW model, 
-$\mathcal{PN}$ to automatically check the validity of the 
-relevant {\em scencario/transaction} pairs of the FW-HW interactions.
-}
-\Omit {
-\verifox performs depth-first exploration 
-of program paths with aggressive pruning strategy  
-with certain optimizations
-that makes it suitable for verifying hardware designs. 
-A hardware circuit having its 
-behaviour specified in a manner similar to state machine, would usually
-be translated into a program that has a large number of control-flow paths with
-only tiny fractions of them being feasible. 
-}
 A typical path-based symbolic execution engine might explore 
@@
 \begin{small}
-\Input{Program Netlist $\mathcal{PN}$ with properties specified with $assert(c)$, scenario specified with $assume(c)$}
+  \Input{Co-verification Model $\mathcal{M}_{seq}$ with properties specified with $assert(c)$, scenario specified with $assume(c)$}
 \Output{The status (\safe or \unsafe) and a counterexample if \unsafe}
@@
 \end{small}
-\caption{Working of \textsc{verifox}\label{Alg:verifox}}
+\caption{Mine Scenario/Transaction Pair Using Symbolic Execution\label{Alg:verifox}}
 \end{algorithm2e}
@@
 paths as early as possible. }
-\vspace{-4mm}
+%\vspace{-4mm}
 \algref{verifox} shows the overall algorithm of \verifox. States mentioned

### 2017-04-03 paper.tex
minor

@@
 model it interacts with, 2) lack of co-specification model that precisely
-captures the design intent of the communication between HW and FW, 3) lack 
+captures the design intent of the communication between HW and FW, 3) Large
+number of interleavings between HW and FW threads, and 4) lack 
 of automated formal tools that support co-designs implemented in C/C++ and 
@@
 
-%A key to building an effective co-verification tool is to translate the HW
-%and SW models to a common formal semantics called, 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 verification reuse and can be readily used in assertion-based verification.  
-
+%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 A firmware only exercise some fragment of hardware state-space in a typical 
-hardware/software co-design~\cite{dac17,taa,ibm-other}.  
+hardware/software
+co-design~\cite{polig2014micro,polig2014fpl,giefers2015accelerating}.  
 A firmware services the requests from the application software 
@@
 practical co-design environment. 
-
-\Omit{
-A system is comprised of a set of concurrent FW and HW transactions which
-interleaves asynchronously. It is well recognized that concurrency is at
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+ %                        Concurrency   
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+A co-design system is comprised of a set of concurrent FW and HW transactions 
+which interleaves asynchronously. It is well recognized that concurrency is at
 the heart of co-verification. The number of interleavings between the FW
@@
 verification process.  
-
-The concurrency between the HW and SW components is a key challenge in
-co-verification.  In this paper, we exploit specific interaction patterns
-between the FW and HW to reduce the number of interleavings.  We observe
-that this interaction pattern follows a producer-consumer relationship --
+However, we observe that in practise, industrial co-designs exhibits 
+producer-consumer
+relationship~\cite{polig2014micro,polig2014fpl,giefers2015accelerating} --
 the master module (producer) solely updates the shared registers which are
 consumed by the slave (consumer).  This key observation allows us to
-sequentialize a concurrent FW-HW model following specific interaction
-patterns.
-}
-
+sequentialize concurrent FW and HW models following specific interaction
+patterns.  This drastically reduces the total number of interleavings 
+between a FW and HW threads and simplies the overall verification effort. 
+%
 %===============================================================================
@@
 Depending on the type of interrupt, the firmware either receives a data packet 
-or sends a data packet over the serial output.
-
-\rmcmt{The $set\_inputs()$ and
+or sends a data packet over the serial output.  The $set\_inputs()$ and
 $next\_timeframe()$ functions, used in $wb$ functions, are 
-primitives in \textsc{HW-CBMC} that direct the tool to set the 
-inputs to the HW signals and advance the HW clock, respectively.}
+firmware primitives that direct our tool to set the inputs to the HW signals 
+and advance the HW clock, respectively.
 
@@
 %
+
 \textbf{Scenario ($\mathcal{S}$):}
@@
 transmitter} as well as {\em receiver} module.
-
-\rmcmt{This constrained interactions can be exploited 
-to decompose the verification state-space. 
-This requires an automatic technique for scenario driven 
-partitioning of the FW-HW transactions to generate only 
-relevant {\em Scenario/Transaction} pairs. Conventional 
-approaches for co-verification construct a unified 
-FW-HW model in FSM or BPDS that restrict such decomposition. 
-In this paper, we built a unified FW-HW model in C program 
-which enable us to automatically generate such {\em scenario/transaction} 
-pairs using path-based symbolic execution techniques. The details 
-of our technique are explained in the next section.}
 %
@@
 signals in the circuit.  $Asgn$ is a finite set of assignments 
-to $Out$, $Seq$ and $Comb$. 
+to $Out$, $Seq$ and $Comb$. \\ 
 %
@@
 Similarly, $\mathcal{FT}$ is the producer of $data$, $(outb(data,UART\_TR))$, 
-in state $s_6$ which is consumed by $\mathcal{HT}$. These interaction patterns 
-between $\mathcal{HT}$ and $\mathcal{FT}$ is exploited to generate a 
-sequential unified {\em program netlist} model which is defined next.\\ \\
+in state $s_6$ which is consumed by $\mathcal{HT}$. Thus, the interaction
+pattern between $\mathcal{HT}$ and $\mathcal{FT}$ clearly exhibits producer-consumer
+relationship. This enables us to sequentialize the HW and FW thread. \\
 %
@@
 program fragments that are relevant to a given property. The sliced program 
-is then passed to the symbolic execution engine for path-based exploration.
-
+is then passed to the symbolic execution engine for path-based exploration. \\
+%
 %=======================================================================================
@@
 
-Generating a unified FW-HW model for co-verification is a well-known 
-technique. Notably, Kurshan et al.~modeled HW and 
+Generating a unified co-verification model is a well-known 
+technique in HW/SW co-verification.  Notably, Kurshan et al.~modeled HW and 
 SW using finite state machines~\cite{fmsd02}, Monniaux in~\cite{emsoft07} modeled
@@
 model a hardware and PDS to abstractly model a software to generate a unified SW-HW model, 
-called Buchi Pushdown System ({\em BPDS}).
+called Buchi Pushdown System ({\em BPDS}).  In this paper, we construct an unified 
+sequential co-verification model in C which enable us to automatically 
+generate {\em scenario/transaction} pairs using path-based symbolic execution.
 
@@
 
-\bibliographystyle{ACM-Reference-Format}
+%\bibliographystyle{ACM-Reference-Format}
+\bibliographystyle{abbrv}
 \bibliography{biblio}

### 2017-04-03 paper.tex
missing reference

@@
 array containers $rx\_b$ and $tx\_b$ stores the data obtained through the $inb$
-and $outb$ function calls which directly reads and writes the UART IP ports
+and $outb$ function calls which directly read from and write to the UART IP ports
 respectively. 

### 2017-04-03 paper.tex
circuit to software

@@
 and $outb$ function calls which directly read from and write to the UART IP ports
-respectively. 
+respectively. \rmcmt{more on co-specification PSL}. 
 \[
@@
 %
-\Omit{
-\textbf{Problem Statement}
-Given a FW model in C, HW models in Verilog RTL, a property $\psi$ and 
-a set of scenarios, the goal is to check whether $\psi$ holds under all 
-scenarios in the combined FW-HW model. 
-}
-%
 \section{Proposed Methodology}
-
+%
 \subsection{Approach 1: Path-based Co-verification Technique}
@@
 signals in the circuit.  $Asgn$ is a finite set of assignments 
-to $Out$, $Seq$ and $Comb$. \\ 
+to $Out$, $Seq$ and $Comb$. Figure~\ref{ex1} shows an example of 
+translating a Verilog RTL circuit with an always block and continuous
+assignment statement into an equivalent C program.
+%
+\begin{figure*}[t]
+\scriptsize  
+\centering
+\begin{tabular}{l|l|l}
+\hline
+ Verilog & Dataflow Graph & Software netlist \\
+\hline
+\begin{lstlisting}[mathescape=true,language=Verilog]
+module top(clk, a);
+input clk, a;
+reg b, d, e;
+wire c = e ? 1'b0:d;
+wire cond = a;
+always @(posedge clk) 
+ begin
+  b<=a;
+  if(cond && b)
+   e<=b;
+  else 
+   e<=0;
+  d<=c;
+ end
+endmodule
+\end{lstlisting}
+&
+\begin{minipage}{5.0cm}
+\centering
+\scalebox{.5}{\import{figures/}{ckt.pspdftex}}
+\end{minipage}
+&
+\begin{lstlisting}[mathescape=true,language=C]
+struct state_elements_top {
+ unsigned int b, d, e, c;
+};
+struct state_elements_top  u1;
+void top(unsigned int clk, 
+   unsigned int a)
+{
+  _Bool b_old,d_old,e_old;
+  _Bool cond;
+
+  b_old = u1.b;
+  d_old = u1.d;
+  e_old = u1.e;
+
+  cond = a;
+  u1.c = (u1.e) ? 0 : u1.d;
+
+ u1.b = a;
+ if(cond && b_old)
+    u1.e = b_old;
+  else
+    u1.e = 0;
+  u1.d = u1.c;  
+}
+\end{lstlisting}
+\\
+\hline
+\end{tabular}
+\caption{Circuit to Software}
+\label{ex1}
+\end{figure*}
 %
@@
 single-threaded co-verification model in C.  The motivation behind
-sequentialization is based on our observation that practical industrial
-co-designs exhibit producer-consumer interaction behavior.  We observe 
-that in practise, a FW thread is mostly independent of the HW thread they interact 
-with~\cite{hvc,codes14}.  This behavior is also prevelant in industrial co-designs, 
-such as IBM Text Accelerator co-design~\cite{polig2014micro,polig2014fpl}
-and IBM coherent FFT coprocessor~\cite{giefers2015accelerating}.
+sequentialization is based on our observation that many practical industrial
+co-designs exhibit producer-consumer interaction behavior, such as IBM 
+Text Accelerator co-design~\cite{polig2014micro,polig2014fpl}, 
+IBM coherent FFT coprocessor~\cite{giefers2015accelerating}, RockBox 
+Media Player~\cite{hvc}, linux device driver interacting with QEMU emulated
+hardware code~\cite{codes14} and others.  We observe that in practise, a FW 
+thread is mostly independent of the HW thread they interact with~\cite{hvc,codes14}.  
 Specifically, a FW thread is only responsible for configuring the 
@@
 %
-We formally define a single-threaded sequential unified co-verification model, 
-denoted by $\mathcal{M}_{seq}$. 
+We now formally define a single-threaded sequential co-verification model, 
+denoted by $\mathcal{M}_{seq}$, obtained by sequentializing the HW and FW 
+models.
+%
 \[ 

### 2017-04-03 paper.tex
table for stats

@@
 available~\cite{codes14,codes15}. Co-verification of the TLM and the
-SW is typically performed by means of testing.
+SW is typically performed by means of testing~\cite{hvc,codes14}.
 
@@
     approach is implemented in a tool called, \verifox. Both tools can handle
-    co-designs where the hardware is implemented in Verilog RTL and firmware is  
-    specified in ANSI-C.  We distribute the HW/SW co-verification tools, \hwcbmcv and 
-    \verifox, along with our co-design benchmarks in Verilog RTL and C models
+    co-designs where the hardware is implemented in Verilog RTL (IEEE
+    SystemVerilog 2005 standards) and firmware is  
+    specified in ANSI-C (C89, C99 standards).  We distribute the HW/SW 
+    co-verification tools, \hwcbmcv and \verifox, along with our co-design 
+    benchmarks in Verilog RTL and C models 
     here~\footnote{https://drive.google.com/folderview?id=0BynC6sd-wTYgWVQ4bXNtRDB5a2c\&usp=sharing}.
@@
 
-   \item We present an unified property specification language in \hwcbmcv and 
-     \verifox that allows designers to write meaningful formal co-specification 
-     over hardware and firmware events. We believe that the formal
-     co-specification model will significantly ease the adoption of formal tools 
-     for co-verification of industrial strength co-designs.
+   \item We present an unified property specification language for
+     co-verification that allows engineers to write meaningful 
+     formal co-specification over hardware and firmware events and specify
+     temporal correlation between these events.  Our tool also supports a
+     fragment of IEEE Property Specification Language.
+
+     %We believe that the formal
+     %co-specification model will significantly ease the adoption of formal tools 
+     %for co-verification of industrial strength co-designs.
 
@@
 \centering
-\begin{tabular}{l|l|l}
+\begin{tabular}{l|l|l|l}
 \hline
- Verilog & Dataflow Graph & Software netlist \\
+  Verilog & Formal Semantics & Synthesized Hardware & Software netlist \\
 \hline
@@
 input clk, a;
-reg b, d, e;
-wire c = e ? 1'b0:d;
-wire cond = a;
+reg b,d,e; 
+wire c,cond;
+assign c = e ? 1'b0:d;
+assign cond = a;
 always @(posedge clk) 
@@
 &
-\begin{minipage}{5.0cm}
+\begin{minipage}{4.2cm}
+%\centering
+\scalebox{.5}{\import{figures/}{semantics.pspdftex}}
+\end{minipage}
+&
+\begin{minipage}{4.0cm}
 \centering
@@
 struct state_elements_top {
- unsigned int b, d, e, c;
-};
+ unsigned int b, d, e; };
 struct state_elements_top  u1;
 void top(unsigned int clk, 
-   unsigned int a)
-{
-  _Bool b_old,d_old,e_old;
-  _Bool cond;
-
-  b_old = u1.b;
-  d_old = u1.d;
-  e_old = u1.e;
-
+   unsigned int a) {
+  _Bool c,cond;
+  _Bool b_old=u1.b, d_old=u1.d;
+  _Bool e_old=u1.e;
   cond = a;
-  u1.c = (u1.e) ? 0 : u1.d;
-
+  c = (u1.e)?0:u1.d;
   u1.b = a;
@@
     u1.e = 0;
-  u1.d = u1.c;  
-}
+  u1.d = c;  }
 \end{lstlisting}
@@
 %
+
 \textbf{Step 2: Constructing Co-verification Model}
@@
 in $V'$ and $V$, respectively.
-
+%
+%
+\begin{figure}[t]
+\scalebox{.55}{\import{figures/}{interleaving.pspdftex}}
+\caption{Producer Consumer Interactions Pattern
+\label{fig:interleaving1}}
+\end{figure}
+%
+\textbf{Step 3: Property Driven Slicing of Co-verification Model}
+A property-driven slicing is performed on the unified model, $\mathcal{M}_{seq}$.  
+This step is purely syntactic, meaning that we perform a backward dependency 
+analysis starting from the property which only preserve those 
+program fragments that are relevant to a given property. The sliced program 
+is then passed to the symbolic execution engine for path-based exploration. \\
+%
+%=======================================================================================
+%\subsection{\verifox: Path-wise Symbolic Execution Tool} 
+%=======================================================================================
+%\Omit{
+%\begin{figure}[tp]
+%\centering
+%\vspace*{0.3cm}
+%\scalebox{.50}{\import{figures/}{work-flow.pspdftex}}
+%\caption{Automated Slicing and Trace partitioning\label{fig:desc}}
+%\end{figure}
+%}
+\Omit{
+\begin{figure}[t]
+\tikzstyle{rblock}=[rounded corners,draw=black]
+\tikzstyle{block}=[draw=black]
+\begin{tikzpicture}
+
+\node (v2c) [rblock] {\scs{\emph{v2c}}};
+\node (snl) [block,below of=v2c] {\scs{Software-netlist}};
+\draw[->] (v2c) -- (snl);
+
+\node (HD) [above left=.3cm and .3cm of v2c] {\scs{\parbox{8em}{Hardware Design \\ (in Verilog)}}};
+\draw[->] (HD) -- (v2c);
+
+\node (prop) [above right=.3cm and .3cm of v2c] {\scs{\parbox{8em}{Property \\ (in SVA)}}};
+\draw[->] (prop) -- (v2c);
+
+\node (cmm) [block,below of=snl] {\scs{\parbox{9em}{Composite Monolithic Model}}};
+\draw[->] (snl) -- (cmm);
+
+\node (dcmm) [left=1cm of cmm] {};
+\node (fw) [above=.1cm of dcmm  ] {\scs{Firmware}};
+\node (as) [below=.1cm of dcmm] {\scs{Assumptions}};
+\draw[->] (fw) -- (cmm);
+\draw[->] (as) -- (cmm);
+
+\node (pds) [block,below of=cmm] {\scs{\parbox{8em}{Property-driven slicing}}};
+\draw[->] (cmm) -- (pds);
+
+\node (tp) [block,below=.8cm of pds] {\scs{Trace partitioning}};
+\node (iss) [block,below right=.5cm  and .05cm of tp.east] {\scs{\parbox{6em}{Incremental SAT solving}}};
+\node (sat) [rblock,below=1.5cm of tp] {\scs{SAT solver}};
+\node (ipp) [block,left=2cm of iss] {\scs{\parbox{6em}{Infeasible path pruning}}};
+
+\draw [<->] (tp) -- (iss);
+\draw [<->] (tp) -- (ipp);
+\draw [<->] (sat) -- (iss);
+\draw [<->] (sat) -- (ipp);
+
+\node (vfbox) [rblock,fit={(tp) (iss) (sat) (ipp)}] {};
+\draw[->] (pds) -- (vfbox);
+
+\node (verifox) [right=.2cm of tp] {\scs{{\bf \verifox}}};
+
+\node (safe) [above right=.2cm and .2cm of vfbox.east] {\scs{Verification Successful}};
+\node (unsafe) [below right=.2cm and .2cm of vfbox.east] {\scs{\parbox{8em}{Verification Failed (Counterexample)}}};
+
+\draw[->] (vfbox.9) -- (safe);
+\draw[->] (vfbox.-12) -- (unsafe);
+
+\end{tikzpicture}
+\caption{Automated Slicing and Trace partitioning\label{fig:desc}}
+\end{figure}
+}
+%
+\input{verifox}
+%
+\subsection{Approach 2: Monolithic Co-verification Technique}
+%
+\begin{figure}[t]
+\begin{center}
+\includegraphics[scale=0.6]{figures/traditional_flow.pdf}
+\caption{Conventional HW/SW Co-verification Flow}
+\label{fig:conventional}
+\end{center}
+\end{figure}
+
+Figure~\ref{fig:conventional} illustrates the conventional approach to HW/SW
+co-veri\-fi\-cation, as implemented in the state-of-the-art co-verification
+tool, \hwcbmcv~\cite{CKY03,vlsid13}.  \hwcbmcv is the only open-source
+formal co-verification tool that supports Verilog RTL (System Verilog 2009
+standard) and C/C++ firmware.  In contrast to our proposed approach,
+\hwcbmcv maintains two separate flows for HW and FW.  The top flow in
+Figure~\ref{fig:conventional} uses synthesis to obtain either a bit-level or
+a word-level netlist from Verilog RTL.  The bottom flow illustrates the
+translation of the C program into static single assignment (SSA) form. 
+These two flows meet only at the solver.  Thus, \hwcbmcv generates a
+monolithic formula from the C and RTL description, which is then checked
+with SAT/SMT solvers.  \hwcbmcv provides specific handshake primitives such
+as $next\_timeframe()$ and $set\_inputs()$ to model FW-HW communications.
+%
+\Omit{
+The hardware and firmware run independently of each other. 
+The communication between them takes place through these function calls. 
+}
+%===============================================================================
+\section{Experimental Results}
+%===============================================================================
+%
+We report experimental results for FW-HW co-verification of a UART IP and a
+SoC design.  All our experiments were performed on an Intel Xeon 3.07\,GHz
+machine with 48\,GB RAM.  All times reported are in seconds.  The timeout 
+for all our experiments was set to 2~hours.  
+%
+%-------------------------------------------------------------------------------
+\subsection{FW-HW co-verification of UART}
+%-------------------------------------------------------------------------------
+
+\textbf{\emph{About UART:}} A UART IP core is used for asynchronous
+transmission and reception of data which provides serial communication
+capabilities with a modem or other external devices.  The UART IP is
+compliant with industry standards for UART and interfaces with the wishbone
+bus.  The core supports single transmission/reception format which is
+1~start bit, 1~stop bit and 8~data bits without parity.  It also contains a
+single transmit/receive buffer.  The UART IP implements a baud rate
+generation circuit based on a harmonic frequency synthesizer that support a
+wide variety of clock frequencies.  The UART IP core is implemented in
+approximately 1000 lines of Verilog RTL, generating several thousand gates. 
+The UART is obtained from~\url{http://www.opencores.org}.  A software
+netlist model (in C) is synthesized from the UART RTL using \emph{v2c}.  The
+software netlist model is approximately 1100 LOC.
+\rmcmt{refer stats table}
+%
+\begin{table}
+\begin{center}
+{\scriptsize
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline
+  Circuit & Verilog & Latches(L)/ & Input & Output & GATE & Firmware \\
+  & LOC & FF & Ports & Ports & Count & (LOC)\\ 
+\cline{1-7}
+\multicolumn{7}{|c|}{Universal Asynchronous Receiver Transmitter} \\ \hline 
+  UART & 1200 & 356 & 12 & 9 & 413 & 528 \\ \hline
+\multicolumn{7}{|c|}{System-On-a-Chip} \\ \hline 
+  SoC & 3567 & 840 & 14 & 11 & 945 & 734 \\ \hline
+\end{tabular}
+}
+\end{center}
+\caption{\scriptsize Design statistics for UART IP and SoC Design}
+\label{table:stats}
+\end{table}  
+%
+\textbf{\emph{UART Configuration:}} The UART IP core is configured in
+different operating modes, namely--{\em transmission without interrupt
+enabled} (Scenario A), {\em transmission with interrupt enabled} (Scenario
+B) and {\em loopback mode with interrupt enabled} (Scenario C).  The
+data-width varies in each mode, ranging from 8~bits to 64~bits.  Scenario A
+and Scenario B exercises only the transmitter module to transmit
+non-deterministic data through the serial output.  The receiver module is
+inactive in Scenario A and Scenario B.  By contrast, in Scenario C we
+configure the UART in loopback mode with interrupt logic enabled.  Thus,
+both the transmitter and the receiver are active in this mode.  The firmware
+can receive interrupt from the transmitter or receiver module depending on
+whether the transmitter buffer is empty or the receiver buffer is full
+respectively, hence the control is non-deterministic in this mode.
+%
+\textbf{Firmware Hardware Interaction Pattern in UART}
 Figure~\ref{fig:interleaving1} illustrates the FW-HW interaction pattern 
@@
 relationship. This enables us to sequentialize the HW and FW thread. \\
-%
-\begin{figure}[t]
-\scalebox{.55}{\import{figures/}{interleaving.pspdftex}}
-\caption{Producer Consumer Interactions Pattern
-\label{fig:interleaving1}}
-\end{figure}
-%
-\textbf{Step 3: Property Driven Slicing of Co-verification Model}
-A property-driven slicing is performed on the unified model, $\mathcal{M}_{seq}$.  
-This step is purely syntactic, meaning that we perform a backward dependency 
-analysis starting from the property which only preserve those 
-program fragments that are relevant to a given property. The sliced program 
-is then passed to the symbolic execution engine for path-based exploration. \\
-%
-%=======================================================================================
-%\subsection{\verifox: Path-wise Symbolic Execution Tool} 
-%=======================================================================================
-%\Omit{
-%\begin{figure}[tp]
-%\centering
-%\vspace*{0.3cm}
-%\scalebox{.50}{\import{figures/}{work-flow.pspdftex}}
-%\caption{Automated Slicing and Trace partitioning\label{fig:desc}}
-%\end{figure}
-%}
-\Omit{
-\begin{figure}[t]
-\tikzstyle{rblock}=[rounded corners,draw=black]
-\tikzstyle{block}=[draw=black]
-\begin{tikzpicture}
-
-\node (v2c) [rblock] {\scs{\emph{v2c}}};
-\node (snl) [block,below of=v2c] {\scs{Software-netlist}};
-\draw[->] (v2c) -- (snl);
-
-\node (HD) [above left=.3cm and .3cm of v2c] {\scs{\parbox{8em}{Hardware Design \\ (in Verilog)}}};
-\draw[->] (HD) -- (v2c);
-
-\node (prop) [above right=.3cm and .3cm of v2c] {\scs{\parbox{8em}{Property \\ (in SVA)}}};
-\draw[->] (prop) -- (v2c);
-
-\node (cmm) [block,below of=snl] {\scs{\parbox{9em}{Composite Monolithic Model}}};
-\draw[->] (snl) -- (cmm);
-
-\node (dcmm) [left=1cm of cmm] {};
-\node (fw) [above=.1cm of dcmm  ] {\scs{Firmware}};
-\node (as) [below=.1cm of dcmm] {\scs{Assumptions}};
-\draw[->] (fw) -- (cmm);
-\draw[->] (as) -- (cmm);
-
-\node (pds) [block,below of=cmm] {\scs{\parbox{8em}{Property-driven slicing}}};
-\draw[->] (cmm) -- (pds);
-
-\node (tp) [block,below=.8cm of pds] {\scs{Trace partitioning}};
-\node (iss) [block,below right=.5cm  and .05cm of tp.east] {\scs{\parbox{6em}{Incremental SAT solving}}};
-\node (sat) [rblock,below=1.5cm of tp] {\scs{SAT solver}};
-\node (ipp) [block,left=2cm of iss] {\scs{\parbox{6em}{Infeasible path pruning}}};
-
-\draw [<->] (tp) -- (iss);
-\draw [<->] (tp) -- (ipp);
-\draw [<->] (sat) -- (iss);
-\draw [<->] (sat) -- (ipp);
-
-\node (vfbox) [rblock,fit={(tp) (iss) (sat) (ipp)}] {};
-\draw[->] (pds) -- (vfbox);
-
-\node (verifox) [right=.2cm of tp] {\scs{{\bf \verifox}}};
-
-\node (safe) [above right=.2cm and .2cm of vfbox.east] {\scs{Verification Successful}};
-\node (unsafe) [below right=.2cm and .2cm of vfbox.east] {\scs{\parbox{8em}{Verification Failed (Counterexample)}}};
-
-\draw[->] (vfbox.9) -- (safe);
-\draw[->] (vfbox.-12) -- (unsafe);
-
-\end{tikzpicture}
-\caption{Automated Slicing and Trace partitioning\label{fig:desc}}
-\end{figure}
-}
-%
-\input{verifox}
-%
-\subsection{Approach 2: Monolithic Co-verification Technique}
-%
-\begin{figure}[t]
-\begin{center}
-\includegraphics[scale=0.6]{figures/traditional_flow.pdf}
-\caption{Conventional HW/SW Co-verification Flow}
-\label{fig:conventional}
-\end{center}
-\end{figure}
-
-Figure~\ref{fig:conventional} illustrates the conventional approach to HW/SW
-co-veri\-fi\-cation, as implemented in the state-of-the-art co-verification
-tool, \hwcbmcv~\cite{CKY03,vlsid13}.  \hwcbmcv is the only open-source
-formal co-verification tool that supports Verilog RTL (System Verilog 2009
-standard) and C/C++ firmware.  In contrast to our proposed approach,
-\hwcbmcv maintains two separate flows for HW and FW.  The top flow in
-Figure~\ref{fig:conventional} uses synthesis to obtain either a bit-level or
-a word-level netlist from Verilog RTL.  The bottom flow illustrates the
-translation of the C program into static single assignment (SSA) form. 
-These two flows meet only at the solver.  Thus, \hwcbmcv generates a
-monolithic formula from the C and RTL description, which is then checked
-with SAT/SMT solvers.  \hwcbmcv provides specific handshake primitives such
-as $next\_timeframe()$ and $set\_inputs()$ to model FW-HW communications.
-%
-\Omit{
-The hardware and firmware run independently of each other. 
-The communication between them takes place through these function calls. 
-}
-%===============================================================================
-\section{Experimental Results}
-%===============================================================================
-
-We report experimental results for FW-HW co-verification of a UART IP and a
-SoC design.  All our experiments were performed on an Intel Xeon 3.07\,GHz
-machine with 48\,GB RAM.  We use a state-of-the-art hardware/software
-co-verification tool, \hwcbmcv, and compare it against \verifox. 
-MiniSAT-2.2.0~\cite{DBLP:conf/sat/EenB05} was used as underlying SAT solver
-with \verifoxver, CBMC-5.0~\cite{DBLP:conf/tacas/ClarkeKL04} and
-\hwcbmcver~\cite{CK03}.  We also used other path-based symbolic execution
-tools, such as, \kleever and \symbioticver for our experiments and presented
-a comparison with \verifoxver.  All times reported are in seconds.  The
-timeout for all our experiments was set to 2~hours.  The UART IP, SoC
-benchmark (Verilog RTL and Firmware in C) and our co-verification
-tools,\hwcbmcv and \verifox, are available for
-download~\footnote{https://drive.google.com/folderview?id=0BynC6sd-wTYgWVQ4bXNtRDB5a2c\&usp=sharing}.
-
-\Omit{
-\item {\em {\verifox} -- A tool for HW/SW co-verification:} We address the
-co-verification problem at post-RTL phase and present a tool, \verifox, for
-bounded HW/SW co-verification of IP level and SoC level design.  \verifox
-supports IEEE 1364-2005 System Verilog standards and the C89, C99 standards. 
-\verifox also supports SAT and SMT backends for constraint solving.  
-}
-\Omit{
-Even though \verifox supports SMT solvers such as
-Z3~\cite{z32008} as backend solvers, the current implementation communicates
-with these solvers using files rather than APIs.  Since a new solver
-instance is generated for every query, incremental encoding cannot be used. 
-Due to this, the runtimes of \verifox with SMT solvers on benchmarks are
-significantly higher.  As the current implementation does not support
-incremental encoding with SMT solvers, the runtimes would not provide a fair
-comparison of \verifox with SMT versus \verifox with SAT solvers. 
-Therefore, we are omitting the results obtained using SMT solvers.
-
-All the benchmarks in
-Verilog (excluding commercial ARM IP), software-netlist models in C,
-firmware models, our tool \textsc{Verifox} and scripts for running \hwcbmcv,
-\cbmc, \textsc{klee} and \textsc{Symbiotic} are available
-here~\footnote{https://drive.google.com/file/d/0BynC6sd-wTYgSEU5eEswbnRqWUE/view?usp=sharing}
-}
-
-%-------------------------------------------------------------------------------
-\subsection{FW-HW co-verification of UART}
-%-------------------------------------------------------------------------------
-
-\textbf{\emph{About UART:}} A UART IP core is used for asynchronous
-transmission and reception of data which provides serial communication
-capabilities with a modem or other external devices.  The UART IP is
-compliant with industry standards for UART and interfaces with the wishbone
-bus.  The core supports single transmission/reception format which is
-1~start bit, 1~stop bit and 8~data bits without parity.  It also contains a
-single transmit/receive buffer.  The UART IP implements a baud rate
-generation circuit based on a harmonic frequency synthesizer that support a
-wide variety of clock frequencies.  The UART IP core is implemented in
-approximately 1000 lines of Verilog RTL, generating several thousand gates. 
-The UART is obtained from~\url{http://www.opencores.org}.  A software
-netlist model (in C) is synthesized from the UART RTL using \emph{v2c}.  The
-software netlist model is approximately 1100 LOC.
-
-\textbf{\emph{UART Configuration:}} The UART IP core is configured in
-different operating modes, namely--{\em transmission without interrupt
-enabled} (Scenario A), {\em transmission with interrupt enabled} (Scenario
-B) and {\em loopback mode with interrupt enabled} (Scenario C).  The
-data-width varies in each mode, ranging from 8~bits to 64~bits.  Scenario A
-and Scenario B exercises only the transmitter module to transmit
-non-deterministic data through the serial output.  The receiver module is
-inactive in Scenario A and Scenario B.  By contrast, in Scenario C we
-configure the UART in loopback mode with interrupt logic enabled.  Thus,
-both the transmitter and the receiver are active in this mode.  The firmware
-can receive interrupt from the transmitter or receiver module depending on
-whether the transmitter buffer is empty or the receiver buffer is full
-respectively, hence the control is non-deterministic in this mode.
-
+\rmcmt{stats in a table, remove klee result, SoC diagram}
 \textbf{\emph{Discussion:}}

### 2017-04-04 paper.tex
restructure intro and approach 1

@@
+%[FORMAT: 10 page ACM two-column format in 9pt]
 \documentclass[sigconf]{acmart}
@@
 \usepackage{booktabs} % For formal tables
-
-%\usepackage[ruled]{algorithm2e} % For algorithms
-%\renewcommand{\algorithmcfname}{ALGORITHM}
-%\SetAlFnt{\small}
-%\SetAlCapFnt{\small}
-%\SetAlCapNameFnt{\small}
-%\SetAlCapHSkip{0pt}
-%\IncMargin{-\parindent}
-
-%\IEEEoverridecommandlockouts
 
@@
 
-\title{Mining Scenario/Transaction Pairs HW/SW Co-verification Using Symbolic Execution}
+\title{Mining Scenario/Transaction Pairs in HW/SW Co-verification Using Symbolic Execution}
+
+\Omit{ % Double blind
+
+\author{
+\alignauthor
+Rajdeep Mukherjee\\
+       \affaddr{University of Oxford}\\
+       \email{rajdeep.mukherjee@cs.ox.ac.uk}
+%
+\alignauthor
+Saurabh Joshi \\
+  \affaddr{IIT, Hyderabad} \\
+  \email{sbjoshi@iith.ac.in}
+%
+\alignauthor
+John O'Leary \\
+  \affaddr{Intel Corporation, USA} \\
+  \email{john.w.oleary@intel.com}
+%
+\alignauthor
+Daniel Kroening \\
+  \affaddr{University of Oxford} \\
+  \email{kroening@cs.ox.ac.uk}
+%
+\alignauthor
+Tom Melham \\
+  \affaddr{University of Oxford} \\
+  \email{tom.melham@cs.ox.ac.uk}
+}
+%
+}
+
 %===============================================================================
@@
 We embody these techniques in our tools, \hwcbmcv and \verifox, respectively.
+
 A desirable characteristic of a co-verification model is the ability to exploit 
-the expressivity of the underlying reasoning engines, for example, constructing 
-a bit-level co-verification model for SAT solvers or a word-level model for SMT 
-solvers.  To this end, \hwcbmcv constructs a co-verification model through 
-in tandem symbolic execution of the HW and FW models.  A bit-level 
-netlist representation in And Inverter Graph (AIG) format or word-level netlist in
-format similar to SMT-LIB standards is synthesized from a HW Register Transfer 
-Level (RTL) implementation. Similarly, the SW, given in C, is automatically 
-translated into a Static Single Assignment (SSA) form.  A monolithic verification 
-condition is generated from these two models which is then solved using a 
-satisfiability solver.  Whereas, a co-verification model in \verifox is constructed 
-by first translating the RTL description into a software representation in C followed 
-by sequentializing the hardware and firmware models.  This results in a single
+the expressivity of the underlying reasoning engines.  To this end, \hwcbmcv
+constructs either a bit-level co-verification model that are checked with a SAT solvers 
+or a word-level model that are checked with SMT solvers.  Whereas, a 
+co-verification model in \verifox is constructed 
+by first translating the RTL description into a software representation in C,
+called \emph{software netlist}, which is then followed by sequentializing the FW 
+model and the software netlist model.  This results in a single
 threaded sequential co-verification model which is represented in C. A path-wise 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-A co-verification models must enable the specification of system-level 
-properties across HW/SW boundaries for uncovering critical co-design bugs 
-and for effective co-verification.  Our co-specification models are 
-specified in C with the support of special primitive, called {\em next\_timeframe()}, 
-that can express temporal correlation between HW and FW events. The
-co-verification models in \hwcbmcv and \verifox can be easily verified against 
-the co-specification models.  The co-design properties expressed by 
-co-specification models are sufficiently expressive, amenable to 
-verification reuse and can be readily used in assertion-based verification.  
-%
+Lack of support for property specification in a HW/SW co-design is one of the
+stumbling blocks for the application of formal techniques in co-verification.  
+In this paper, we express a co-design property in C 
+with the support of special primitive, called {\em next\_timeframe()}, 
+that can express temporal correlation between HW and FW events. 
+The co-design properties captures the overall design intent that enables
+specification of system-level properties across HW/SW boundaries. Thus, 
+they are sufficiently expressive, amenable to verification reuse and can be 
+readily used in assertion-based verification.  Closest to our
+unified property specification for co-verification is the language
+\textit{xPSL}~\cite{xPSL} proposed by Xie et al., which is the extension of IEEE PSL.  
+Note that the co-verification models in \hwcbmcv and \verifox are fully compliant 
+with our specification language, hence easily verifiable.  
+%
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 A monolithic approach in \hwcbmcv is based on Bounded Model Checking~\cite{CKY03}, 
-hence it cannot exploit the infeasibility arising from scenario driven constrained 
-interaction behaviors.  Whereas, a path-based symbolic execution in 
-\verifox can automatically infer such Scenario/Transaction pairs and check their 
-validity using backend solvers.  We experimentally show that for building 
-effective and scalable formal co-verification tool, it is imperative to 
-automatically mine only relevant scenario/transaction pairs that occurs in 
-practical co-design environment. 
-%
+hence it cannot exploit the infeasibility arising from scenario driven
+partitioning of HW-FW interaction behaviors.  Whereas, a path-based symbolic 
+execution in \verifox can automatically infer such Scenario/Transaction 
+pairs and check their validity using backend solvers.  We experimentally 
+show that for building an effective and scalable formal co-verification tool, 
+it is imperative to automatically mine only relevant scenario/transaction 
+pairs that occurs in practical co-design environment. 
+%
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 patterns.  This drastically reduces the total number of interleavings 
-between a FW and HW threads and simplies the overall verification effort. 
+between a FW and HW threads and simplies the overall complexity of the 
+verification task. 
 %
@@
     -- 1) A \emph{monolithic} approach that clearly separates the symbolic
-    execution of hardware and firmware model and generates a monolithic SAT
-    formula for verification, 2) A \emph{path-based} approach that constructs a
-    unified co-verification model by sequentializing the hardware and firmware
-    models and generates multiple SAT formulas through combined symbolic
-    execution of the unified model.
+    execution of HW and FW model and generate a monolithic SAT query for 
+    verification purpose, 2) A \emph{path-based} approach that constructs
+    an unified sequential co-verification model from HW and FW models and
+    generates multiple SAT queries that encodes relevant scenario/transaction 
+    pairs using symbolic execution.  To the best of our knowledge, this is the 
+    first attempt to synthesize a pure software co-verification model from
+    C/RTL co-designs specifically targeted for formal analysis.
 
@@
     here~\footnote{https://drive.google.com/folderview?id=0BynC6sd-wTYgWVQ4bXNtRDB5a2c\&usp=sharing}.
-
-  \item We show that the proposed path-based approach translates the HW/SW co-verification problem
-     into a purely software verification problem.  Our experiments show that the representation
-     of the sequentialized unified co-verification model in software languages allows us to 
-     mine relevant transaction/snecario pairs for effective co-verification.  To the 
-     best of our knowledge, this is the first attempt to synthesize a pure
-     software model for co-verification purpose.
 
@@
 \begin{figure}[t]
-\scalebox{.55}{\import{figures/}{fw-hw-interleaving.pspdftex}}
+\scalebox{.50}{\import{figures/}{fw-hw-interleaving.pspdftex}}
 \caption{Some HW Transactions for UART
@@
 %
-%\textbf{Producer-consumer Interaction:}
+
+\textbf{Step 3: Sequentialization based on Producer-Consumer Interaction}
 %
@@
 %
-\textbf{Step 3: Property Driven Slicing of Co-verification Model}
+
+\textbf{Step 4: Property Driven Slicing of Co-verification Model}
 A property-driven slicing is performed on the unified model, $\mathcal{M}_{seq}$.  
@@
 as $next\_timeframe()$ and $set\_inputs()$ to model FW-HW communications.
+\rmcmt{
+To this end, \hwcbmcv constructs a co-verification model through 
+in tandem symbolic execution of the HW and FW models.  A bit-level 
+netlist representation in And Inverter Graph (AIG) format or word-level netlist in
+format similar to SMT-LIB standards is synthesized from a HW Register Transfer 
+Level (RTL) implementation. Similarly, the SW, given in C, is automatically 
+translated into a Static Single Assignment (SSA) form.  A monolithic verification 
+condition is generated from these two models which is then solved using a 
+}
 %

### 2017-04-04 verifox.tex
table for stats
restructure intro and approach 1

@@
-\textbf{Step 4: Mining Scenario/Transaction Pairs Using Symbolic Execution}
+\textbf{Step 5: Mining Scenario/Transaction Pairs Using Symbolic Execution}
 Given a co-verification model, $\mathcal{M}_{seq}$, a scenario, 
@@
 then $\mathcal{M}_{seq}$ is said to have violated the property. 
+\rmcmt{mark algo with FT and HT scenario transaction pair}
 

### 2017-04-04 paper.tex
section 3.1

@@
 
-\textbf{Step 2: Constructing Co-verification Model}
+\textbf{Step 2: Sequentialization based on Producer-Consumer Interaction}
+%
+A communicating pair of executions of 
+$\mathcal{FT}$ and $\mathcal{HT}$ is an {\em interaction}, which 
+takes place through shared variables (or shared registers)
+only.  An interaction is said to exhibit {\em producer-consumer}
+interaction pattern if 1) the set of variables $V$ written by 
+the execution of $\mathcal{FT}$ and and the set of variables 
+$V'$ written by the execution of $\mathcal{HT}$ are disjoint 
+($V \cap V' = \emptyset$), (2) and the executions 
+of $\mathcal{FT}$ and $\mathcal{HT}$ consumes values 
+in $V'$ and $V$, respectively.
+%
+Figure~\ref{fig:interleaving1} illustrates the FW-HW interaction pattern 
+for the UART IP. The FW CFG is shown in the left and the 
+HW RTL code snippet is shown in the right. We abuse notations and 
+represent $\mathcal{HT}$ in the form of RTL and $\mathcal{FT}$ as CFG
+for our illustration purpose. Here, $\mathcal{HT}$ is the producer of interrupt 
+status signal, $irq\_o$, which is read by $\mathcal{FT}$ in state $s_1$. 
+The signal $irq\_o$ is  triggered when transmitter buffer is 
+{\em EMPTY} or receiver buffer is {\em FULL}. 
+$\mathcal{HT}$ also produces interrupt status by writing to the 
+memory mapped register, $UART\_IS$, which is consumed by 
+$\mathcal{FT}$ in state $s_2$.  In another interaction, $\mathcal{HT}$
+sends a data-packet to $UART\_TR$ which is consumed by $\mathcal{FT}$ in state $s_7$.
+Similarly, $\mathcal{FT}$ is the producer of $data$, $(outb(data,UART\_TR))$, 
+in state $s_6$ which is consumed by $\mathcal{HT}$. These interaction patterns 
+between $\mathcal{HT}$ and $\mathcal{FT}$ is exploited to generate a 
+sequential unified {\em program netlist} model which is defined next.\\ \\
+%
+\begin{figure}[t]
+\scalebox{.55}{\import{figures/}{interleaving.pspdftex}}
+\caption{Producer Consumer Interactions Pattern
+\label{fig:interleaving1}}
+\end{figure}
+%
+
+\textbf{Step 3: Constructing Co-verification Model}
 An unified co-verification model is constructed by sequentializing 
@@
 
-\textbf{Step 3: Sequentialization based on Producer-Consumer Interaction}
-%
-A communicating pair of executions of 
-$\mathcal{FT}$ and $\mathcal{HT}$ is an {\em interaction}, which 
-takes place through shared variables (or shared registers)
-only.  An interaction is said to exhibit {\em producer-consumer}
-interaction pattern if 1) the set of variables $V$ written by 
-the execution of $\mathcal{FT}$ and and the set of variables 
-$V'$ written by the execution of $\mathcal{HT}$ are disjoint 
-($V \cap V' = \emptyset$), (2) and the executions 
-of $\mathcal{FT}$ and $\mathcal{HT}$ consumes values 
-in $V'$ and $V$, respectively.
-%
-%
-\begin{figure}[t]
-\scalebox{.55}{\import{figures/}{interleaving.pspdftex}}
-\caption{Producer Consumer Interactions Pattern
-\label{fig:interleaving1}}
-\end{figure}
-%
-
 \textbf{Step 4: Property Driven Slicing of Co-verification Model}
@@
 %=======================================================================================
-%\Omit{
-%\begin{figure}[tp]
-%\centering
-%\vspace*{0.3cm}
-%\scalebox{.50}{\import{figures/}{work-flow.pspdftex}}
-%\caption{Automated Slicing and Trace partitioning\label{fig:desc}}
-%\end{figure}
-%}
-\Omit{
-\begin{figure}[t]
-\tikzstyle{rblock}=[rounded corners,draw=black]
-\tikzstyle{block}=[draw=black]
-\begin{tikzpicture}
-
-\node (v2c) [rblock] {\scs{\emph{v2c}}};
-\node (snl) [block,below of=v2c] {\scs{Software-netlist}};
-\draw[->] (v2c) -- (snl);
-
-\node (HD) [above left=.3cm and .3cm of v2c] {\scs{\parbox{8em}{Hardware Design \\ (in Verilog)}}};
-\draw[->] (HD) -- (v2c);
-
-\node (prop) [above right=.3cm and .3cm of v2c] {\scs{\parbox{8em}{Property \\ (in SVA)}}};
-\draw[->] (prop) -- (v2c);
-
-\node (cmm) [block,below of=snl] {\scs{\parbox{9em}{Composite Monolithic Model}}};
-\draw[->] (snl) -- (cmm);
-
-\node (dcmm) [left=1cm of cmm] {};
-\node (fw) [above=.1cm of dcmm  ] {\scs{Firmware}};
-\node (as) [below=.1cm of dcmm] {\scs{Assumptions}};
-\draw[->] (fw) -- (cmm);
-\draw[->] (as) -- (cmm);
-
-\node (pds) [block,below of=cmm] {\scs{\parbox{8em}{Property-driven slicing}}};
-\draw[->] (cmm) -- (pds);
-
-\node (tp) [block,below=.8cm of pds] {\scs{Trace partitioning}};
-\node (iss) [block,below right=.5cm  and .05cm of tp.east] {\scs{\parbox{6em}{Incremental SAT solving}}};
-\node (sat) [rblock,below=1.5cm of tp] {\scs{SAT solver}};
-\node (ipp) [block,left=2cm of iss] {\scs{\parbox{6em}{Infeasible path pruning}}};
-
-\draw [<->] (tp) -- (iss);
-\draw [<->] (tp) -- (ipp);
-\draw [<->] (sat) -- (iss);
-\draw [<->] (sat) -- (ipp);
-
-\node (vfbox) [rblock,fit={(tp) (iss) (sat) (ipp)}] {};
-\draw[->] (pds) -- (vfbox);
-
-\node (verifox) [right=.2cm of tp] {\scs{{\bf \verifox}}};
-
-\node (safe) [above right=.2cm and .2cm of vfbox.east] {\scs{Verification Successful}};
-\node (unsafe) [below right=.2cm and .2cm of vfbox.east] {\scs{\parbox{8em}{Verification Failed (Counterexample)}}};
-
-\draw[->] (vfbox.9) -- (safe);
-\draw[->] (vfbox.-12) -- (unsafe);
-
-\end{tikzpicture}
-\caption{Automated Slicing and Trace partitioning\label{fig:desc}}
-\end{figure}
-}
-%
 \input{verifox}
@@
 \end{figure}
-
+%
 Figure~\ref{fig:conventional} illustrates the conventional approach to HW/SW
@@
 for all our experiments was set to 2~hours.  
+%
+
+\textit{\textbf{State-of-the-art Co-verification tools:}} 
+%There exists plethora of tools for either SW verification or HW verification.
+%
+Despite extensive use of model checking and other formal methods in 
+SW verification or HW verification domain, building automated 
+co-verification tools using formal methods has received 
+little attention in the past.  We are not aware of any automated 
+formal co-verification tool in the literature that can readily accept 
+co-designs written in C and Verilog RTL. In this paper, we address this gap. 
 %
@@
 % ===============================================================================
+\section{Limitations of Proposed Approach}
+% ===============================================================================
+
+% ===============================================================================
 \section{Related work}

### 2017-04-04 paper.tex
table1

@@
 \usepackage{multirow}
+\usepackage{mathtools}
 \usepackage[algo2e,linesnumbered,ruled,lined]{algorithm2e}
@@
 verification process.  
-However, we observe that in practise, industrial co-designs exhibits 
+However, we observe that in practise that, industrial co-designs exhibits 
 producer-consumer
@@
 to $Out$, $Seq$ and $Comb$. Figure~\ref{ex1} shows an example of 
-translating a Verilog RTL circuit with an always block and continuous
-assignment statement into an equivalent C program.
+Verilog RTL circuit containing an always block and continuous
+assignment statement and the equivalent software netlist in C.
 %
@@
 \centering
-\begin{tabular}{l|l|l|l}
+\begin{tabular}{|l|l|l|l|}
 \hline
@@
 
-\textbf{Step 2: Sequentialization based on Producer-Consumer Interaction}
+\textbf{Step 2: Sequentialization based on Transaction Interaction}
+%
+Concurrency is at the heart of co-verification.  Testing concurrent 
+threads requires exploring all possible interleavings between a HW 
+and FW thread.  The number of interleavings could be potentially 
+exponential.  However,~\cite{codes14,hvc} showed that the 
+interaction between a FW thread and HW thread follows a 
+producer-consumer relationship. That is, a FW 
+thread is mostly independent of the HW thread they interact with~\cite{hvc,codes14}.  
+Specifically, a FW thread is only responsible for configuring the 
+HW transactions by writing to memory mapped registers or polling 
+the interrupt status register for data transmission or receiving 
+incoming data packets.
+
+Furthermore, we observe producer-consumer interaction pattern 
+in many practical industrial co-designs, such as IBM 
+Text Accelerator co-design~\cite{polig2014micro,polig2014fpl}, 
+IBM coherent FFT coprocessor~\cite{giefers2015accelerating}, RockBox 
+Media Player~\cite{hvc}, linux device driver interacting with QEMU emulated
+hardware code~\cite{codes14}.
+
+%This interaction pattern exhibits producer-consumer 
+%relationship, which is also evident in case of our UART example in 
+%Figure~\ref{fig:interleaving1}.  
 %
@@
 %
-Figure~\ref{fig:interleaving1} illustrates the FW-HW interaction pattern 
-for the UART IP. The FW CFG is shown in the left and the 
+Figure~\ref{fig:interleaving1} illustrates the producer-consumer relationship 
+in UART IP. The FW CFG is shown in the left and the 
 HW RTL code snippet is shown in the right. We abuse notations and 
@@
 Similarly, $\mathcal{FT}$ is the producer of $data$, $(outb(data,UART\_TR))$, 
-in state $s_6$ which is consumed by $\mathcal{HT}$. These interaction patterns 
-between $\mathcal{HT}$ and $\mathcal{FT}$ is exploited to generate a 
-sequential unified {\em program netlist} model which is defined next.\\ \\
+in state $s_6$ which is consumed by $\mathcal{HT}$.  
 %
@@
 %
-
-\textbf{Step 3: Constructing Co-verification Model}
+\begin{table}
+\begin{center}
+{\scriptsize
+\begin{tabular}{|c|c|c|}
+\hline
+  Firmware & Hardware  \\
+  Transaction ($\mathcal{ST}$) & Transaction ($\mathcal{HT}$) \\ 
+\cline{1-2}
+   $s_1 \xrightarrow[]{irq_o} s_2 \xrightarrow[\mathcal{C}]{inb()} s_4
+   \xrightarrow[]{status == 0x0c} s_6 \xrightarrow[\mathcal{P}]{outb()} s_9 \rightarrow
+   s_{11} \rightarrow s_{12}$  & $s_2 \xrightarrow[\mathcal{C}]{inb()} s_4\;\; uart\_{rx}$
+   \\ 
+   & $s_6 \xrightarrow[]{outb()} s_9\;\; uart\_{tx}$ \\  \hline
+
+   $s_1 \xrightarrow[]{irq_o} s_2 \xrightarrow[\mathcal{C}]{inb()} s_4
+   \xrightarrow[]{status \neq 0x0c} s_7 \xrightarrow[\mathcal{C}]{inb()} s_{10} \rightarrow
+   s_{11} \rightarrow s_{12}$  & $s_2 \xrightarrow[\mathcal{C}]{inb()} s_4\;\; uart\_{rx}$
+   \\ 
+   & $s_7 \xrightarrow[]{outb()} s_{10}\;\; uart\_{rx}$ \\  \hline
+
+   $s_1 \xrightarrow[]{\neg irq_o} s_3 \xrightarrow[]{wb\_{idle()}}
+   s_5 \xrightarrow[]{wb\_{idle()}} s_8 \rightarrow
+   s_{12}$ & $s_3 \xrightarrow[]{wb\_{idle()}} s_5\;\; uart\_{top}$ \\ 
+   & $s_5 \xrightarrow[]{wb\_{idle()}} s_8\;\; uart\_{top}$ \\  \hline
+\end{tabular}
+}
+\end{center}
+\caption{\scriptsize Firmware Transactions and its interacting HW transaction}
+\label{table:stats}
+\end{table}  
+%
+This interaction behavior can be analysed 
+to produce a sequential single-threaded co-verification model.
+
+\textbf{Step 3: Co-verification Model}
 An unified co-verification model is constructed by sequentializing 
 HW and its interacting FW threads, thereby generating a sequential 
-single-threaded co-verification model in C.  The motivation behind
-sequentialization is based on our observation that many practical industrial
-co-designs exhibit producer-consumer interaction behavior, such as IBM 
-Text Accelerator co-design~\cite{polig2014micro,polig2014fpl}, 
-IBM coherent FFT coprocessor~\cite{giefers2015accelerating}, RockBox 
-Media Player~\cite{hvc}, linux device driver interacting with QEMU emulated
-hardware code~\cite{codes14} and others.  We observe that in practise, a FW 
-thread is mostly independent of the HW thread they interact with~\cite{hvc,codes14}.  
-Specifically, a FW thread is only responsible for configuring the 
-HW transactions by writing to memory mapped registers or polling 
-the interrupt status register for data transmission or receiving 
-incoming data packets. This interaction pattern exhibits producer-consumer 
-relationship, which is also evident in case of our UART example in 
-Figure~\ref{fig:interleaving1}.  
+single-threaded co-verification model in C.  
 %

### 2017-04-04 paper.tex
section 3.2

@@
 %
+Table~\ref{transaction} shows the FW transactions $(\mathcal{FT})$ and its 
+interacting HW transactions $(\mathcal{HT})$ from Figure~\ref{fig:interleaving1}. 
+The description above the arrows 
+in column 1 shows the events in $\mathcal{FT}$ and the letter below the
+arrows denotes the event type, producer $(\mathcal{P})$ or consumer 
+$(\mathcal{C})$. Arrows with empty description below denotes reading of interface
+variables or local variables in $\mathcal{FT}$.  Arrows with no description
+simply denotes control-flow with no events.  The entires in the right column of
+Table~\ref{transaction} shows the corresponding transaction in HW modules. We
+simply denote a transaction in HW module with the name of the module,
+transmitter module in UART ($uart\_tx$), receiver module in UART ($uart\_rx$), or
+the top UART module ($uart\_top$).
+%
 \begin{table}
@@
 \caption{\scriptsize Firmware Transactions and its interacting HW transaction}
-\label{table:stats}
+\label{transaction}
 \end{table}  
 %
-This interaction behavior can be analysed 
-to produce a sequential single-threaded co-verification model.
 
 \textbf{Step 3: Co-verification Model}
-An unified co-verification model is constructed by sequentializing 
-HW and its interacting FW threads, thereby generating a sequential 
-single-threaded co-verification model in C.  
-%
-We now formally define a single-threaded sequential co-verification model, 
-denoted by $\mathcal{M}_{seq}$, obtained by sequentializing the HW and FW 
-models.
+An unified co-verification model is constructed by instrumenting  
+the software netlist model of HW RTL inside the FW thread, thereby 
+generating a sequential single-threaded co-verification model in C.  
+%
+We now formally define a our co-verification model, denoted by 
+$\mathcal{M}_{seq}$.\rmcmt{refer moduleName} as software netlist.
 %

### 2017-04-05 paper.tex
psl

@@
 %===============================================================================
+\section{Property Specification for Co-verification}
+%===============================================================================
+Lack of support for property specification in a HW/SW co-design is one of the
+stumbling blocks for the application of formal techniques in co-verification.  
+In this paper, we express a co-design property in C 
+with the support of special primitive, called {\em next\_timeframe()}, 
+that can express temporal correlation between HW and FW events. 
+In this paper, we classify co-design properties into two 
+classes -- {\em transaction-level} property and {\em component-level} property.
+%-------------------------------------------------------------------------------
+\subsection{Transaction-level Property}
+%-------------------------------------------------------------------------------
+A {\em Transaction-level} property ($\psi_{t}$) formally captures the 
+design intent of the interaction between a $\mathcal{ST}$ and $\mathcal{HT}$, 
+that is, it is defined at the transaction boundaries.  
+Recall that a $\mathcal{ST}$ is a service in response to some external environment 
+or HW interrupts (for example acknowledgement or exceptions). Similarly, 
+$\mathcal{HT}$ is a finite-length service in response to some SW events or 
+other HW events.
+
+Thus, a transaction-level property follows implication structure -- the 
+antecedent of the implication is an event in $\mathcal{ST}$ or 
+$\mathcal{HT}$ and the consequent is an event in $\mathcal{HT}$ 
+or $\mathcal{ST}$ respectively.  An event in $\mathcal{ST}$ may be 
+a function call or an update to program variables. Similarly, an event in 
+$\mathcal{HT}$ corresponds to an update of combinational or sequential 
+elements. \rmcmt{example}
+
+%-------------------------------------------------------------------------------
+\subsection{Component-level Property}
+%-------------------------------------------------------------------------------
+A {\em component-level} property ($\psi_{c}$) is defined purely at the 
+level of individual components of a co-design system. Recall that a component 
+may be a HW model, a SW model or an interface model which contains only the 
+interface logic.  A component-level property captures the design intent of a 
+component in terms of its input/output behaviors.  This type of property 
+is useful in a co-design environment for verifying individual components.   
+Note that unlike the structure of $\psi_{t}$ which requires the antecedent 
+or consequent to be a HW or SW event,  $\psi_{c}$ only contains signals 
+(ports) or variables of a particular component. \rmcmt{example}
+
+%===============================================================================
 \section{Experimental Results}
@@
 % ===============================================================================
+The primary motivation for constructing a sequential single threaded unified 
+co-verification model is to avoid enumerating exponential number of interleavings 
+between the HW and FW threads.  We have shown that this is extremely beneficial for 
+co-designs that exhibits producer-consumer relationship.  To this end, we construct 
+a sequential co-verification model in \verifox through appropriate composition of 
+HW and FW threads.  Our path-based algorithm in \verifox is able to suitably exploit 
+this interaction behavior in a sequential co-verification model through symbolic 
+execution by generating relevant scenario/transaction pairs.  However, this approach 
+is not applicable for co-designs that exhibits true concurrency~\cite{concurrency}, 
+that is, a FW its interacting HW threads does not show producer-consumer relationship.
 

### 2017-04-05 paper.tex
limitation

@@
 \begin{figure*}[t]
-\scriptsize  
+%\scriptsize  
 \centering
@@
 struct state_elements_top  u1;
-void top(unsigned int clk, 
-   unsigned int a) {
+void top(_Bool clk, unsigned a) {
   _Bool c,cond;
@@
     u1.e = 0;
-  u1.d = c;  }
+  u1.d = c;  
+}
 \end{lstlisting}
@@
 \begin{center}
-{\scriptsize
+{
+ %\scriptsize
 \begin{tabular}{|c|c|c|}
@@
 \end{center}
-\caption{\scriptsize Firmware Transactions and its interacting HW transaction}
+\caption{Firmware Transactions and its interacting HW transaction}
 \label{transaction}
@@
 \textbf{Step 3: Co-verification Model}
-An unified co-verification model is constructed by instrumenting  
-the software netlist model of HW RTL inside the FW thread, thereby 
-generating a sequential single-threaded co-verification model in C.  
+An unified co-verification model is constructed through appropriate composition of 
+FW and its interacting HW threads.  This is done by instrumenting the 
+software netlist model of HW RTL inside the FW thread at every invocation 
+of the interface functions.  This leads to a single-threaded sequential
+co-verification model in C.  
 %
@@
 (input, output and inout ports) are declared inside the 
-FW to communicate with $\mathcal{SN}$. \\ 
+FW to communicate with $\mathcal{SN}$. \rmcmt{explain instrumentation with
+diagram} \\ 
 %
@@
 \begin{center}
-{\scriptsize
+{
+%\scriptsize
 \begin{tabular}{|c|c|c|c|c|c|c|}
@@
 \end{center}
-\caption{\scriptsize Design statistics for UART IP and SoC Design}
+\caption{Design statistics for UART IP and SoC Design}
 \label{table:stats}
@@
 {
-\begin{scriptsize}
+%\begin{scriptsize}
 \begin{tabular}{|l|l|l|l|l|l|l|l|l|l|}
@@
 \end{tabular}
-\end{scriptsize}
+%\end{scriptsize}
 }
@@
 {
-\begin{scriptsize}
+%\begin{scriptsize}
 \begin{tabular}{|l|l|l|l|l|l|l|l|}
@@
 between the HW and FW threads.  We have shown that this is extremely beneficial for 
-co-designs that exhibits producer-consumer relationship.  To this end, we construct 
-a sequential co-verification model in \verifox through appropriate composition of 
-HW and FW threads.  Our path-based algorithm in \verifox is able to suitably exploit 
+co-designs that exhibits producer-consumer relationship.  
+In particular, our path-based algorithm in \verifox is able to suitably exploit 
 this interaction behavior in a sequential co-verification model through symbolic 
-execution by generating relevant scenario/transaction pairs.  However, this approach 
+execution which generates relevant scenario/transaction pairs.  However, this approach 
 is not applicable for co-designs that exhibits true concurrency~\cite{concurrency}, 
 that is, a FW its interacting HW threads does not show producer-consumer relationship.  
+In this case, it is imperative to consider all possible interleavings between
+these threads in some effecient manner.  However, our experience is that such 
+co-designs occurs rarely in practise.
 

### 2017-04-05 paper.tex
minor changes

@@
 
-  \item We present two approaches for formal hardware/software co-verification
+  \item \textbf{Monolithic versus Path-based:} We present two approaches for formal hardware/software co-verification
     -- 1) A \emph{monolithic} approach that clearly separates the symbolic
@@
     generates multiple SAT queries that encodes relevant scenario/transaction 
-    pairs using symbolic execution.  To the best of our knowledge, this is the 
-    first attempt to synthesize a pure software co-verification model from
-    C/RTL co-designs specifically targeted for formal analysis.
-
-  \item We present an automatic HW/SW co-verifcation tool called, \hwcbmcv,
+    pairs using symbolic execution.
+
+    To the best of our knowledge, this is the first attempt to synthesize a pure 
+    software co-verification model from C/RTL co-designs specifically targeted 
+    for formal analysis.
+
+  \item \textbf{Co-verification Tools:} We present an automatic HW/SW co-verification tool called, \hwcbmcv,
     which follows the monolithic verification technique.  Our path-based 
@@
 
-   \item We present an unified property specification language for
-     co-verification that allows engineers to write meaningful 
+  \item \textbf{Property Specification Language:} We present an unified property
+    specification language for co-verification that allows engineers to write meaningful 
      formal co-specification over hardware and firmware events and specify
@@
 
-\textbf{Co-specification Model} We verify that the transmitted data is the same as the 
+\textbf{Co-design Property} We verify that the transmitted data is the same as the 
 received data in the {\em loopback} mode.  To do so, we annotate the FW model 
@@
 %
+\section{Scenario and Transaction}
+%
 We formally describe the notion of \emph{transaction} and \emph{scenario} with the
@@
 \scriptsize
-\begin{tabular}{l|l}
+\begin{tabular}{|l|l|}
 \hline
@@
 \begin{figure*}[t]
-%\scriptsize  
+\scriptsize  
 \centering
@@
 %
+
 Figure~\ref{fig:interleaving1} illustrates the producer-consumer relationship 
@@
 {
- %\scriptsize
+ \scriptsize
 \begin{tabular}{|c|c|c|}
@@
 \includegraphics[scale=0.6]{figures/traditional_flow.pdf}
-\caption{Conventional HW/SW Co-verification Flow}
+\caption{Monolithic HW/SW Co-verification Flow}
 \label{fig:conventional}
@@
 {
-%\scriptsize
+\scriptsize
 \begin{tabular}{|c|c|c|c|c|c|c|}
@@
 %
-\textbf{Firmware Hardware Interaction Pattern in UART}
-Figure~\ref{fig:interleaving1} illustrates the FW-HW interaction pattern 
-for the UART IP. The FW CFG is shown in the left and the 
-HW RTL code snippet is shown in the right. We abuse notations and 
-represent $\mathcal{HT}$ in the form of RTL and $\mathcal{FT}$ as CFG
-for our illustration purpose. Here, $\mathcal{HT}$ is the producer of interrupt 
-status signal, $irq\_o$, which is read by $\mathcal{FT}$ in state $s_1$. 
-The signal $irq\_o$ is  triggered when transmitter buffer is 
-{\em EMPTY} or receiver buffer is {\em FULL}. 
-$\mathcal{HT}$ also produces interrupt status by writing to the 
-memory mapped register, $UART\_IS$, which is consumed by 
-$\mathcal{FT}$ in state $s_2$.  In another interaction, $\mathcal{HT}$
-sends a data-packet to $UART\_TR$ which is consumed by $\mathcal{FT}$ in state $s_7$.
-Similarly, $\mathcal{FT}$ is the producer of $data$, $(outb(data,UART\_TR))$, 
-in state $s_6$ which is consumed by $\mathcal{HT}$. Thus, the interaction
-pattern between $\mathcal{HT}$ and $\mathcal{FT}$ clearly exhibits producer-consumer
-relationship. This enables us to sequentialize the HW and FW thread. \\
 \rmcmt{stats in a table, remove klee result, SoC diagram}
@@
 {
-%\begin{scriptsize}
+\begin{scriptsize}
 \begin{tabular}{|l|l|l|l|l|l|l|l|l|l|}
@@
 \end{tabular}
-%\end{scriptsize}
+\end{scriptsize}
 }

### 2017-04-05 paper.tex
unified model

@@
 FW running on a processor could be much faster than the HW
-model it interacts with, 2) lack of co-specification model that precisely
-captures the design intent of the communication between HW and FW, 3) Large
+model it interacts with, 2) lack of support for property specification in 
+HW/FW co-designs that can precisely capture the design intent of the 
+communication between HW and FW, 3) Large
 number of interleavings between HW and FW threads, and 4) lack 
@@
 instead of register-transfer level implementation, 2) the HW-FW model
-construction is agnostic to the underlying reasoning engine, 3) does not
-leverage the co-specification model, hence ineffective for practical
-co-verification.  We will call the unified FW-HW model as \emph{co-verification model}.
+construction is agnostic to the underlying reasoning engine, and 3) 
+does not leverage the property specification over HW-FW boundary, hence 
+ineffective for practical co-verification.  We will call the unified FW-HW 
+model as \emph{co-verification model}.
 
@@
 
+\textbf{Interface functions} The \emph{interface functions} are lowest level of 
+implementation in a FW model that directly read from or write to the HW ports. 
+For example, the interface functions in figure~\ref{firmware} are the $wb$ class
+of functions that directly wiggles the input/output ports of UART HW.
+
 \textbf{Hardware Model} Figure~\ref{fig:interleaving2} shows a fragment of the state machine 
@@
 and $outb$ function calls which directly read from and write to the UART IP ports
-respectively. \rmcmt{more on co-specification PSL}. 
+respectively. Section~\ref{property} describes the property specification in
+HW-FW co-designs in more details. 
 \[
@@
 satisfaction~\cite{leo-thesis}.  To the best of our knowledge, this is the first 
-attempt that demonstrate the efficacy of such translation in the context of 
+attempt to demonstrate the efficacy of such translation in the context of 
 hardware/software co-verification. 
@@
 variables or local variables in $\mathcal{FT}$.  Arrows with no description
-simply denotes control-flow with no events.  The entires in the right column of
-Table~\ref{transaction} shows the corresponding transaction in HW modules. We
-simply denote a transaction in HW module with the name of the module,
+simply denotes control-flow join.  The entries in the right column of
+Table~\ref{transaction} shows the corresponding transactions in HW.  We 
+denote a transaction in HW module with the name of the module,
 transmitter module in UART ($uart\_tx$), receiver module in UART ($uart\_rx$), or
@@
 \textbf{Step 3: Co-verification Model}
+%
 An unified co-verification model is constructed through appropriate composition of 
@@
 software netlist model of HW RTL inside the FW thread at every invocation 
-of the interface functions.  This leads to a single-threaded sequential
-co-verification model in C.  
+of the $next\_timeframe()$ primitive in the interface functions.  Recall that a
+call to $next\_timeframe()$ is used to advance the HW clock by one cycle. A call
+to the software netlist emulates the same effect.  Furthermore, a software
+netlist is a sequential model of the HW RTL represented in C.  Thus, the
+composition leads to a single-threaded sequential co-verification model in C.  
 %
 We now formally define a our co-verification model, denoted by 
-$\mathcal{M}_{seq}$.\rmcmt{refer moduleName} as software netlist.
+$\mathcal{M}_{seq}$.
 %
@@
 $\mathit{moduleName(Var_1,\dots,Var_n)}$ invokes the top level 
-procedure of the $\mathcal{SN}$. Recall that $\mathcal{SN}$ is a
-software netlist representation of HW RTL models.
-The interface variables $\{Var\_1,\dots,Var\_n\}$ 
+procedure of $\mathcal{SN}$, which is also the top level 
+module of the HW RTL, since the translation from RTL to software preserves
+the module hierarchy.  The interface variables $\{Var\_1,\dots,Var\_n\}$ 
 (input, output and inout ports) are declared inside the 
-FW to communicate with $\mathcal{SN}$. \rmcmt{explain instrumentation with
-diagram} \\ 
+FW to communicate with $\mathcal{SN}$.  Figure~\ref{compose} shows the 
+composition of $\mathcal{SN}$ and FW thread for the UART IP.
 %
@@
 %===============================================================================
-\section{Property Specification for Co-verification}
+\section{Property Specification for Co-verification}\label{property}
 %===============================================================================

### 2017-04-05 paper.tex
section 3.1
monolithic approach

@@
 software netlist model of HW RTL inside the FW thread at every invocation 
-of the $next\_timeframe()$ primitive in the interface functions.  Recall that a
+of the $next\_timeframe()$ primitive in interface functions.  Recall that a
 call to $next\_timeframe()$ is used to advance the HW clock by one cycle.  A call
-to the software netlist emulates the same effect.  Furthermore, a software
-netlist is a sequential model of the HW RTL represented in C.  Thus, the
+to the software netlist emulates the effect of one clock period in the RTL 
+model. That is, the state of state holding elements (registers) and combinational 
+elements (wires) are uniform in software netlist and RTL model after every invocation of 
+$next_timeframe()$.  Furthermore, a software
+netlist is a sequential model of HW RTL which is represented in C.  Thus, the
 composition leads to a single-threaded sequential co-verification model in C.  
@@
 %
+%\begin{figure}[t]
+%\scalebox{.50}{\import{figures/}{compose.pspdftex}}
+%  \caption{Composition of FW and HW threads}
+%\label{fig:interleaving2}
+%\end{figure}
+%
 
@@
 %
-Figure~\ref{fig:conventional} illustrates the conventional approach to HW/SW
-co-veri\-fi\-cation, as implemented in the state-of-the-art co-verification
-tool, \hwcbmcv~\cite{CKY03,vlsid13}.  \hwcbmcv is the only open-source
-formal co-verification tool that supports Verilog RTL (System Verilog 2009
-standard) and C/C++ firmware.  In contrast to our proposed approach,
+Figure~\ref{fig:conventional} illustrates the monolithic approach to HW/SW
+co-veri\-fi\-cation, as implemented in \hwcbmcv.  
+%\hwcbmcv is the only open-source
+%formal co-verification tool that supports Verilog RTL (System Verilog 2009
+%standard) and C/C++ firmware.  
+In contrast to path-based approach,
 \hwcbmcv maintains two separate flows for HW and FW.  The top flow in
 Figure~\ref{fig:conventional} uses synthesis to obtain either a bit-level or
-a word-level netlist from Verilog RTL.  The bottom flow illustrates the
-translation of the C program into static single assignment (SSA) form. 
+a word-level netlist from Verilog RTL.  A bit-level netlist is represented 
+in And Inverter Graph (AIG) format.  Whereas, a word-level netlist is represented 
+in format that resembles SMT-LIB standards.  The bottom flow illustrates the
+translation of C program into static single assignment (SSA) form. 
+Synthesizing netlist from RTL is a standard technique which is widely 
+used in hardware model checkers~\cite{}. Similarly, translating a C program 
+into a SSA representation is a standard technique which is widely used in 
+software verification tools, such as CBMC~\cite{}, 2LS~{}. 
 These two flows meet only at the solver.  Thus, \hwcbmcv generates a
-monolithic formula from the C and RTL description, which is then checked
-with SAT/SMT solvers.  \hwcbmcv provides specific handshake primitives such
+unified monolithic co-verification model from AIG and SSA which is 
+represented in Conjunctive Normal Form (CNF).  This model is then used to perform 
+bounded model checking~\cite{} using the underlying SAT/SMT solvers.  
+\hwcbmcv provides specific handshake primitives such
 as $next\_timeframe()$ and $set\_inputs()$ to model FW-HW communications.
+
 \rmcmt{

### 2017-04-06 paper.tex
minor
statement reordering for better flow

@@
 of the hardware RTL from the behavior expected by the software.  Formal
-methods can deliver proof that the RTL and the firmware match, but are
+methods can deliver a proof that the RTL and the firmware match, but are
 difficult to scale up.  We propose to identify partitions of the firmware and
@@
 conventional approach, which constructs a single monolithic SAT/SMT
-instance, and observe speedups of an order of magnitude over conventional 
+instance, and observe speedup of an order of magnitude over conventional 
 approach for proving safety properties as well as detecting firmware/hardware bugs.
@@
 of the final HW, and addresses concerns related to power, area and
-timing.  Verification is mandatory to assert that the driver or firmware (FW) 
-is executed correctly together with the RTL.  The effectiveness of testing 
-is thus severely limited in post-RTL co-verification.
+timing.  The effectiveness of testing 
+is thus severely limited in post-RTL co-verification. Verification is mandatory to ensure that the driver or firmware (FW) 
+is executed correctly together with the RTL.
 

### 2017-04-06 paper.tex
articles, capitalization

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The verification of FW given in C/C++ together with the RTL given in a hardware
-description language (HDL) such as Verilog/VHDL is a challenging task due to 
+The verification of a FW given in C/C++ together with an RTL given in a hardware
+description language (HDL) such as Verilog/VHDL is a challenging task due to a
 few reasons -- 1) the timing and semantic mismatch between the synchronous
-clock-driven HW model and asynchronous event-driven SW model -- for example,
+clock-driven HW model and asynchronous event-driven SW model. For example, the
 FW running on a processor could be much faster than the HW
@@
 HW/FW co-designs that can precisely capture the design intent of the 
-communication between HW and FW, 3) Large
+communication between HW and FW, 3) large
 number of interleavings between HW and FW threads, and 4) lack 

### 2017-04-06 paper.tex
rephrase and minor

@@
 Generating a unified FW-HW model for co-verification is a 
-well-known phenomenon to handle the semantic mismatch between the 
+well-known phenomenon to handle the semantic mismatch between  
 HW~\footnote{Note that whenever we refer to ``hardware'' 
@@
 useful in practise for three reasons -- 1) use of abstract HW models 
-instead of register-transfer level implementation, 2) the HW-FW model
+instead of RTL implementation, 2) the HW-FW model
 construction is agnostic to the underlying reasoning engine, and 3) 
-does not leverage the property specification over HW-FW boundary, hence 
+it does not leverage the property specification over HW-FW boundary, hence 
 ineffective for practical co-verification.  We will call the unified FW-HW 
@@
 A desirable characteristic of a co-verification model is the ability to exploit 
-the expressivity of the underlying reasoning engines.  To this end, \hwcbmcv
-constructs either a bit-level co-verification model that are checked with a SAT solvers 
-or a word-level model that are checked with SMT solvers.  Whereas, a 
+the expressiveness of the underlying reasoning engines.  To this end, \hwcbmcv
+constructs either a bit-level co-verification model that is checked with a SAT solver 
+or a word-level model that is checked with an SMT solver.  Whereas, a 
 co-verification model in \verifox is constructed 
@@
 symbolic execution is then performed over the co-verification model to
-automatically mine relevant interaction behaviors between the FW and HW models.
+automatically mine relevant interactions between the FW and HW models.
 

### 2017-04-06 paper.tex
minor

@@
 Note that the co-verification models in \hwcbmcv and \verifox are fully compliant 
-with our specification language, hence easily verifiable.  
+with our specification language, hence easily amenable to verification.
 %
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-A firmware only exercise some fragment of hardware state-space in a typical 
+A firmware only exercises a fraction of the hardware state-space in a typical 
 hardware/software
@@
 restricts the interaction between $\mathcal{FT}$ and $\mathcal{HT}$.  In
-other words, given a scenario $\mathcal{S}$, the FW only exercises a fragment
+other words, given a scenario $\mathcal{S}$, the FW exercises only a fragment
 of the HW state-space.  This renders many interactions between
@@
 UART in \emph{transmitter} mode which restricts the communication between the FW 
-and HW to set of services that only transfers data from the FW to the serial output 
+and HW to set of services that only transfer data from the FW to the serial output 
 port of the transmitter HW while completely bypassing the receiver HW.  
@@
 it is imperative to automatically mine only relevant scenario/transaction 
-pairs that occurs in practical co-design environment. 
+pairs that occur in practical co-design environment. 
 %

### 2017-04-06 paper.tex
minor

@@
 verification process.  
-However, we observe that in practise that, industrial co-designs exhibits 
+However, we observe that in practice, industrial co-designs exhibit 
 producer-consumer
-relationship~\cite{polig2014micro,polig2014fpl,giefers2015accelerating} --
+relationships~\cite{polig2014micro,polig2014fpl,giefers2015accelerating} --
 the master module (producer) solely updates the shared registers which are
 consumed by the slave (consumer).  This key observation allows us to
-sequentialize concurrent FW and HW models following specific interaction
+sequentialize concurrent FW and HW models \sjcmt{transactions instead of models?} that follow specific interaction
 patterns.  This drastically reduces the total number of interleavings 
@@
     co-designs where the hardware is implemented in Verilog RTL (IEEE
-    SystemVerilog 2005 standards) and firmware is  
+    SystemVerilog 2005 standards) and the firmware is  
     specified in ANSI-C (C89, C99 standards).  We distribute the HW/SW 
@@
 
-  \item \textbf{Property Specification Language:} We present an unified property
+  \item \textbf{Property Specification Language:} We present a unified property
     specification language for co-verification that allows engineers to write meaningful 
      formal co-specification over hardware and firmware events and specify
-     temporal correlation between these events.  Our tool also supports a
+     temporal correlations between these events.  Our tool also supports a
      fragment of IEEE Property Specification Language.

### 2017-04-06 paper.tex
composition figure

--- 2017-04-06 paper.tex
@@
 conventional approach, which constructs a single monolithic SAT/SMT
-instance, and observe speedup of an order of magnitude over conventional 
+instance, and observe speedups of an order of magnitude over conventional 
 approach for proving safety properties as well as detecting firmware/hardware bugs.
@@
 of the final HW, and addresses concerns related to power, area and
-timing.  The effectiveness of testing 
-is thus severely limited in post-RTL co-verification. Verification is mandatory to ensure that the driver or firmware (FW) 
-is executed correctly together with the RTL.
+timing.  Verification is mandatory to assert that the driver or firmware (FW) 
+is executed correctly together with the RTL.  The effectiveness of testing 
+is thus severely limited in post-RTL co-verification.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The verification of a FW given in C/C++ together with an RTL given in a hardware
-description language (HDL) such as Verilog/VHDL is a challenging task due to a
+The verification of FW given in C/C++ together with the RTL given in a hardware
+description language (HDL) such as Verilog/VHDL is a challenging task due to 
 few reasons -- 1) the timing and semantic mismatch between the synchronous
-clock-driven HW model and asynchronous event-driven SW model. For example, the
+clock-driven HW model and asynchronous event-driven SW model -- for example,
 FW running on a processor could be much faster than the HW
@@
 HW/FW co-designs that can precisely capture the design intent of the 
-communication between HW and FW, 3) large
+communication between HW and FW, 3) Large
 number of interleavings between HW and FW threads, and 4) lack 
@@
 Generating a unified FW-HW model for co-verification is a 
-well-known phenomenon to handle the semantic mismatch between  
+well-known phenomenon to handle the semantic mismatch between the 
 HW~\footnote{Note that whenever we refer to ``hardware'' 
@@
 useful in practise for three reasons -- 1) use of abstract HW models 
-instead of RTL implementation, 2) the HW-FW model
+instead of register-transfer level implementation, 2) the HW-FW model
 construction is agnostic to the underlying reasoning engine, and 3) 
-it does not leverage the property specification over HW-FW boundary, hence 
+does not leverage the property specification over HW-FW boundary, hence 
 ineffective for practical co-verification.  We will call the unified FW-HW 
@@
 A desirable characteristic of a co-verification model is the ability to exploit 
-the expressiveness of the underlying reasoning engines.  To this end, \hwcbmcv
-constructs either a bit-level co-verification model that is checked with a SAT solver 
-or a word-level model that is checked with an SMT solver.  Whereas, a 
+the expressivity of the underlying reasoning engines.  To this end, \hwcbmcv
+constructs either a bit-level co-verification model that are checked with a SAT solvers 
+or a word-level model that are checked with SMT solvers.  Whereas, a 
 co-verification model in \verifox is constructed 
@@
 symbolic execution is then performed over the co-verification model to
-automatically mine relevant interactions between the FW and HW models.
+automatically mine relevant interaction behaviors between the FW and HW models.
 
@@
 \scalebox{.48}{\import{figures/}{work-flow.pspdftex}}
-\caption{Proposed HW/SW Co-verification Flow
+\caption{Path-based HW/SW Co-verification Flow in \verifox
 \label{proposed-flow}}
@@
 %
-%\begin{figure}[t]
-%\scalebox{.50}{\import{figures/}{compose.pspdftex}}
-%  \caption{Composition of FW and HW threads}
-%\label{fig:interleaving2}
-%\end{figure}
-%
+\begin{figure}[t]
+\scalebox{.50}{\import{figures/}{compose.pspdftex}}
+  \caption{Composition of FW and HW threads}
+\label{compose}
+\end{figure}
 
@@
 \includegraphics[scale=0.6]{figures/traditional_flow.pdf}
-\caption{Monolithic HW/SW Co-verification Flow}
+\caption{Monolithic HW/SW Co-verification Flow in \hwcbmcv}
 \label{fig:conventional}
@@
 \end{figure}
+%
+\textbf{Step 1: Co-verification Model}
 %
@@
 Synthesizing netlist from RTL is a standard technique which is widely 
-used in hardware model checkers~\cite{}. Similarly, translating a C program 
-into a SSA representation is a standard technique which is widely used in 
-software verification tools, such as CBMC~\cite{}, 2LS~{}. 
-These two flows meet only at the solver.  Thus, \hwcbmcv generates a
-unified monolithic co-verification model from AIG and SSA which is 
-represented in Conjunctive Normal Form (CNF).  This model is then used to perform 
-bounded model checking~\cite{} using the underlying SAT/SMT solvers.  
-\hwcbmcv provides specific handshake primitives such
-as $next\_timeframe()$ and $set\_inputs()$ to model FW-HW communications.
-
-\rmcmt{
-To this end, \hwcbmcv constructs a co-verification model through 
-in tandem symbolic execution of the HW and FW models.  A bit-level 
-netlist representation in And Inverter Graph (AIG) format or word-level netlist in
-format similar to SMT-LIB standards is synthesized from a HW Register Transfer 
-Level (RTL) implementation. Similarly, the SW, given in C, is automatically 
-translated into a Static Single Assignment (SSA) form.  A monolithic verification 
-condition is generated from these two models which is then solved using a 
-}
+used in hardware model checkers~\cite{DBLP:journals/tse/Clarke76}.
+Similarly, translating a C program into a SSA representation is a 
+standard technique which is widely used in 
+software verification tools, such as CBMC~\cite{cbmc.tacas:2004}. 
+\hwcbmcv generates a monolithic co-verification model from AIG and SSA through 
+in-tandem symbolic execution of HW and FW components.
+
+\textbf{Step 2: Bounded Model Checking}
+%
+The co-verification model is checked with bounded model checking (BMC).
+Given an unwind depth depth~$k$ and a co-design property $P$, BMC operates
+by unwinding the co-verification model~$M$ up to depth~$k$ starting from
+initial state $x_0$, represented by an initial state predicate~$I$.
+This results in the following formula which is then checked for
+satisfiability using an efficient SAT or SMT procedure.
+%
+\[ I(x_0) \wedge \bigwedge_{i=0}^{k-1} M(x_i, x_{i+1}) \wedge \bigvee_{i=0}^{k} 
+\neg P(x_i) \]
+%
+Thus, BMC exploits the finiteness of $M$ and creates k copies of the
+$M$ for each unrolling.
+
+%\hwcbmcv provides specific handshake primitives such
+%as $next\_timeframe()$ and $set\_inputs()$ to model FW-HW communications.
+
+\textbf{Step 3: Scenario/Transaction Pair} In \hwcbmcv, the symbolic execution 
+of HW and FW components meet only at the solver phase.  Thus, a complex
+monolithic formula is passed on to the solver for verification purpose.  This
+limits the opportunity for extracting relevant scenario/transaction pairs
+through symbolic execution. Instead, the technique relies on the underlying
+SAT/SMT solver to effeciently reason about the co-verification model. 
 %

### 2017-04-06 paper.tex
result table 1

@@
 \scalebox{.48}{\import{figures/}{work-flow.pspdftex}}
-\caption{Path-based HW/SW Co-verification Flow in \verifox
+\caption{\small Path-based HW/SW Co-verification Flow in \verifox
 \label{proposed-flow}}
@@
 \includegraphics[scale=0.6]{figures/traditional_flow.pdf}
-\caption{Monolithic HW/SW Co-verification Flow in \hwcbmcv}
+\caption{\small Monolithic HW/SW Co-verification Flow in \hwcbmcv}
 \label{fig:conventional}
@@
 compliant with industry standards for UART and interfaces with the wishbone
-bus.  The core supports single transmission/reception format which is
+bus.  The design statistics for UART is shown in Table~\ref{table:stats}.
+
+\Omit{
+The core supports single transmission/reception format which is
 1~start bit, 1~stop bit and 8~data bits without parity.  It also contains a
@@
 \rmcmt{refer stats table}
+}
 %
@@
 %
-\rmcmt{stats in a table, remove klee result, SoC diagram}
 \textbf{\emph{Discussion:}}
@@
 firmware.  Column~3~and~4 present the co-verification times using \hwcbmcv
-at the bit-level and word-level.  Column~5,6,7~and~10 give the verification
-times for the corresponding unified program netlist model using \cbmcv,
-\klee, \textsc{symbiotic} and \verifox, respectively.  Column~8~and~9 report
+at the bit-level and word-level.  Column~7 gives the verification
+times using \verifox.  Column~5~and~6 report
 the total/feasible path counts and the percentage of infeasible paths pruned
-for each mode.  The focus of our experiment is to demonstrate the
-scalability of path-based techniques over monolithic BMC instances for
-effectively pruning infeasible FW-HW interactions with respect to a
-scenario.  This is demonstrated by the \%-age of pruned paths (reported in
-column~9) for each scenario.
+for each mode.  The focus of our experiment is to compare the performance of 
+path-based techniques over monolithic BMC. 
+%effectively pruning infeasible FW-HW interactions with respect to a
+%scenario.  is demonstrated by the \%-age of pruned paths (reported in
+%column~9) for each scenario.
 
@@
 \textbf{\emph{Detecting UART bugs:}}
-We found several bugs in the open source UART IP. 
+We found several bugs in the open source UART IP obtained from~\url{http://www.opencores.org}.  
+The bottom part of Table~\ref{table:safe} reports the verification
+times for detecting data-path and control-path bugs in UART IP.  
 The bug in the UART data-path is manifested in the transmission mode when no
@@
 transmitter buffer is empty, thereby violating the data transfer protocol. 
-On the other hand, the control bug occurs in the loopback mode only when the
+On the other hand, the \emph{control bug} occurs in the loopback mode only when the
 data is present at the receiver buffer but the $data\_present$ signal is
@@
 proving safety properties is on average $21\times$ for \verifox over
-\hwcbmcv.  \verifox also outperforms \klee for most configurations in
+\hwcbmcv.  The average speedup for detecting bugs is $48\times$ on average 
+for \verifox over \hwcbmcv.  Thus, \verifox outperforms \hwcbmcv 
+in all scenarios.
+
+\Omit{
+\verifox also outperforms \klee for most configurations in
 Scenario~A and Scenario~C.  In Scenario~B, \klee marginally wins over
@@
 FW, thereby causing \cbmcv to get stuck in unwinding the program netlist
-model.  The bottom part of Table~\ref{table:safe} reports the verification
-times for detecting data-path and control-path bugs in UART IP.  The result
-shows that \verifox is the fastest in detecting both the data-path and
-control-flow bugs for all scenarios.  The average speedup for detecting bugs
-is $48\times$ on average for \verifox over \hwcbmcv.
+model.
 
@@
 MiniSAT~2.2.0 in the backend.
-
+}
 \Omit
@@
 \begin{scriptsize}
-\begin{tabular}{|l|l|l|l|l|l|l|l|l|l|}
+\begin{tabular}{|l|l|l|l|l|l|l|}
 \hline
-  & Bound & \multicolumn{3}{c|}{Monolithic} & \multicolumn{5}{c|}{Path-based} \\ 
-\cline{3-10}
- Scenario &  & \multicolumn{2}{c|}{HW-CBMC} & CBMC & Klee & Symbiotic & \multicolumn{3}{c|}{VerifOx} \\ 
-\cline{3-10}
-      &       &  Bit-level & Word-level & $\mathcal{PN}$ & $\mathcal{PN}$ & $\mathcal{PN}$ & Total/Feasible & \%-age & SAT \\
+  & Bound & \multicolumn{2}{c|}{Monolithic} & \multicolumn{3}{c|}{Path-based} \\ 
+\cline{3-7}
+ Scenario &  & \multicolumn{2}{c|}{HW-CBMC} & \multicolumn{3}{c|}{VerifOx} \\ 
+\cline{3-7}
+      &       &  Bit-level & Word-level & Total/Feasible & \%-age & $\mathcal{M}_{seq}$  \\
+%\cline{1-7}
+      &       &   Time     &   Time      & Paths & Pruning & Time \\
 \cline{1-7}      
-      &       &   Time     &   Time      & Time  &  Time & Time & Paths & Pruning & Time \\
-\cline{1-10}      
-\multicolumn{10}{|c|}{non-deterministic data but deterministic control (Scenario A)} \\ \hline
-transmit (32) & 250 & 15.02 & 15.78 & 108.25 & \textbf{0}.\textbf{98} & 29.36 & 247104/224 & 99.90 & 1.13 \\ 
-transmit (64) & 500 & 23.87 & 23.29 & 206.89 & 1.68 & 29.90 & 247104/324 & 99.86 & \textbf{1}.\textbf{61}  \\ \hline 
-\multicolumn{10}{|c|}{non-deterministic data and non-deterministic control
+\multicolumn{7}{|c|}{non-deterministic data but deterministic control (Scenario A)} \\ \hline
+  transmit (32) & 250 & 15.02 & 15.78 & 247104/224 & 99.90 & \textbf{1}.{13} \\ 
+transmit (64) & 500 & 23.87 & 23.29 & 247104/324 & 99.86 & \textbf{1}.\textbf{61}  \\ \hline 
+\multicolumn{7}{|c|}{non-deterministic data and non-deterministic control
 (Scenario B)} \\ \hline
-trans\_intr (32) & 250 & 14.86 & 15.98 & 69.19 & \textbf{1}.\textbf{15} & 29.53 & 247104/295 & 99.88 & 1.49 \\
-trans\_intr (64) & 500 & 24.14 & 26.42 & 117.73 & \textbf{1}.\textbf{27} & 29.58 & 247104/362 & 99.85 & 1.81 \\ \hline
-\multicolumn{10}{|c|}{non-deterministic data and non-deterministic control
+  trans\_intr (32) & 250 & 14.86 & 15.98 & 247104/295 & 99.88 & \textbf{1}.{49} \\
+  trans\_intr (64) & 500 & 24.14 & 26.42 & 247104/362 & 99.85 & \textbf{1}.{81} \\ \hline
+\multicolumn{7}{|c|}{non-deterministic data and non-deterministic control
 (scenario C)} \\ \hline
-loopback (8)  & 230 & 52.06 & 55.71 & 1289.85 & 10.76 & 29.01 & 247104/354 & 99.85 & \textbf{3}.\textbf{95} \\ 
-loopback (16) & 500 & 122.12 & 147.65 & 5410.18 & 32.24 & 29.04 & 247104/690 & 99.72 & \textbf{12}.\textbf{89} \\ 
-loopback (32) & 650 & 170.62 & 192.35 & TO & 112.32 & 28.27 & 247104/1282 & 99.48 & \textbf{21}.\textbf{85}   \\ 
-loopback (64) & 1300 & 409.71 & 445.66 & TO & 494.25 & 56.71 & 247104/2566 & 98.96 & \textbf{62}.\textbf{31}  \\ \hline
-\multicolumn{10}{|c|}{detecting data-path bugs in transmission mode w/o interrupt} \\ \hline
-transmit (64) & 520 & 28.43 & 28.14 & 186.99 & \textbf{0}.\textbf{96} & 26.67 &
-247104/324 & 99.86 & 1.12 \\ \hline
-\multicolumn{10}{|c|}{detecting control bugs with interrupt enabled} \\ \hline
-transmit (64) & 520 & 31.35 & 29.70 & 113.57 & 1.18 & 27.13 & 247104/362 & 99.85 & \textbf{1}.\textbf{05} \\ \hline
-\multicolumn{10}{|c|}{detecting control bugs in loopback mode} \\ \hline
-loopback (64) & 1300 & 443.15 & 427.68 & TO & 492.59 & 54.23 & 247104/2566 &
-98.96 & \textbf{62}.\textbf{34} \\ \hline
+loopback (8)  & 230 & 52.06 & 55.71 & 247104/354 & 99.85 & \textbf{3}.\textbf{95} \\ 
+loopback (16) & 500 & 122.12 & 147.65 & 247104/690 & 99.72 & \textbf{12}.\textbf{89} \\ 
+loopback (32) & 650 & 170.62 & 192.35 & 247104/1282 & 99.48 & \textbf{21}.\textbf{85}   \\ 
+loopback (64) & 1300 & 409.71 & 445.66 & 247104/2566 & 98.96 & \textbf{62}.\textbf{31}  \\ \hline
+\multicolumn{7}{|c|}{detecting data-path bugs in transmission mode w/o interrupt} \\ \hline
+  transmit (64) & 520 & 28.43 & 28.14 & 247104/324 & 99.86 &
+  \textbf{1}.\textbf{12} \\ \hline
+\multicolumn{7}{|c|}{detecting control bugs with interrupt enabled} \\ \hline
+transmit (64) & 520 & 31.35 & 29.70 & 247104/362 & 99.85 & \textbf{1}.\textbf{05} \\ \hline
+\multicolumn{7}{|c|}{detecting control bugs in loopback mode} \\ \hline
+loopback (64) & 1300 & 443.15 & 427.68 & 247104/2566 & 98.96 & \textbf{62}.\textbf{34} \\ \hline
 \end{tabular}
@@
 \end{center}
-\vspace{-1.3mm}
+%\vspace{-1.3mm}
 \caption{Bounded safety proof times for HW/SW co-verification of UART 

### 2017-04-06 paper.tex
minor and comments

--- 2017-04-06 paper.tex
@@
 %===============================================================================
-In this section, we present an working example of FW and HW model to explain our 
+In this section, we present a working example of FW and HW model to explain our 
 co-verification methodologies.
@@
 respectively. Section~\ref{property} describes the property specification in
-HW-FW co-designs in more details. 
+HW-FW co-designs in more detail. 
 \[
@@
 %
-We formally describe the notion of \emph{transaction} and \emph{scenario} with the
+We describe the notion of \emph{transaction} and \emph{scenario} with the
 help of our working example. \\
@@
 \textbf{Scenario ($\mathcal{S}$):}
-Let $B$ denote a set of all possible behaviors of a system. A scenario is a set of 
+Let $B$ denote the set of all possible behaviors of a system. A scenario is a set of 
 constraints $\mathcal{S}$ that restrict the system behaviors
@@
 gives an example scenario for the UART FW shown in Figure~\ref{firmware}. 
-Here, $\mathcal{S}$ configure the UART IP in {\em loopback} mode with 
+Here, $\mathcal{S}$ configures the UART IP in {\em loopback} mode with 
 interrupt enabled.
@@
 with a start state and an end state, which is similar to the notion of 
-transactions in TLM~\cite{codes14}. 
-Each transition in $\mathcal{FT}$ is guarded with a quantifier free predicates
+a transaction in TLM~\cite{codes14}. 
+Each transition in $\mathcal{FT}$ is guarded with a quantifier free predicate
 over FW variables and HW signals.
-If the guard evaluates to $TRUE$, it may perform some action, which may be 
+If the guard evaluates to $TRUE$, it may perform some action, which may  
 read/write data. If the guard is not specified, it is assumed to be $TRUE$.
@@
 UART output signal, $irq_o$. An execution of $\mathcal{FT}$, also called a 
-FW transaction instance, takes a simple path from start state to end state. 
+FW transaction instance, takes a simple path from the start state to the end state. 
 The path taken by an execution is determined by the state of 
 the FW variables or its interacting HW signals. Repeated execution of 
-$\mathcal{FT}$ can happen only in a sequential manner.
+$\mathcal{FT}$ can happen only in a sequential manner \sjcmt{not clear what this means}.
 
@@
 state elements, $\{Reg\}$, $\{Mem\}$, $\{Wire\}$.  
-A {\em transaction step}, $\varphi$, is defined by 2 tuple,
+A {\em transaction step}, $\varphi$, is defined by a 2-tuple,
 $\varphi \equiv \langle \Gamma_{\varphi}, \Delta_{\varphi} \rangle$, where 
@@
 $\varphi$ with a unique source vertex, $init \in V$, and a unique sink vertex, 
-$comp \in V$, $\Sigma$ is a set of labels such that $\Sigma \subseteq 2^{G}$ and  
+$comp \in V$, $\Sigma$ is a set of labels such that $\Sigma \subseteq 2^{G}$ \sjcmt{2 power G may not be required, just G may be sufficient as it is closed under disjunction, conjunction and negation} and
 $\rightarrow \subseteq V \times \Sigma \times V$ is a set of labelled
@@
 \scalebox{.48}{\import{figures/}{work-flow.pspdftex}}
-\caption{Path-based HW/SW Co-verification Flow in \verifox
+\caption{Proposed HW/SW Co-verification Flow
 \label{proposed-flow}}
@@
 %
-\begin{figure}[t]
-\scalebox{.50}{\import{figures/}{compose.pspdftex}}
-  \caption{Composition of FW and HW threads}
-\label{compose}
-\end{figure}
+%\begin{figure}[t]
+%\scalebox{.50}{\import{figures/}{compose.pspdftex}}
+%  \caption{Composition of FW and HW threads}
+%\label{fig:interleaving2}
+%\end{figure}
+%
 
@@
 \includegraphics[scale=0.6]{figures/traditional_flow.pdf}
-\caption{Monolithic HW/SW Co-verification Flow in \hwcbmcv}
+\caption{Monolithic HW/SW Co-verification Flow}
 \label{fig:conventional}
@@
 \end{figure}
-%
-\textbf{Step 1: Co-verification Model}
 %
@@
 Synthesizing netlist from RTL is a standard technique which is widely 
-used in hardware model checkers~\cite{DBLP:journals/tse/Clarke76}.
-Similarly, translating a C program into a SSA representation is a 
-standard technique which is widely used in 
-software verification tools, such as CBMC~\cite{cbmc.tacas:2004}. 
-\hwcbmcv generates a monolithic co-verification model from AIG and SSA through 
-in-tandem symbolic execution of HW and FW components.
-
-\textbf{Step 2: Bounded Model Checking}
-%
-The co-verification model is checked with bounded model checking (BMC).
-Given an unwind depth depth~$k$ and a co-design property $P$, BMC operates
-by unwinding the co-verification model~$M$ up to depth~$k$ starting from
-initial state $x_0$, represented by an initial state predicate~$I$.
-This results in the following formula which is then checked for
-satisfiability using an efficient SAT or SMT procedure.
-%
-\[ I(x_0) \wedge \bigwedge_{i=0}^{k-1} M(x_i, x_{i+1}) \wedge \bigvee_{i=0}^{k} 
-\neg P(x_i) \]
-%
-Thus, BMC exploits the finiteness of $M$ and creates k copies of the
-$M$ for each unrolling.
-
-%\hwcbmcv provides specific handshake primitives such
-%as $next\_timeframe()$ and $set\_inputs()$ to model FW-HW communications.
-
-\textbf{Step 3: Scenario/Transaction Pair} In \hwcbmcv, the symbolic execution 
-of HW and FW components meet only at the solver phase.  Thus, a complex
-monolithic formula is passed on to the solver for verification purpose.  This
-limits the opportunity for extracting relevant scenario/transaction pairs
-through symbolic execution. Instead, the technique relies on the underlying
-SAT/SMT solver to effeciently reason about the co-verification model. 
+used in hardware model checkers~\cite{}. Similarly, translating a C program 
+into a SSA representation is a standard technique which is widely used in 
+software verification tools, such as CBMC~\cite{}, 2LS~{}. 
+These two flows meet only at the solver.  Thus, \hwcbmcv generates a
+unified monolithic co-verification model from AIG and SSA which is 
+represented in Conjunctive Normal Form (CNF).  This model is then used to perform 
+bounded model checking~\cite{} using the underlying SAT/SMT solvers.  
+\hwcbmcv provides specific handshake primitives such
+as $next\_timeframe()$ and $set\_inputs()$ to model FW-HW communications.
+
+\rmcmt{
+To this end, \hwcbmcv constructs a co-verification model through 
+in tandem symbolic execution of the HW and FW models.  A bit-level 
+netlist representation in And Inverter Graph (AIG) format or word-level netlist in
+format similar to SMT-LIB standards is synthesized from a HW Register Transfer 
+Level (RTL) implementation. Similarly, the SW, given in C, is automatically 
+translated into a Static Single Assignment (SSA) form.  A monolithic verification 
+condition is generated from these two models which is then solved using a 
+}
 %

### 2017-04-06 paper.tex
comment
comments, minor

@@
 Figure~\ref{proposed-flow} describes our overall tool framework. In the
-subsequent section, we describe each step in details.\\ 
+subsequent section, we describe each step in detail.\\ 
 %
@@
 \textit{software netlist}~\cite{mtk2016,mskm2016,mkm2015} following synthesis 
-semantics. The software netlist model is cycle-accurate as well as 
+semantics \sjcmt{ref for synthesis semantics?}. The software netlist model is cycle-accurate as well as 
 bit-precise~\footnote{http://www.cprover.org/hardware/v2c/}. The 
 translation automatically handles concurrent statements 
-in Verilog such as procedural blocks and continuous assignments, multiple always
-blocks, multiple modules and translates them into an equivalent C program.  This
+in Verilog such as procedural blocks and continuous assignments, multiple {\em always}
+blocks, multiple modules, and translates them into an equivalent \sjcmt{we should specify equivalent in what sense} C program.  This
 is a radically new but promising approach for synthesizing software 
-models from RTL description, mainly targeted for word-level formal hardware 
+models from RTL description, primarily targeted for word-level formal hardware 
 verification using software verification techniques such as abstract 
-satisfaction~\cite{leo-thesis}.  To the best of our knowledge, this is the first 
-attempt to demonstrate the efficacy of such translation in the context of 
+satisfaction\sjcmt{?}~\cite{leo-thesis}.  To the best of our knowledge, this is the first 
+attempt to demonstrate the efficacy of such a translation in the context of 
 hardware/software co-verification. 
@@
 %
-Here, $\mathit{In}$, $\mathit{Out}$, $\mathit{Seq}$, $\mathit{Comb}$
-are programs variables that model \emph{input}, \emph{output}, 
+Here, $\mathit{In}$ \sjcmt{this is missing from the def}, $\mathit{Out}$, $\mathit{Seq}$, $\mathit{Comb}$
+are program variables that model \emph{input}, \emph{output}, 
 \emph{sequential/state-holding} and \emph{combinational/stateless} 
@@
 to $Out$, $Seq$ and $Comb$. Figure~\ref{ex1} shows an example of 
-Verilog RTL circuit containing an always block and continuous
-assignment statement and the equivalent software netlist in C.
+Verilog RTL circuit containing an {\em always} block and continuous
+assignment statements, and the equivalent software netlist in C.
 %

### 2017-04-06 paper.tex
Experimental text

--- 2017-04-06 paper.tex
@@
 %===============================================================================
-In this section, we present a working example of FW and HW model to explain our 
+In this section, we present an working example of FW and HW model to explain our 
 co-verification methodologies.
@@
 respectively. Section~\ref{property} describes the property specification in
-HW-FW co-designs in more detail. 
+HW-FW co-designs in more details. 
 \[
@@
 %
-We describe the notion of \emph{transaction} and \emph{scenario} with the
+We formally describe the notion of \emph{transaction} and \emph{scenario} with the
 help of our working example. \\
@@
 \textbf{Scenario ($\mathcal{S}$):}
-Let $B$ denote the set of all possible behaviors of a system. A scenario is a set of 
+Let $B$ denote a set of all possible behaviors of a system. A scenario is a set of 
 constraints $\mathcal{S}$ that restrict the system behaviors
@@
 gives an example scenario for the UART FW shown in Figure~\ref{firmware}. 
-Here, $\mathcal{S}$ configures the UART IP in {\em loopback} mode with 
+Here, $\mathcal{S}$ configure the UART IP in {\em loopback} mode with 
 interrupt enabled.
@@
 with a start state and an end state, which is similar to the notion of 
-a transaction in TLM~\cite{codes14}. 
-Each transition in $\mathcal{FT}$ is guarded with a quantifier free predicate
+transactions in TLM~\cite{codes14}. 
+Each transition in $\mathcal{FT}$ is guarded with a quantifier free predicates
 over FW variables and HW signals.
-If the guard evaluates to $TRUE$, it may perform some action, which may  
+If the guard evaluates to $TRUE$, it may perform some action, which may be 
 read/write data. If the guard is not specified, it is assumed to be $TRUE$.
@@
 UART output signal, $irq_o$. An execution of $\mathcal{FT}$, also called a 
-FW transaction instance, takes a simple path from the start state to the end state. 
+FW transaction instance, takes a simple path from start state to end state. 
 The path taken by an execution is determined by the state of 
 the FW variables or its interacting HW signals. Repeated execution of 
-$\mathcal{FT}$ can happen only in a sequential manner \sjcmt{not clear what this means}.
+$\mathcal{FT}$ can happen only in a sequential manner.
 
@@
 state elements, $\{Reg\}$, $\{Mem\}$, $\{Wire\}$.  
-A {\em transaction step}, $\varphi$, is defined by a 2-tuple,
+A {\em transaction step}, $\varphi$, is defined by 2 tuple,
 $\varphi \equiv \langle \Gamma_{\varphi}, \Delta_{\varphi} \rangle$, where 
@@
 $\varphi$ with a unique source vertex, $init \in V$, and a unique sink vertex, 
-$comp \in V$, $\Sigma$ is a set of labels such that $\Sigma \subseteq 2^{G}$ \sjcmt{2 power G may not be required, just G may be sufficient as it is closed under disjunction, conjunction and negation} and
+$comp \in V$, $\Sigma$ is a set of labels such that $\Sigma \subseteq 2^{G}$ and  
 $\rightarrow \subseteq V \times \Sigma \times V$ is a set of labelled
@@
 In this paper, we classify co-design properties into two 
-classes -- {\em transaction-level} property and {\em component-level} property.
+classes -- {\em transaction level} property and {\em component level} property.
 %-------------------------------------------------------------------------------
-\subsection{Transaction-level Property}
+\subsection{Transaction level Property}
 %-------------------------------------------------------------------------------
-A {\em Transaction-level} property ($\psi_{t}$) formally captures the 
+A {\em Transaction level} property ($\psi_{t}$) formally captures the 
 design intent of the interaction between a $\mathcal{ST}$ and $\mathcal{HT}$, 
@@
 
-Thus, a transaction-level property follows implication structure -- the 
+Thus, a transaction level property follows implication structure -- the 
 antecedent of the implication is an event in $\mathcal{ST}$ or 
@@
 $\mathcal{HT}$ corresponds to an update of combinational or sequential 
-elements. \rmcmt{example}
+elements. Table~\ref{figure:transaction} shows few examples of transaction 
+level property, written as monitors in C, for the UART IP.  In $monitor_P1()$, 
+$outb(UART\_TR,0x0c)$ is a FW event and $ack\_o$ is a HW event. Whereas in
+$monitor_P2$, the antecedent $tx\_empty()$ is a HW event and $send_data$ is a FW
+event. 
+%
+\begin{figure}[htbp]
+\scriptsize
+\begin{tabular}{l|l}
+\hline
+\multicolumn{2}{c}{Monitors (in C)}
+\\
+\hline
+\begin{lstlisting}[mathescape=true,language=C,moredelim={[is][keywordstyle]{@@}{@@}}]
+int monitor_P1() { 
+ if(outb(UART_TR,0x0c)){
+  next_timeframe();
+  assert(@@ ack_o==1 @@);}}
+\end{lstlisting} 
+&
+\begin{lstlisting}[mathescape=true,language=C,moredelim={[is][keywordstyle]{@@}{@@}}]
+int monitor_P2() { 
+ assert(!tx_empty() || 
+ (@@(send_data&0x1)==1)@@);
+}
+\end{lstlisting} \\ 
+\hline
+\end{tabular}
+\caption{Transaction-level property as monitor (in C)}
+\label{figure:transaction}
+\end{figure}
+%
 
 %-------------------------------------------------------------------------------
-\subsection{Component-level Property}
+\subsection{Component level Property}
 %-------------------------------------------------------------------------------
-A {\em component-level} property ($\psi_{c}$) is defined purely at the 
+A {\em component level} property ($\psi_{c}$) is defined purely at the 
 level of individual components of a co-design system. Recall that a component 
@@
 
-\begin{table*}
+\begin{table}
 \begin{center}
@@
 \label{table:safe}}
-\end{table*}
+\end{table}
 
@@
 micro-controller, a memory arbiter, an external memory (XRAM) and
-cryptographic accelerators.  The SoC is implemented in approximately~3000
-lines of Verilog RTL, which generate several thousand gates.  The
-accelerator implements encryption/decryption using the Advanced Encryption
+cryptographic accelerators.  The design statistics for SoC is given in
+
+Table~\ref{table:stats}.  
+The accelerator implements encryption/decryption using the Advanced Encryption
 Standard (AES) and is obtained
@@
 separate module that interfaces the AES to the 8051 micro-controller using a
-memory-mapped I/O interface.  The micro-con\-tro\-ller communicates with the
+memory-mapped I/O interface.  The micro-controller communicates with the
 accelerators and the XRAM by reading or writing to XRAM addresses.  The
-arbitration of these module is done by the memory arbiter module.  We
-synthesized the SoC to a software netlist (in C) using {\em v2c}.  The
-generated model is bit-precise as well as cycle accurate.  The size of the
+arbitration of these module is done by the memory arbiter module.
+
+\Omit{
+We synthesized the SoC to a software netlist (in C).  The generated model 
+is bit-precise as well as cycle accurate.  The size of the
 software netlist is approximately~3200 LOC.  The combinatorial exchanges
 between the memory arbiter, XRAM and the AES module is modelled
-appropriately in the software netlist.  \\
+appropriately in the software netlist.
+}
 
@@
 %\begin{scriptsize}
-\begin{tabular}{|l|l|l|l|l|l|l|l|}
+\begin{tabular}{|l|l|l|l|l|}
 \hline
-  & Bound & \multicolumn{3}{c|}{Monolithic} & \multicolumn{3}{c|}{Path-based} \\ 
-\cline{3-8}
- Scenario &  & \multicolumn{2}{c|}{HW-CBMC} & CBMC & Klee & Symbiotic & VerifOx \\ 
-\cline{3-8}
-      &       &  Bit-level & Word-level & $\mathcal{PN}$ & $\mathcal{PN}$ & $\mathcal{PN}$ & $\mathcal{PN}$ \\
-\cline{1-8}
-      &       &   Time     &   Time      & Time  &  Time & Time & Time \\
-\cline{1-8}      
-\multicolumn{8}{|c|}{non-deterministic data and non-deterministic control (safe)} \\ \hline
-data\_transfer & 20 & 86.92 & 86.23 & 104.25 & 25.98 & 29.36 &
-\textbf{17}.\textbf{42} \\ 
+  & Bound & \multicolumn{2}{c|}{Monolithic} & \multicolumn{1}{c|}{Path-based} \\ 
+\cline{3-5}
+ Scenario &  & \multicolumn{2}{c|}{\hwcbmcv} & \verifox \\ 
+\cline{3-5}
+      &       &  Bit-level & Word-level & $\mathcal{M}_{seq}$ \\
+\cline{1-5}
+      &       &   Time     &   Time     & Time \\
+\cline{1-5}      
+\multicolumn{5}{|c|}{non-deterministic data and non-deterministic control (safe)} \\ \hline
+data\_transfer & 20 & 86.92 & 86.23 & \textbf{17}.\textbf{42} \\ 
 \hline
-\multicolumn{8}{|c|}{non-deterministic data and non-deterministic control
+\multicolumn{5}{|c|}{non-deterministic data and non-deterministic control
 (unsafe)} \\ \hline
-data\_transfer & 20 & 92.63 & 91.28 & 95.76 & 5.68 & 28.14 &
-\textbf{1}.\textbf{27} \\ 
+data\_transfer & 20 & 92.63 & 91.28 & \textbf{1}.\textbf{27} \\ 
 \hline
@@
 \end{center}
-\vspace{-1.3mm}
+%\vspace{-1.3mm}
 \caption{Bounded safety proof times for HW/SW co-verification of a SoC 
 \label{table:SoC}}
-\end{table*}
+\end{table}
 

### 2017-04-06 paper.tex
property syntax

@@
 elements. Table~\ref{figure:transaction} shows few examples of transaction 
-level property, written as monitors in C, for the UART IP.  In $monitor_P1()$, 
+level property, written as monitors in C, for the UART IP.  In $monitor\_P1()$, 
 $outb(UART\_TR,0x0c)$ is a FW event and $ack\_o$ is a HW event. Whereas in
-$monitor_P2$, the antecedent $tx\_empty()$ is a HW event and $send_data$ is a FW
+$monitor\_P2$, the antecedent $tx\_empty()$ is a HW event and $send\_data$ is a FW
 event. 
@@
 or consequent to be a HW or SW event,  $\psi_{c}$ only contains signals 
-(ports) or variables of a particular component. \rmcmt{example}
-
+(ports) or variables of a particular component.  Table~\ref{figure:component} 
+shows an example of component level property for the UART HW only.  The 
+System Verilog Assertion (SVA) is shown in the left and the equivalent 
+monitor in C is shown in right.  
+%
+\begin{figure}[htbp]
+\scriptsize
+\begin{tabular}{l|l}
+\hline
+System Verilog Assertions  & Monitor (in C)
+\\
+\hline
+\begin{lstlisting}[mathescape=true,language=Verilog]
+P3: assert property 
+ (@(posedge clk) 
+ ack == 1|-> 
+ (valid == 1 && 
+ ##2 empty == 0)); 
+\end{lstlisting}
+&
+\begin{lstlisting}[mathescape=true,language=C]
+int monitor_P3() {
+ assert(!ack || valid);
+ next_timeframe();
+ next_timeframe();
+ assert(empty==0); }
+\end{lstlisting} \\
+\hline
+\end{tabular}
+\caption{Component-level property (in SVA) as monitor (in C)}
+\label{figure:component}
+\end{figure}
+% 
 %===============================================================================

### 2017-04-06 paper.tex
minor

@@
 \begin{lstlisting}[mathescape=true,language=C]
-int monitor_P3() {
+Bool monitor_P3() {
  assert(!ack || valid);
@@
 whether the transmitter buffer is empty or the receiver buffer is full
-respectively, hence the control is non-deterministic in this mode.
+respectively, hence the control is non-deterministic in this mode. \\
 %
@@
 cryptographic accelerators.  The design statistics for SoC is given in
-
-Table~\ref{table:stats}.  
-The accelerator implements encryption/decryption using the Advanced Encryption
-Standard (AES) and is obtained
-from~\href{http://www.opencores.org}{http://www.opencores.org}.  There is a
-separate module that interfaces the AES to the 8051 micro-controller using a
-memory-mapped I/O interface.  The micro-controller communicates with the
-accelerators and the XRAM by reading or writing to XRAM addresses.  The
-arbitration of these module is done by the memory arbiter module.
+Table~\ref{table:stats}.  The accelerator implements encryption/decryption 
+using the Advanced Encryption Standard (AES).  There is a separate 
+module that interfaces the AES to the 8051 micro-controller using 
+a memory-mapped I/O interface.  The micro-controller communicates 
+with the accelerators and the XRAM by reading or writing to 
+XRAM addresses.  The arbitration of these module is done by 
+the memory arbiter module.
 

### 2017-04-06 paper.tex
soc figure

@@
 $\mathcal{HT}$ corresponds to an update of combinational or sequential 
-elements. Table~\ref{figure:transaction} shows few examples of transaction 
+elements. Figure~\ref{figure:transaction} shows an example of transaction 
 level property, written as monitors in C, for the UART IP.  In $monitor\_P1()$, 
 $outb(UART\_TR,0x0c)$ is a FW event and $ack\_o$ is a HW event. Whereas in
-$monitor\_P2$, the antecedent $tx\_empty()$ is a HW event and $send\_data$ is a FW
+$monitor\_P2()$, the antecedent $tx\_empty()$ is a HW event and $send\_data$ is a FW
 event. 
@@
 or consequent to be a HW or SW event,  $\psi_{c}$ only contains signals 
-(ports) or variables of a particular component.  Table~\ref{figure:component} 
+(ports) or variables of a particular component.  Figure~\ref{figure:component} 
 shows an example of component level property for the UART HW only.  The 
@@
 micro-controller, a memory arbiter, an external memory (XRAM) and
-cryptographic accelerators.  The design statistics for SoC is given in
+cryptographic accelerators, as shown in Figure~\ref{fig:soc}.  
+The design statistics for SoC is given in
 Table~\ref{table:stats}.  The accelerator implements encryption/decryption 
@@
 the memory arbiter module.  
-
+%
+\begin{figure}[t]
+\scalebox{.50}{\import{figures/}{soc.pspdftex}}
+  \caption{SoC Design obtained from~\cite{DBLP:conf/fmcad/SubramanyanVRM15}
+\label{fig:soc}}
+\end{figure}
+%
 \Omit{
@@
 is not applicable for co-designs that exhibits true concurrency~\cite{concurrency}, 
-that is, a FW its interacting HW threads does not show producer-consumer relationship.  
-In this case, it is imperative to consider all possible interleavings between
-these threads in some effecient manner.  However, our experience is that such 
+that is, a FW its interacting HW threads do not show producer-consumer relationship.  
+In this case, it is imperative to consider all possible interleavings between participating 
+threads in an effecient manner.  However, our experience is that such 
 co-designs occurs rarely in practise.

### 2017-04-06 paper.tex
minor

@@
 \begin{lstlisting}[mathescape=true,language=C,moredelim={[is][keywordstyle]{@@}{@@}}]
-int monitor_P1() { 
+bool monitor_P1() { 
  if(outb(UART_TR,0x0c)){
@@
 \begin{lstlisting}[mathescape=true,language=C,moredelim={[is][keywordstyle]{@@}{@@}}]
-int monitor_P2() { 
+bool monitor_P2() { 
  assert(!tx_empty() || 
@@
 \end{tabular}
-\caption{Transaction-level property as monitor (in C)}
+\caption{Transaction level property as monitor (in C)}
 \label{figure:transaction}
@@
 \begin{lstlisting}[mathescape=true,language=C]
-Bool monitor_P3() {
+bool monitor_P3() {
  assert(!ack || valid);
@@
 \end{tabular}
-\caption{Component-level property (in SVA) as monitor (in C)}
+\caption{Component level property as monitor (in C)}
 \label{figure:component}
@@
 bus.  The design statistics for UART is shown in Table~\ref{table:stats}.
-
-\Omit{
-The core supports single transmission/reception format which is
-1~start bit, 1~stop bit and 8~data bits without parity.  It also contains a
-single transmit/receive buffer.  The UART IP implements a baud rate
-generation circuit based on a harmonic frequency synthesizer that support a
-wide variety of clock frequencies.  The UART IP core is implemented in
-approximately 1000 lines of Verilog RTL, generating several thousand gates. 
-The UART is obtained from~\url{http://www.opencores.org}.  A software
-netlist model (in C) is synthesized from the UART RTL using \emph{v2c}.  The
-software netlist model is approximately 1100 LOC.
-\rmcmt{refer stats table}
-}
 %
@@
 for each mode.  The focus of our experiment is to compare the performance of 
-path-based techniques over monolithic BMC. 
-%effectively pruning infeasible FW-HW interactions with respect to a
-%scenario.  is demonstrated by the \%-age of pruned paths (reported in
-%column~9) for each scenario.
-
+path-based techniques over monolithic BMC.\\ 
 \textbf{\emph{Safety properties:}}
@@
 \cline{3-7}
- Scenario &  & \multicolumn{2}{c|}{HW-CBMC} & \multicolumn{3}{c|}{VerifOx} \\ 
+ Scenario &  & \multicolumn{2}{c|}{HW-CBMC} & \multicolumn{3}{c|}{\verifox} \\ 
 \cline{3-7}
@@
 %\vspace{-1.3mm}
-\caption{Bounded safety proof times for HW/SW co-verification of UART 
+\caption{Bounded safety proof times for verification of UART 
 \label{table:safe}}
@@
 %\vspace{-1.3mm}
-\caption{Bounded safety proof times for HW/SW co-verification of a SoC 
+\caption{Bounded safety proof times for verification of a SoC 
 \label{table:SoC}}

### 2017-04-06 paper.tex
transaction level property

@@
     benchmarks in Verilog RTL and C models 
-    here~\footnote{https://drive.google.com/folderview?id=0BynC6sd-wTYgWVQ4bXNtRDB5a2c\&usp=sharing}.
+    here~\footnote{https://drive.google.com/folderview?id=0BynC6sd-wTYgWVQ4bXNtRDB5a2c\&usp=sharing}.\rmcmt{check
+    link}
 
@@
 \textbf{\emph{Safety properties:}}
-We verify several properties of the FW-HW interactions of UART IP. 
-In Scenario~A and scenario~B, we verified whether
+We verify a total of~17 transaction level properties and~22 component level 
+properties of the UART IP.  Table~\ref{table:safe} reports some of the
+representative properties.  In Scenario~A and scenario~B, we verified whether
 the transmitted data (32-bit or 64-bit) is available through the serial
 output port after a pre-determined number of clock cycles.
-In both of the
-configurations, \verifox is able to prune the receiver logic since the
+In both of the configurations, \verifox is able to prune the receiver logic since the
 FW only exercises the transmitter module by appropriately configuring
@@
 %
-The firmware initiates the operation in the SoC by first writing to an
-initial memory-mapped register.  The firmware implements Linux-style $inb()$
+The FW initiates the operation in the SoC by first writing to an
+initial memory-mapped register.  The FW implements Linux-style $inb()$
 and $outb()$ functions calls, which are used to communicate with the HW
-ports.  The firmware writes a sequence of non-deterministic data to the XRAM
+ports.  The FW writes a sequence of non-deterministic data to the XRAM
 port and then reads the data from the same port.  The cryptographic
@@
 Table~\ref{table:SoC} gives the runtimes for bounded safety proofs of 
-FW-HW interaction properties of the SoC.  Column~1 in
+co-design properties of the SoC.  Column~1 in
 Table~\ref{table:SoC} gives the name of the scenario -- transmission with
 interrupt (data\_transfer).  Column~2 report the maximum loop bound in the 
-firmware.  Column~3~and~4 present the co-verification times using \hwcbmcv
-at the bit-level and word-level.  Columns~[5-8] report the
-verification times for the corresponding unified program netlist model using
-\cbmcv, \klee, \textsc{symbiotic} and \verifox, respectively.
+FW.  Column~3~and~4 present the co-verification times using \hwcbmcv
+at the bit-level and word-level, respectively.  Columns~5 report the
+verification time using \verifox.
 
@@
 %
-We verify several safety properties for the FW-HW interactions.  We check
+We verify a total of 7 transaction level propertes and 12 
+component level properties for the SoC co-design.  Due to space 
+limitations, we describe some representative properties.  We check
 whether the acknowledgment for data transmission and data reception arrives
@@
 reading/writing to the appropriate memory-mapped registers produce the
-correct result during the data transmission phase.\\ \textbf{\emph{Detecting
-SoC bugs:}} We found a control-path bug in the SoC design.  The bug is
-manifested when memory arbiter hardware wrongly arbitrates the port
-selection thereby forcing the write strobe for the external RAM to be LOW. 
-This violates the data transfer protocol in the SoC design.
+correct result during the data transmission phase.\\
+
+\textbf{\emph{Detecting SoC bugs:}} We found one critical \emph{control bug} 
+in the SoC design.  The bug is manifested when memory arbiter hardware 
+wrongly arbitrates the port selection thereby forcing the write strobe 
+for the external RAM to be LOW.  This violates the data transfer protocol 
+in the SoC design.
 
 The result in Table~\ref{table:SoC} shows that \verifox is approximately
-$5\times$ faster than \hwcbmcv and $6\times$ faster than \cbmcv for proving
-safety.  For detecting bugs, the speedup is $72\times$ and $75\times$ for
-\verifox over \hwcbmcv and \cbmcv.  However, \verifox marginally wins over
-other path-based tools such as \symbiotic and \klee for safety proofs as
-well as finding bugs. The result shows that the verification times for all
-path-based techniques are comparable.  The reason for better scalability for
-symbolic execution tools compared to \hwcbmcv is attributed to the path-based 
-exploration strategy combined with eager path pruning and incremental SAT
-solving. The FW exercises only the micro-controller
-and transfer sequence of bytes to the XRAM port bypassing peripherals
-connected to other ports such as hardware accelerator.  This scenario
-allows path-based tools to prune the logic for accelerator which otherwise
-could not have been removed by simple property-driven slicing of the
-program netlist.  It is important to note that forward symbolic execution without
+$5\times$ faster than \hwcbmcv for proving safety.  For detecting bugs, 
+the speedup is $72\times$ for \verifox over \hwcbmcv.
+
+\textbf{\emph{Monolithic versus Path-based:}}
+The reason for better scalability of \verifox compared to 
+\hwcbmcv is attributed to the path-based exploration strategy combined 
+with eager path pruning and incremental SAT solving.  In the case of SoC, 
+the FW exercises only the micro-controller and transfer sequence of bytes to the XRAM port 
+bypassing peripherals connected to other ports such as hardware accelerator.  
+This scenario allows path-based exploration techniques to prune the logic for
+accelerator.  It is important to note that forward symbolic execution without
 these optimizations timeout for all the benchmarks.
 
-By contrast, \hwcbmcv is not able to prune the FW-HW transactions with
+By contrast, \hwcbmcv is not able to prune the irrelevant transactions with
 respect to a scenario due to monolithic BMC based approach.  Hence, \hwcbmcv
 passes extremely complex formulas to the underlying solver, which often
-contain irrelevant logic with respect to a particular scenario and are
-therefore difficult to solve.
+contain irrelevant logic and are therefore difficult to solve.
 
@@
 interaction pattern between FW and HW transactions can be exploited to
-generate a unified program netlist model.  To this end, we presented a
+generate a unified co-verification model.  To this end, we presented a
 path-based symbolic execution technique to automatically infer
-scenario/transaction pairs from a program netlist.  Our general observation
+scenario/transaction pairs from a co-verification model.  Our general observation
 is that monolithic BMC based approaches cannot exploit these interactions

### 2017-04-06 paper.tex
debug output paragraph

@@
 %
+%-------------------------------------------------------------------------------
+\subsection{Debugging Using Counterexample Trace}
+%-------------------------------------------------------------------------------
+A failure of co-design property implies a fault in HW or defective FW 
+or bug in the interface functions.  Hence, an important feature of a
+co-verification tool is its ability to produce a counterexample trace 
+in order to localize the bug.  \hwcbmcv generates a counterexample
+trace in value change dump (vcd) format that contains concrete assignments to FW
+variables, interface signals and HW RTL signals up to a given bound. Whereas, a
+counterexample trace in \verifox is a bounded path in the sequential co-verification
+model that contains a scenario and its corresponding HW and FW transactions. 
+%
 %===============================================================================
@@
 Table~\ref{table:safe} reports the run times for bounded safety proofs of 
-FW-HW interaction properties of the UART IP core.  Column~1 in
-Table~\ref{table:safe} gives the name of the scenario -- transmission
+co-design properties in UART IP core.  Column~1 in Table~\ref{table:safe} 
+gives the name of the scenario -- transmission
 without interrupt (transmit), transmission with interrupt (trans\_intr) and
 loopback mode (loopback).  Column~2 gives the maximum loop bound in the
-firmware.  Column~3~and~4 present the co-verification times using \hwcbmcv
-at the bit-level and word-level.  Column~7 gives the verification
-times using \verifox.  Column~5~and~6 report
-the total/feasible path counts and the percentage of infeasible paths pruned
-for each mode.  The focus of our experiment is to compare the performance of 
-path-based techniques over monolithic BMC.\\ 
+firmware.  Column~3 present the co-verification times using \hwcbmcv
+at the bit-level.  Column~4~and~5 report the total/feasible path counts and the 
+percentage of infeasible paths pruned for each scenario in \verifox.  
+Column~6 gives the verification times using \verifox.  Column~7 report 
+the verification outcome. The focus of our experiment is to compare 
+the performance of path-based technique with monolithic BMC approach for 
+co-verification.  We observe similar performance of bit-level and word-level 
+flow in \hwcbmcv. So, we only report bit-level results for \hwcbmcv in this paper. \\ 
 \textbf{\emph{Safety properties:}}
@@
 \hline
-  & Bound & \multicolumn{2}{c|}{Monolithic} & \multicolumn{3}{c|}{Path-based} \\ 
+  & & \multicolumn{1}{c|}{Monolithic} & \multicolumn{3}{c|}{Path-based} &
+  Verification \\ 
+\cline{3-6}
+  Scenario & Bound & \multicolumn{1}{c|}{HW-CBMC} & \multicolumn{3}{c|}{\verifox} &
+  Results \\ 
 \cline{3-7}
- Scenario &  & \multicolumn{2}{c|}{HW-CBMC} & \multicolumn{3}{c|}{\verifox} \\ 
-\cline{3-7}
-      &       &  Bit-level & Word-level & Total/Feasible & \%-age & $\mathcal{M}_{seq}$  \\
-%\cline{1-7}
-      &       &   Time     &   Time      & Paths & Pruning & Time \\
+      &       &  Bit-level & Total/Feasible & \%-age & $\mathcal{M}_{seq}$ &
+      Safe/Unsafe \\
+  \cline{3-3}\cline{6-6}
+      &       &   Time     & Paths & Pruning & Time &  \\
 \cline{1-7}      
 \multicolumn{7}{|c|}{non-deterministic data but deterministic control (Scenario A)} \\ \hline
-  transmit (32) & 250 & 15.02 & 15.78 & 247104/224 & 99.90 & \textbf{1}.{13} \\ 
-transmit (64) & 500 & 23.87 & 23.29 & 247104/324 & 99.86 & \textbf{1}.\textbf{61}  \\ \hline 
+  transmit (32) & 250 & 15.02 & 247104/224 & 99.90 & \textbf{1}.\textbf{13} &
+  Safe $(\psi_{c})$ \\ 
+transmit (64) & 500 & 23.87 & 247104/324 & 99.86 &
+  \textbf{1}.\textbf{61}  & Safe $(\psi_{t})$ \\ \hline 
 \multicolumn{7}{|c|}{non-deterministic data and non-deterministic control
 (Scenario B)} \\ \hline
-  trans\_intr (32) & 250 & 14.86 & 15.98 & 247104/295 & 99.88 & \textbf{1}.{49} \\
-  trans\_intr (64) & 500 & 24.14 & 26.42 & 247104/362 & 99.85 & \textbf{1}.{81} \\ \hline
+  trans\_intr (32) & 250 & 14.86 & 247104/295 & 99.88 & \textbf{1}.\textbf{49} &
+  Safe $(\psi_{t})$ \\
+  trans\_intr (64) & 500 & 24.14 & 247104/362 & 99.85 & \textbf{1}.\textbf{81}
+  & Safe $(\psi_{t})$ \\ \hline
 \multicolumn{7}{|c|}{non-deterministic data and non-deterministic control
 (scenario C)} \\ \hline
-loopback (8)  & 230 & 52.06 & 55.71 & 247104/354 & 99.85 & \textbf{3}.\textbf{95} \\ 
-loopback (16) & 500 & 122.12 & 147.65 & 247104/690 & 99.72 & \textbf{12}.\textbf{89} \\ 
-loopback (32) & 650 & 170.62 & 192.35 & 247104/1282 & 99.48 & \textbf{21}.\textbf{85}   \\ 
-loopback (64) & 1300 & 409.71 & 445.66 & 247104/2566 & 98.96 & \textbf{62}.\textbf{31}  \\ \hline
+  loopback (8)  & 230 & 52.06 & 247104/354 & 99.85 & \textbf{3}.\textbf{95} &
+  Safe $(\psi_{t})$ \\ 
+  loopback (16) & 500 & 122.12 & 247104/690 & 99.72 & \textbf{12}.\textbf{89} &
+  Safe $(\psi_{c})$ \\ 
+  loopback (32) & 650 & 170.62 & 247104/1282 & 99.48 & \textbf{21}.\textbf{85} &
+  Safe $(\psi_{c})$ \\ 
+  loopback (64) & 1300 & 409.71 & 247104/2566 & 98.96 & \textbf{62}.\textbf{31}
+  & Safe $(\psi_{t})$ \\ \hline
 \multicolumn{7}{|c|}{detecting data-path bugs in transmission mode w/o interrupt} \\ \hline
-  transmit (64) & 520 & 28.43 & 28.14 & 247104/324 & 99.86 &
-  \textbf{1}.\textbf{12} \\ \hline
+  transmit (64) & 520 & 28.43 & 247104/324 & 99.86 &
+  \textbf{1}.\textbf{12} & Unsafe $(\psi_{t})$ \\ \hline
 \multicolumn{7}{|c|}{detecting control bugs with interrupt enabled} \\ \hline
-transmit (64) & 520 & 31.35 & 29.70 & 247104/362 & 99.85 & \textbf{1}.\textbf{05} \\ \hline
+transmit (64) & 520 & 31.35 & 247104/362 & 99.85 &
+  \textbf{1}.\textbf{05} & Unsafe $(\psi_{c})$ \\ \hline
 \multicolumn{7}{|c|}{detecting control bugs in loopback mode} \\ \hline
-loopback (64) & 1300 & 443.15 & 427.68 & 247104/2566 & 98.96 & \textbf{62}.\textbf{34} \\ \hline
+  loopback (64) & 1300 & 443.15 & 247104/2566 & 98.96 & \textbf{62}.\textbf{34}
+  & Unsafe $(\psi_{t})$ \\ \hline
 \end{tabular}
@@
 %
-We obtained an open source SoC design
+We obtained an open source System-on-a-Chip design
 from~\cite{DBLP:conf/fmcad/SubramanyanVRM15}.  It consists of an 8051
@@
 XRAM addresses.  The arbitration of these module is done by 
-the memory arbiter module.  
+the memory arbiter module. \\ 
 %
@@
 %
-\Omit{
-We synthesized the SoC to a software netlist (in C).  The generated model 
-is bit-precise as well as cycle accurate.  The size of the
-software netlist is approximately~3200 LOC.  The combinatorial exchanges
-between the memory arbiter, XRAM and the AES module is modelled
-appropriately in the software netlist.
-}
-
 \textbf{\emph{About the firmware:}}
@@
 appropriate memory-mapped registers in the FW.
-
+%
 \begin{table}
@@
 \hline
-  & Bound & \multicolumn{2}{c|}{Monolithic} & \multicolumn{1}{c|}{Path-based} \\ 
+  & Bound & \multicolumn{1}{c|}{Monolithic} & \multicolumn{1}{c|}{Path-based} &
+  Verification \\ 
+\cline{3-4}
+  Scenario &  & \multicolumn{1}{c|}{\hwcbmcv} & \verifox & Result \\ 
 \cline{3-5}
- Scenario &  & \multicolumn{2}{c|}{\hwcbmcv} & \verifox \\ 
-\cline{3-5}
-      &       &  Bit-level & Word-level & $\mathcal{M}_{seq}$ \\
+      &       & Bit-level Netlist & $\mathcal{M}_{seq}$ & Safe/Unsafe \\
 \cline{1-5}
-      &       &   Time     &   Time     & Time \\
+      &       &   Time      & Time &  \\
 \cline{1-5}      
-\multicolumn{5}{|c|}{non-deterministic data and non-deterministic control (safe)} \\ \hline
-data\_transfer & 20 & 86.92 & 86.23 & \textbf{17}.\textbf{42} \\ 
-\hline
-\multicolumn{5}{|c|}{non-deterministic data and non-deterministic control
-(unsafe)} \\ \hline
-data\_transfer & 20 & 92.63 & 91.28 & \textbf{1}.\textbf{27} \\ 
+\multicolumn{5}{|c|}{non-deterministic data and non-deterministic control} \\ \hline
+  data\_transfer & 20 & 86.92 & \textbf{17}.\textbf{42} & Safe $(\psi_{t})$ \\
+  \hline
+  data\_transfer & 30 & 102.92 & \textbf{56}.\textbf{29} & Safe $(\psi_{c})$ \\ 
+\hline
+\multicolumn{5}{|c|}{non-deterministic data and non-deterministic control} \\ \hline
+  data\_transfer & 20 & 92.63 & \textbf{1}.\textbf{27} & Unsafe $(\psi_{c})$ \\ 
 \hline
@@
 \end{table}
-
+%
 \textbf{\emph{Discussion of the result:}}
@@
 Table~\ref{table:SoC} gives the runtimes for bounded safety proofs of 
-co-design properties of the SoC.  Column~1 in
+co-design properties in SoC.  Column~1 in
 Table~\ref{table:SoC} gives the name of the scenario -- transmission with
 interrupt (data\_transfer).  Column~2 report the maximum loop bound in the 
-FW.  Column~3~and~4 present the co-verification times using \hwcbmcv
-at the bit-level and word-level, respectively.  Columns~5 report the
-verification time using \verifox.
-
+FW.  Column~3 present the co-verification times using \hwcbmcv
+at the bit-level.  Columns~4 report the verification time using \verifox. 
+Column~5 report the verification outcome. \\
 \textbf{\emph{Safety properties:}}
@@
 correct result during the data transmission phase.\\ 
-
 \textbf{\emph{Detecting SoC bugs:}} We found one critical \emph{control bug} 
@@
 $5\times$ faster than \hwcbmcv for proving safety.  For detecting bugs, 
-the speedup is $72\times$ for \verifox over \hwcbmcv.
-
+the speedup is $72\times$ for \verifox over \hwcbmcv. \\ 
 \textbf{\emph{Monolithic versus Path-based:}}
@@
 This scenario allows path-based exploration techniques to prune the logic for
-accelerator.  It is important to note that forward symbolic execution without
-these optimizations timeout for all the benchmarks.
+accelerator and thereby generate only relevant scenario/transaction pairs.  It 
+is important to note that forward symbolic execution without these optimizations 
+timeout for all the benchmarks.
 
@@
 %===============================================================================
-
+\rmcmt{
 In this paper, we presented a novel HW/SW co-verification tool, \verifox,
@@
 models that exhibit further interaction patterns.
-
+}
 %\bibliographystyle{ACM-Reference-Format}

### 2017-04-06 paper.tex
conclusion

@@
 %===============================================================================
-\rmcmt{
-In this paper, we presented a novel HW/SW co-verification tool, \verifox,
-for C-based FW and hardware models given in Verilog RTL.  We presented a
-notion of transaction in joint RTL and FW models.  We showed that the
-interaction pattern between FW and HW transactions can be exploited to
-generate a unified co-verification model.  To this end, we presented a
-path-based symbolic execution technique to automatically infer
-scenario/transaction pairs from a co-verification model.  Our general observation
-is that monolithic BMC based approaches cannot exploit these interactions
-and thus generate very complex formulas, which are difficult to solve. 
+%
+In this paper, we presented two approaches for verification of 
+HW/SW co-designs using formal techniques.  These approaches are 
+embodied in our tool \hwcbmcv and \verifox.  We presented a 
+notion of scenario and transaction for effective verification 
+of co-designs.  To this end, we presented a path-based algorithm
+to automatically mine scenario/transaction pairs.  We showed that 
+the construction of a co-verification model must leverage specification of 
+co-design properties over hardware and firmware events in order to 
+successfully apply formal methods in co-verification.  To enable this, we 
+presented two types of co-design properties, \emph{transaction level} and 
+\emph{component level}.  Our tools support co-designs written in Verilog RTL 
+and C.
+
+Our general observation is that monolithic BMC based approaches 
+cannot prune irrelevant transactions with respect to a given scenario, 
+and hence generate very complex formulas, which are difficult to solve. 
 Owing to specific optimizations in \verifox such as eager path pruning
 combined with incremental SAT solving, we experimentally show that \verifox
-is an order of magnitude faster than the state-of-the-art HW/SW
-co-verification tool, \hwcbmcv.  We demonstrate applicability of our
-approach for proving safety as well as finding FW-HW bugs for a UART IP and
-a SoC design.  In the future, we plan to extend our framework to FW-HW
-models that exhibit further interaction patterns.
-}
+is an order of magnitude faster than the \hwcbmcv.  We demonstrate applicability of our
+approach for proving safety as well as finding critical co-design bugs for 
+a UART IP and a complex SoC design.  In the future, we plan to extend our 
+framework to co-design models that exhibit further interaction patterns.
+
 %\bibliographystyle{ACM-Reference-Format}

### 2017-04-06 paper.tex
minor

@@
 \end{center}
-\caption{Firmware Transactions and its interacting HW transaction}
+\caption{\small Firmware Transactions and interacting HW transactions}
 \label{transaction}
@@
 mode.\\ 
-\textbf{\emph{Detecting UART bugs:}}
+\textbf{\emph{Bug Finding:}}
 We found several bugs in the open source UART IP obtained from~\url{http://www.opencores.org}.  
@@
 correct result during the data transmission phase.\\ 
-\textbf{\emph{Detecting SoC bugs:}} We found one critical \emph{control bug} 
+\textbf{\emph{Bug Finding:}} We found one critical \emph{control bug} 
 in the SoC design.  The bug is manifested when memory arbiter hardware 

### 2017-04-07 paper.tex
minor

@@
 Concurrency is at the heart of co-verification.  Testing concurrent 
-threads requires exploring all possible interleavings between a HW 
-and FW thread.  The number of interleavings could be potentially 
+threads requires exploring all possible interleavings between HW 
+and FW threads.  The number of interleavings could potentially be  
 exponential.  However,~\cite{codes14,hvc} showed that the 
-interaction between a FW thread and HW thread follows a 
+interaction between a FW thread and a HW thread follows a 
 producer-consumer relationship. That is, a FW 
@@
 Specifically, a FW thread is only responsible for configuring the 
-HW transactions by writing to memory mapped registers or polling 
-the interrupt status register for data transmission or receiving 
+HW transactions by writing to memory mapped registers, or polling 
+the interrupt status register for data transmission, or receiving 
 incoming data packets.

### 2017-04-07 paper.tex
minor and comments

@@
 Figure~\ref{fig:interleaving1} illustrates the producer-consumer relationship 
-in UART IP. The FW CFG is shown in the left and the 
-HW RTL code snippet is shown in the right. We abuse notations and 
+in UART IP. The FW CFG is shown on the left and the 
+HW RTL code snippet is shown on the right. We abuse notations and 
 represent $\mathcal{HT}$ in the form of RTL and $\mathcal{FT}$ as CFG
-for our illustration purpose. Here, $\mathcal{HT}$ is the producer of interrupt 
+for illustration purpose. Here, $\mathcal{HT}$ is the producer of interrupt 
 status signal, $irq\_o$, which is read by $\mathcal{FT}$ in state $s_1$. 
@@
 elements (wires) are uniform in software netlist and RTL model after every invocation of 
-$next_timeframe()$.  Furthermore, a software
+$next\_timeframe()$.  Furthermore, a software
 netlist is a sequential model of HW RTL which is represented in C.  Thus, the
@@
 %
-We now formally define a our co-verification model, denoted by 
+We now formally define our co-verification model, denoted by 
 $\mathcal{M}_{seq}$.
@@
 in And Inverter Graph (AIG) format.  Whereas, a word-level netlist is represented 
-in format that resembles SMT-LIB standards.  The bottom flow illustrates the
-translation of C program into static single assignment (SSA) form. 
+in format that resembles SMT-LIB \sjcmt{which version? 1 or 2?} standard.  The bottom flow illustrates the
+translation of C program into a static single assignment (SSA) form. 
 Synthesizing netlist from RTL is a standard technique which is widely 
 used in hardware model checkers~\cite{DBLP:journals/tse/Clarke76}.
-Similarly, translating a C program into a SSA representation is a 
+Similarly, translating a C program into an SSA representation is a 
 standard technique which is widely used in 
@@
 The co-verification model is checked with bounded model checking (BMC).
-Given an unwind depth depth~$k$ and a co-design property $P$, BMC operates
+Given an unwind depth~$k$ and a co-design property $P$, BMC operates
 by unwinding the co-verification model~$M$ up to depth~$k$ starting from
@@
 Thus, BMC exploits the finiteness of $M$ and creates k copies of the
-$M$ for each unrolling.
+$M$ for each unrolling \sjcmt{not always true}.
 

### 2017-04-07 paper.tex
minor

@@
 A {\em Transaction level} property ($\psi_{t}$) formally captures the 
-design intent of the interaction between a $\mathcal{ST}$ and $\mathcal{HT}$, 
+design intent of the interaction between a $\mathcal{ST}$\sjcmt{shouldn't it be FT?} and $\mathcal{HT}$, 
 that is, it is defined at the transaction boundaries.  
@@
 shows an example of component level property for the UART HW only.  The 
-System Verilog Assertion (SVA) is shown in the left and the equivalent 
-monitor in C is shown in right.  
+System Verilog Assertion (SVA) is shown on the left and the equivalent 
+monitor in C is shown on the right.  
 %
@@
 %-------------------------------------------------------------------------------
-A failure of co-design property implies a fault in HW or defective FW 
-or bug in the interface functions.  Hence, an important feature of a
+A failure of co-design property implies a fault in HW, or a defective FW, 
+or a bug in the interface functions.  Hence, an important feature of a
 co-verification tool is its ability to produce a counterexample trace 

### 2017-04-07 paper.tex
minor, typo, comments

@@
 We report experimental results for FW-HW co-verification of a UART IP and a
-SoC design.  All our experiments were performed on an Intel Xeon 3.07\,GHz
+SoC design.  All our experiments were performed on an Intel\textsuperscript{\textregistered} Xeon\textsuperscript{\textregistered} 3.07\,GHz
 machine with 48\,GB RAM.  All times reported are in seconds.  The timeout 
@@
 co-verification.  We observe similar performance of bit-level and word-level 
-flow in \hwcbmcv. So, we only report bit-level results for \hwcbmcv in this paper. \\ 
+flow in \hwcbmcv. So, we only report bit-level results for \hwcbmcv in this paper. \sjcmt{I think this can backfire. The reivewers may ask why were other results not reported if available}\\ 
 \textbf{\emph{Safety properties:}}
@@
 serial output of the transmitter.  However, when the interrupt is enabled
-during transmission mode, the bug in the control-path of the transmitter
+during the transmission mode, the bug in the control-path of the transmitter
 module is triggered which deactivates the transmitter $empty$ signal.  This
@@
 monolithic BMC in all scenarios (marked bold).  The average speedup for
-proving safety properties is on average $21\times$ for \verifox over
+proving safety properties is on average $21\times$ \sjcmt{is it average for table 3 only? or also table 4?} for \verifox over
 \hwcbmcv.  The average speedup for detecting bugs is $48\times$ on average 
@@
 %
-We obtained an open source System-on-a-Chip design
+We obtained an open source System-on-a-Chip \sjcmt{or is it System-on-Chip?} design
 from~\cite{DBLP:conf/fmcad/SubramanyanVRM15}.  It consists of an 8051
@@
 Table~\ref{table:stats}.  The accelerator implements encryption/decryption 
-using the Advanced Encryption Standard (AES).  There is a separate 
+using the Advanced Encryption Standard (AES) \sjcmt{cite if possible}.  There is a separate 
 module that interfaces the AES to the 8051 micro-controller using 
@@
 %
+
 \textbf{\emph{Discussion of the result:}}
@@
 from the micro-controller in the correct cycle.  We verify whether the
-non-deterministic data transmitted through $outb()$ is the same
+non-deterministic data transmitted through $outb()$ is the same as 
 the data received through $inb()$.  We also verify that
@@
 is not applicable for co-designs that exhibits true concurrency~\cite{concurrency}, 
-that is, a FW its interacting HW threads do not show producer-consumer relationship.  
+that is, a FW and its interacting HW threads do not show producer-consumer relationship.  
 In this case, it is imperative to consider all possible interleavings between participating 
-threads in an effecient manner.  However, our experience is that such 
-co-designs occurs rarely in practise.
+threads in an efficient manner.  However, our experience is that such 
+co-designs occur rarely in practise.
 

### 2017-04-07 paper.tex
minor

@@
 model a hardware and PDS to abstractly model a software to generate a unified SW-HW model, 
-called Buchi Pushdown System ({\em BPDS}).  In this paper, we construct an unified 
+called Buchi Pushdown System ({\em BPDS}).  In this paper, we construct a unified 
 sequential co-verification model in C which enable us to automatically 
@@
 HW/SW co-designs using formal techniques.  These approaches are 
-embodied in our tool \hwcbmcv and \verifox.  We presented a 
+embodied in our tools \hwcbmcv and \verifox.  We presented a 
 notion of scenario and transaction for effective verification 

### 2017-04-07 paper.tex
conclusion

@@
 \newcommand{\verifoxver}{\tool{VerifOx 0.1}}
-\newcommand{\verifox}{\tool{CoVeriIf}}
+\newcommand{\verifox}{\tool{CoVerIf}}
 \newcommand{\iimc}{\tool{iimc}}
@@
 simulation with custom path-pruning.  We have implemented this approach in 
-our tool \verifox.  We have experimentally compared \verifox with a
-conventional approach, which constructs a single monolithic SAT/SMT
-instance, and observe speedup of an order of magnitude over conventional 
-approach for proving safety properties as well as detecting firmware/hardware bugs.
+our tool \verifox.  We have experimentally compared \verifox with \hwcbmcv, 
+which constructs a single monolithic SAT/SMT instance, and observe speedup of 
+an order of magnitude over \hwcbmcv for proving safety properties as well as 
+detecting firmware/hardware bugs.
 %
@@
 this interaction behavior in a sequential co-verification model through symbolic 
-execution which generates relevant scenario/transaction pairs.  However, this approach 
-is not applicable for co-designs that exhibits true concurrency~\cite{concurrency}, 
+execution by generating relevant scenario/transaction pairs.  However, this approach 
+is not applicable for co-designs that exhibits true concurrency~\cite{codesign}, 
 that is, a FW and its interacting HW threads do not show producer-consumer relationship.  
 In this case, it is imperative to consider all possible interleavings between participating 
-threads in an efficient manner.  However, our experience is that such 
-co-designs occur rarely in practise.
+threads in an efficient manner.  Fortunately, a producer-consumer interaction pattern is
+prevelant in many practical co-designs~\cite{polig2014micro,polig2014fpl,giefers2015accelerating,hvc}.
 
@@
 %
-In this paper, we presented two approaches for verification of 
-HW/SW co-designs using formal techniques.  These approaches are 
-embodied in our tools \hwcbmcv and \verifox.  We presented a 
-notion of scenario and transaction for effective verification 
-of co-designs.  To this end, we presented a path-based algorithm
-to automatically mine scenario/transaction pairs.  We showed that 
-the construction of a co-verification model must leverage specification of 
-co-design properties over hardware and firmware events in order to 
-successfully apply formal methods in co-verification.  To enable this, we 
-presented two types of co-design properties, \emph{transaction level} and 
-\emph{component level}.  Our tools support co-designs written in Verilog RTL 
-and C.
-
-Our general observation is that monolithic BMC based approaches 
+In this paper, we presented two different approaches for formal verification of 
+HW/SW co-designs -- \emph{monolithic} and \emph{path-based}.  These approaches are 
+embodied in \hwcbmcv and \verifox.  Our tools support co-designs written 
+in Verilog RTL and C.  We also presented a specification language to 
+effectively capture co-design properties.  To this end, we classify co-design 
+properties into two types --  \emph{transaction level} and \emph{component level} 
+property.  We successfully demonstrate the application of \hwcbmcv and \verifox 
+for proving safety as well as finding critical co-design bugs for 
+a UART IP and a complex SoC design.
+
+A FW exercises only a fragment of the HW state-space for a given scenario.  
+This renders many interactions between HW and FW transactions infeasible.   
+Our general observation is that bounded model checking technique in \hwcbmcv 
 cannot prune irrelevant transactions with respect to a given scenario, 
-and hence generate very complex formulas, which are difficult to solve. 
-Owing to specific optimizations in \verifox such as eager path pruning
-combined with incremental SAT solving, we experimentally show that \verifox
-is an order of magnitude faster than the \hwcbmcv.  We demonstrate applicability of our
-approach for proving safety as well as finding critical co-design bugs for 
-a UART IP and a complex SoC design.  In the future, we plan to extend our 
+and hence generate a monolithic co-verification model, which are often 
+extremely difficult to solve with a SAT/SMT solver. On the other hand, 
+a path-based exploration strategy in \verifox is able to automatically 
+mine relevant scenario/transaction pairs in a sequential co-verification 
+model, owing to specific optimizations such as eager path pruning
+combined with incremental SAT solving.  Our experiments show that \verifox 
+is an order of magnitude faster than \hwcbmcv for proving safety as well as 
+bug finding.  In the future, we plan to extend our 
 framework to co-design models that exhibit further interaction patterns.

### 2017-04-07 paper.tex
fixes

--- 2017-04-07 paper.tex
@@
 post-RTL.  In the pre-RTL phase,
-engineers write high-level software (SW) models for Intellectual Property (IP), 
+engineers write high-level software (SW) models for Intellectual Property (), 
 which are commonly known as {\em Transaction Level Model}s
@@
 enough functionality of the hardware (HW) such that it is possible to execute the
-SW (drivers/firmware) against it.  Consequently, the TLMs are
+SW (drivers or firmware (FW)) against it.  Consequently, the TLMs are
 incomplete, as they are designed to contain only those behaviors that are
-observable by the SW (the drivers or firmware).  In particular, TLMs
+observable by the SW (the drivers or FW).  In particular, TLMs
 are often not cycle-accurate.  These models are used to verify high-level
@@
 timing.  The effectiveness of testing 
-is thus severely limited in post-RTL co-verification. Verification is mandatory to ensure that the driver or firmware (FW) 
-is executed correctly together with the RTL.
+is thus severely limited in post-RTL co-verification. Verification is mandatory
+to ensure that the driver or FW is executed correctly together with the RTL.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The verification of a FW given in C/C++ together with an RTL given in a hardware
-description language (HDL) such as Verilog/VHDL is a challenging task due to a
+The verification of a FW given in C/C++ together with an RTL given in 
+Verilog/VHDL is a challenging task due to a
 few reasons -- 1) the timing and semantic mismatch between the synchronous
@@
 FW running on a processor could be much faster than the HW
-model it interacts with, 2) lack of support for property specification in 
-HW/FW co-designs that can precisely capture the design intent of the 
-communication between HW and FW, 3) large
+model it interacts with, 2) lack of support for property specification of 
+co-designs that can precisely capture the design intent of the 
+communication between FW and HW, 3) large
 number of interleavings between HW and FW threads, and 4) lack 
 of automated formal tools that support co-designs implemented in C/C++ and 
-Verilog/VHDL.   In this paper, we address some of these challenges to enable
-seamless adoption of formal techniques in hardware/software co-verification.
+Verilog/VHDL.   In this paper, we address some of these challenges to apply 
+formal techniques in hardware/software co-verification.
 
@@
 Generating a unified FW-HW model for co-verification is a 
-well-known phenomenon to handle the semantic mismatch between  
+well-known technique to handle the semantic mismatch between  
 HW~\footnote{Note that whenever we refer to ``hardware'' 
@@
 and not a TLM.}  and FW models.  Most of the existing techniques 
-in~\cite{fmsd02,emsoft07,fase10} for constructing a unified FW-HW model are not 
-useful in practise for three reasons -- 1) use of abstract HW models 
-instead of RTL implementation, 2) the HW-FW model
+for constructing a unified FW-HW model~\cite{fmsd02,emsoft07,fase10} 
+are not useful in practise for three reasons -- 1) use of abstract HW models 
+instead of RTL implementation, 2) the unified model
 construction is agnostic to the underlying reasoning engine, and 3) 
-it does not leverage the property specification over HW-FW boundary, hence 
-ineffective for practical co-verification.  We will call the unified FW-HW 
-model as \emph{co-verification model}.
-
-In this paper, we present two different approaches for automatic formal
-verification of HW/SW co-designs -- \emph{monolithic} and \emph{path-based}.  
-We embody these techniques in our tools, \hwcbmcv and \verifox, respectively.
+the unified model does not leverage property specification over the
+interaction between a FW and HW, hence ineffective for practical co-verification.  
+We will call the unified FW-HW model as \emph{co-verification model}.
+
+In this paper, we present two different approaches for constructing a
+co-verification model.  Based on the type of the co-verification model, 
+we employ specific bounded verification algorithm to reason about these models
+-- \emph{monolithic} and \emph{path-based}.  We embody these techniques 
+in our tools, \hwcbmcv and \verifox, respectively.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-A firmware only exercises a fraction of the hardware state-space in a typical 
-hardware/software
+A FW only exercises a fraction of the HW state-space in a typical 
 co-design~\cite{polig2014micro,polig2014fpl,giefers2015accelerating}.  
-A firmware services the requests from the application software 
+A FW services the requests from the application software 
 layer or its interacting hardware.  Similarly, the hardware services 
-the requests from the firmware or the
-physical environment.  Thus, the firmware and its interacting hardware
+the requests from the FW or the
+physical environment.  Thus, the FW and its interacting hardware
 components can be seen as a set of services.  In this paper, we call a
@@
 $\mathcal{HT}$ and $\mathcal{FT}$ infeasible. For example, a scenario in 
-\emph{Universal Asynchronous Receiver Transmitter} (UART) IP can configure the 
+\emph{Universal Asynchronous Receiver Transmitter} (UART)  can configure the 
 UART in \emph{transmitter} mode which restricts the communication between the FW 
@@
 hence it cannot exploit the infeasibility arising from scenario driven
-partitioning of HW-FW interaction behaviors.  Whereas, a path-based symbolic 
-execution in \verifox can automatically infer such Scenario/Transaction 
-pairs and check their validity using backend solvers.  We experimentally 
-show that for building an effective and scalable formal co-verification tool, 
-it is imperative to automatically mine only relevant scenario/transaction 
-pairs that occur in practical co-design environment. 
+partitioning of FW-HW interaction behaviors.  On the other hand, a 
+path-based symbolic execution in \verifox can automatically infer 
+such Scenario/Transaction pairs and check their validity using backend 
+solvers.  We experimentally show that for building an effective and 
+scalable formal co-verification tool, it is imperative to automatically 
+mine only relevant scenario/transaction pairs that occur in practical 
+co-design environment. 
 %
@@
 and HW threads can be large, which can become a bottleneck in the
-verification process.  
-However, we observe that in practice, industrial co-designs exhibit 
-producer-consumer
-relationships~\cite{polig2014micro,polig2014fpl,giefers2015accelerating} --
+verification process.  However, we observe that in practice, 
+producer-consumer relationship is prevelant in many industrial 
+co-designs~\cite{polig2014micro,polig2014fpl,giefers2015accelerating} --
 the master module (producer) solely updates the shared registers which are
 consumed by the slave (consumer).  This key observation allows us to
-sequentialize concurrent FW and HW models \sjcmt{transactions instead of models?} that follow specific interaction
+sequentialize concurrent FW and HW transactions that follow specific interaction
 patterns.  This drastically reduces the total number of interleavings 
@@
 
-  \item \textbf{Co-verification Tools:} We present an automatic HW/SW co-verification tool called, \hwcbmcv,
-    which follows the monolithic verification technique.  Our path-based 
-    approach is implemented in a tool called, \verifox. Both tools can handle
-    co-designs where the hardware is implemented in Verilog RTL (IEEE
-    SystemVerilog 2005 standards) and the firmware is  
+  \item \textbf{Co-verification Tools:} We present an automatic HW/SW co-verification 
+    tool called, \hwcbmcv, which implements the monolithic verification technique 
+    using bounded model checking.  Our path-based approach is implemented in a tool 
+    called, \verifox. Both tools can handle co-designs where the hardware is 
+    implemented in Verilog RTL (IEEE SystemVerilog 2005 standards) and the firmware is  
     specified in ANSI-C (C89, C99 standards).  We distribute the HW/SW 
     co-verification tools, \hwcbmcv and \verifox, along with our co-design 
-    benchmarks in Verilog RTL and C models 
+    benchmarks in Verilog RTL and C 
     here~\footnote{https://drive.google.com/folderview?id=0BynC6sd-wTYgWVQ4bXNtRDB5a2c\&usp=sharing}.\rmcmt{check
@@
 \textbf{Firmware Model} Figure~\ref{firmware} gives a fragment of a FW model for a Universal 
-Asynchronous Transmitter/ Receiver (UART) IP.  The
+Asynchronous Transmitter/ Receiver.  The
 $wb$ class of functions communicate with the {\em wishbone} bus interface to
@@
 invokes the $wb$ functions to communicate with the UART.  The FW begins 
-by resetting the UART IP which is followed by a $wb\_idle()$ function.  The 
+by resetting the UART  which is followed by a $wb\_idle()$ function.  The 
 FW then configures the UART in {\em loopback} mode using $outb$ function calls. 
-Inside the loop, the firmware checks for a {\em transmitter} or {\em
+Inside the loop, the FW checks for a {\em transmitter} or {\em
 receiver} interrupt by reading the Interrupt Status register $(UART\_IS)$. 
-Depending on the type of interrupt, the firmware either receives a data packet 
+Depending on the type of interrupt, the FW either receives a data packet 
 or sends a data packet over the serial output.  The $set\_inputs()$ and
 $next\_timeframe()$ functions, used in $wb$ functions, are 
-firmware primitives that direct our tool to set the inputs to the HW signals 
+FW primitives that direct our tool to set the inputs to the HW signals 
 and advance the HW clock, respectively.
@@
 \textbf{Hardware Model} Figure~\ref{fig:interleaving2} shows a fragment of the state machine 
-implementation of the UART hardware RTL.  The UART IP contains a
+implementation of the UART hardware RTL.  The UART  contains a
 \emph{transmitter} module, a \emph{receiver} module and a \emph{clock
@@
 array containers $rx\_b$ and $tx\_b$ stores the data obtained through the $inb$
-and $outb$ function calls which directly read from and write to the UART IP ports
-respectively. Section~\ref{property} describes the property specification in
-HW-FW co-designs in more detail. 
+and $outb$ function calls which read from and write to the UART  ports
+respectively. Section~\ref{property} describes the property specification for 
+co-designs in more detail. 
 \[
@@
 \end{tabular}
-\caption{Firmware model of UART IP}
+\caption{Firmware model of UART }
 \label{firmware} 
@@
 gives an example scenario for the UART FW shown in Figure~\ref{firmware}. 
-Here, $\mathcal{S}$ configures the UART IP in {\em loopback} mode with 
+Here, $\mathcal{S}$ configures the UART  in {\em loopback} mode with 
 interrupt enabled.
@@
 defines all the behaviors required of the system. For example, 
-a use case in case of UART IP may be to transmit 
+a use case in case of UART  may be to transmit 
 the data through the serial port. A scenario is an 
@@
 The path taken by an execution is determined by the state of 
-the FW variables or its interacting HW signals. Repeated execution of 
-$\mathcal{FT}$ can happen only in a sequential manner \sjcmt{not clear what this means}.
+the FW variables or its interacting HW signals.
 
@@
 $\varphi$ with a unique source vertex, $init \in V$, and a unique sink vertex, 
-$comp \in V$, $\Sigma$ is a set of labels such that $\Sigma \subseteq 2^{G}$ \sjcmt{2 power G may not be required, just G may be sufficient as it is closed under disjunction, conjunction and negation} and
-$\rightarrow \subseteq V \times \Sigma \times V$ is a set of labelled
+$comp \in V$, $\Sigma$ is a set of labels such that $\Sigma \subseteq
+2^{\mathcal{G}}$ and $\rightarrow \subseteq V \times \Sigma \times V$ is a set of labelled
 transitions.
@@
 Figure~\ref{fig:interleaving2} shows a fragment of $\mathcal{HT}$
-corresponding to the top module of UART IP.  Let us consider a possible
+corresponding to the top module of UART .  Let us consider a possible
 execution of $\mathcal{HT}$, $(init \rightarrow t_1 \rightarrow t_4
@@
 interactions between $\mathcal{HT}$ and $\mathcal{FT}$ for a
-particular~$\mathcal{S}$.  For example, an UART IP contains a {\em
+particular~$\mathcal{S}$.  For example, an UART  contains a {\em
 transmitter} and a {\em receiver} module.  Let us assume that a scenario,
@@
 A hardware circuit in Verilog RTL is automatically 
-translated into a word level C program, called a 
+translated into a C program, called a 
 \textit{software netlist}~\cite{mtk2016,mskm2016,mkm2015} following synthesis 
-semantics \sjcmt{ref for synthesis semantics?}. The software netlist model is cycle-accurate as well as 
+semantics. The software netlist model is cycle-accurate as well as 
 bit-precise~\footnote{http://www.cprover.org/hardware/v2c/}. The 
@@
 in Verilog such as procedural blocks and continuous assignments, multiple {\em always}
-blocks, multiple modules, and translates them into an equivalent \sjcmt{we should specify equivalent in what sense} C program.  This
-is a radically new but promising approach for synthesizing software 
-models from RTL description, primarily targeted for word-level formal hardware 
-verification using software verification techniques such as abstract 
-satisfaction\sjcmt{?}~\cite{leo-thesis}.  To the best of our knowledge, this is the first 
-attempt to demonstrate the efficacy of such a translation in the context of 
-hardware/software co-verification. 
+blocks, and communication between modules.  This is a radically new 
+but promising approach for synthesizing software 
+models from RTL description, primarily targeted for word-level formal verification.  
+To the best of our knowledge, this is the first attempt to demonstrate the 
+efficacy of such a translation in the context of hardware/software co-verification. 
 % 
@@
 %
-Here, $\mathit{In}$ \sjcmt{this is missing from the def}, $\mathit{Out}$, $\mathit{Seq}$, $\mathit{Comb}$
+Here, $\mathit{Out}$, $\mathit{Seq}$, $\mathit{Comb}$
 are program variables that model \emph{input}, \emph{output}, 
@@
 to $Out$, $Seq$ and $Comb$. Figure~\ref{ex1} shows an example of 
-Verilog RTL circuit containing an {\em always} block and continuous
-assignment statements, and the equivalent software netlist in C.
+Verilog RTL circuit containing both sequential and combinational 
+elements. Column~2,3 in Figure~\ref{ex1} shows the formal semantics 
+of the Verilog RTL and the synthesized HW respectively.  The equivalent 
+software netlist model is shown in column~4.
 %
@@
 Concurrency is at the heart of co-verification.  Testing concurrent 
-threads requires exploring all possible interleavings between HW 
-and FW threads.  The number of interleavings could potentially be  
+threads requires exploring all possible interleavings between a HW 
+and FW thread.  The number of interleavings could be potentially 
 exponential.  However,~\cite{codes14,hvc} showed that the 
-interaction between a FW thread and a HW thread follows a 
+interaction between a FW thread and HW thread follows a 
 producer-consumer relationship. That is, a FW 
@@
 Specifically, a FW thread is only responsible for configuring the 
-HW transactions by writing to memory mapped registers, or polling 
-the interrupt status register for data transmission, or receiving 
+HW transactions by writing to memory mapped registers or polling 
+the interrupt status register for data transmission or receiving 
 incoming data packets.
@@
 Media Player~\cite{hvc}, linux device driver interacting with QEMU emulated
-hardware code~\cite{codes14}.
+hardware code~\cite{codes14}. In this paper, we verify co-designs that 
+exhibits producer-consumer interaction behavior.
 
@@
 Figure~\ref{fig:interleaving1} illustrates the producer-consumer relationship 
-in UART IP. The FW CFG is shown on the left and the 
-HW RTL code snippet is shown on the right. We abuse notations and 
+in UART . The FW CFG is shown in the left and the 
+HW RTL code snippet is shown in the right. We abuse notations and 
 represent $\mathcal{HT}$ in the form of RTL and $\mathcal{FT}$ as CFG
-for illustration purpose. Here, $\mathcal{HT}$ is the producer of interrupt 
+for our illustration purpose. Here, $\mathcal{HT}$ is the producer of interrupt 
 status signal, $irq\_o$, which is read by $\mathcal{FT}$ in state $s_1$. 
@@
 %
+
 Table~\ref{transaction} shows the FW transactions $(\mathcal{FT})$ and its 
@@
 An unified co-verification model is constructed through appropriate composition of 
-FW and its interacting HW threads.  This is done by instrumenting the 
-software netlist model of HW RTL inside the FW thread at every invocation 
+FW and its interacting HW transaction.  This is done by instrumenting the 
+software netlist model of HW RTL inside the FW transaction at every invocation 
 of the $next\_timeframe()$ primitive in interface functions.  Recall that a
@@
 to the software netlist emulates the effect of one clock period in the RTL 
-model. That is, the state of state holding elements (registers) and combinational 
+model. That is, the configuration of state holding elements (registers) and combinational 
 elements (wires) are uniform in software netlist and RTL model after every invocation of 
@@
 %
-We now formally define our co-verification model, denoted by 
+We now formally define a our co-verification model, denoted by 
 $\mathcal{M}_{seq}$.
@@
 FW to communicate with $\mathcal{SN}$.  Figure~\ref{compose} shows the 
-composition of $\mathcal{SN}$ and FW thread for the UART IP.
+composition of $\mathcal{SN}$ and FW transaction for UART.
 %
@@
 \scalebox{.50}{\import{figures/}{compose.pspdftex}}
-  \caption{Composition of FW and HW threads}
+  \caption{Composition of FW and HW transactions}
 \label{compose}
@@
 in And Inverter Graph (AIG) format.  Whereas, a word-level netlist is represented 
-in format that resembles SMT-LIB \sjcmt{which version? 1 or 2?} standard.  The bottom flow illustrates the
-translation of C program into a static single assignment (SSA) form. 
+in format that resembles SMT-LIB2
+standards~\footnote{http://smtlib.cs.uiowa.edu/}.  The bottom flow illustrates the
+translation of C program into static single assignment (SSA) form. 
 Synthesizing netlist from RTL is a standard technique which is widely 
 used in hardware model checkers~\cite{DBLP:journals/tse/Clarke76}.
-Similarly, translating a C program into an SSA representation is a 
+Similarly, translating a C program into a SSA representation is a 
 standard technique which is widely used in 
@@
 The co-verification model is checked with bounded model checking (BMC).
-Given an unwind depth~$k$ and a co-design property $P$, BMC operates
+Given an unwind depth depth~$k$ and a co-design property $P$, BMC operates
 by unwinding the co-verification model~$M$ up to depth~$k$ starting from
@@
 Thus, BMC exploits the finiteness of $M$ and creates k copies of the
-$M$ for each unrolling \sjcmt{not always true}.
+$M$ for each unrolling.
 
@@
 \textbf{Step 3: Scenario/Transaction Pair} In \hwcbmcv, the symbolic execution 
-of HW and FW components meet only at the solver phase.  Thus, a complex
-monolithic formula is passed on to the solver for verification purpose.  This
-limits the opportunity for extracting relevant scenario/transaction pairs
-through symbolic execution. Instead, the technique relies on the underlying
-SAT/SMT solver to effeciently reason about the co-verification model. 
+of HW and FW models are clearly separate and the two flow meet only at the
+solver phase, where a complex monolithic formula is generated in 
+Conjunctive Normal Form (CNF) from the AIG and SSA.  This complex formula 
+is passed on to the solver for verification purpose.  
+Hence, the verification flow in \hwcbmcv limits the opportunity for extracting 
+relevant scenario/transaction pairs through symbolic execution.  Instead, the 
+technique relies on the underlying SAT/SMT solver to effeciently reason about 
+the co-verification model. 
 %
@@
 A {\em Transaction level} property ($\psi_{t}$) formally captures the 
-design intent of the interaction between a $\mathcal{ST}$\sjcmt{shouldn't it be FT?} and $\mathcal{HT}$, 
+design intent of the interaction between a $\mathcal{FT}$ and $\mathcal{HT}$, 
 that is, it is defined at the transaction boundaries.  
-Recall that a $\mathcal{ST}$ is a service in response to some external environment 
+Recall that a $\mathcal{FT}$ is a service in response to some external environment 
 or HW interrupts (for example acknowledgement or exceptions). Similarly, 
@@
 Thus, a transaction level property follows implication structure -- the 
-antecedent of the implication is an event in $\mathcal{ST}$ or 
+antecedent of the implication is an event in $\mathcal{FT}$ or 
 $\mathcal{HT}$ and the consequent is an event in $\mathcal{HT}$ 
-or $\mathcal{ST}$ respectively.  An event in $\mathcal{ST}$ may be 
+or $\mathcal{FT}$ respectively.  An event in $\mathcal{FT}$ may be 
 a function call or an update to program variables. Similarly, an event in 
@@
 elements. Figure~\ref{figure:transaction} shows an example of transaction 
-level property, written as monitors in C, for the UART IP.  In $monitor\_P1()$, 
-$outb(UART\_TR,0x0c)$ is a FW event and $ack\_o$ is a HW event. Whereas in
-$monitor\_P2()$, the antecedent $tx\_empty()$ is a HW event and $send\_data$ is a FW
-event. 
+level property, written as monitors in C, for UART.  In $monitor\_P1()$, 
+$outb(UART\_TR,0x0c)$ is a FW event and $ack\_o$ is a HW event (marked in bold).  
+Whereas in $monitor\_P2()$, the antecedent $tx\_empty()$ is a HW event and 
+$send\_data$ is a FW event (marked in bold). 
 %
@@
 shows an example of component level property for the UART HW only.  The 
-System Verilog Assertion (SVA) is shown on the left and the equivalent 
-monitor in C is shown on the right.  
+System Verilog Assertion (SVA) is shown in the left and the equivalent 
+monitor in C is shown in right.  
 %
@@
 %-------------------------------------------------------------------------------
-A failure of co-design property implies a fault in HW, or a defective FW, 
-or a bug in the interface functions.  Hence, an important feature of a
+A failure of co-design property implies a fault in HW or a defective FW 
+or bug in the interface functions.  Hence, an important feature of a
 co-verification tool is its ability to produce a counterexample trace 
@@
 %
-We report experimental results for FW-HW co-verification of a UART IP and a
-SoC design.  All our experiments were performed on an Intel\textsuperscript{\textregistered} Xeon\textsuperscript{\textregistered} 3.07\,GHz
+We report experimental results for FW-HW co-verification of a UART  and a
+SoC design.  All our experiments were performed on an Intel Xeon 3.07\,GHz
 machine with 48\,GB RAM.  All times reported are in seconds.  The timeout 
@@
 
-\textbf{\emph{About UART:}} A UART IP core is used for asynchronous
+\textbf{\emph{About UART:}} A UART  core is used for asynchronous
 transmission and reception of data which provides serial communication
-capabilities with a modem or other external devices.  The UART IP is
+capabilities with a modem or other external devices.  The UART  is
 compliant with industry standards for UART and interfaces with the wishbone
@@
 {
-\scriptsize
+\small
 \begin{tabular}{|c|c|c|c|c|c|c|}
@@
 \end{center}
-\caption{Design statistics for UART IP and SoC Design}
+\caption{Design statistics for UART and SoC Design}
 \label{table:stats}
@@
 %
-\textbf{\emph{UART Configuration:}} The UART IP core is configured in
+\textbf{\emph{UART Configuration:}} The UART  core is configured in
 different operating modes, namely--{\em transmission without interrupt
@@
 Table~\ref{table:safe} reports the run times for bounded safety proofs of 
-co-design properties in UART IP core.  Column~1 in Table~\ref{table:safe} 
+co-design properties in UART  core.  Column~1 in Table~\ref{table:safe} 
 gives the name of the scenario -- transmission
@@
 co-verification.  We observe similar performance of bit-level and word-level 
-flow in \hwcbmcv. So, we only report bit-level results for \hwcbmcv in this paper. \sjcmt{I think this can backfire. The reivewers may ask why were other results not reported if available}\\ 
+flow in \hwcbmcv. So, we only report bit-level results for \hwcbmcv in this paper. \\ 
 \textbf{\emph{Safety properties:}}
 We verify a total of~17 transaction level properties and~22 component level 
-properties of the UART IP.  Table~\ref{table:safe} reports some of the
+properties of the UART .  Table~\ref{table:safe} reports some of the
 representative properties.  In Scenario~A and scenario~B, we verified whether
@@
 \textbf{\emph{Bug Finding:}}
-We found several bugs in the open source UART IP obtained from~\url{http://www.opencores.org}.  
+We found several bugs in the open source UART  obtained from~\url{http://www.opencores.org}.  
 The bottom part of Table~\ref{table:safe} reports the verification
-times for detecting data-path and control-path bugs in UART IP.  
+times for detecting data-path and control-path bugs in UART .  
 The bug in the UART data-path is manifested in the transmission mode when no
@@
 serial output of the transmitter.  However, when the interrupt is enabled
-during the transmission mode, the bug in the control-path of the transmitter
+during transmission mode, the bug in the control-path of the transmitter
 module is triggered which deactivates the transmitter $empty$ signal.  This
@@
 monolithic BMC in all scenarios (marked bold).  The average speedup for
-proving safety properties is on average $21\times$ \sjcmt{is it average for table 3 only? or also table 4?} for \verifox over
+proving safety properties is on average $21\times$ for \verifox over
 \hwcbmcv.  The average speedup for detecting bugs is $48\times$ on average 
@@
 %
-We obtained an open source System-on-a-Chip \sjcmt{or is it System-on-Chip?} design
+We obtained an open source System-on-Chip design
 from~\cite{DBLP:conf/fmcad/SubramanyanVRM15}.  It consists of an 8051
@@
 Table~\ref{table:stats}.  The accelerator implements encryption/decryption 
-using the Advanced Encryption Standard (AES) \sjcmt{cite if possible}.  There is a separate 
+using the Advanced Encryption Standard (AES).  There is a separate 
 module that interfaces the AES to the 8051 micro-controller using 
@@
 %
-
 \textbf{\emph{Discussion of the result:}}
@@
 from the micro-controller in the correct cycle.  We verify whether the
-non-deterministic data transmitted through $outb()$ is the same as 
+non-deterministic data transmitted through $outb()$ is the same
 the data received through $inb()$.  We also verify that
@@
 is not applicable for co-designs that exhibits true concurrency~\cite{concurrency}, 
-that is, a FW and its interacting HW threads do not show producer-consumer relationship.  
+that is, a FW its interacting HW threads do not show producer-consumer relationship.  
 In this case, it is imperative to consider all possible interleavings between participating 
-threads in an efficient manner.  However, our experience is that such 
-co-designs occur rarely in practise.
+threads in an effecient manner.  However, our experience is that such 
+co-designs occurs rarely in practise.
 
@@
 that this producer-consumer interaction pattern is not specific to the UART
-IP or SoC designs used as exemplars in this paper.  Malik et
+ or SoC designs used as exemplars in this paper.  Malik et
 al.~in~\cite{hvc} showed that these patterns are meaningful in further
@@
 approach for proving safety as well as finding critical co-design bugs for 
-a UART IP and a complex SoC design.  In the future, we plan to extend our 
+a UART  and a complex SoC design.  In the future, we plan to extend our 
 framework to co-design models that exhibit further interaction patterns.

### 2017-04-07 verifox.tex
minor and comments
fixes

@@
 then $\mathcal{M}_{seq}$ is said to have violated the property.
-\rmcmt{mark algo with FT and HT scenario transaction pair}
 
@@
 
-Eager infeasibility check restrict the search to explore
+Eager infeasibility check restricts the search to explore
 only those FW/HW interations which are feasible under a

### 2017-04-07 paper.tex
fixes

@@
 phases in the design cycle: pre-Register Transfer Level (pre-RTL) and 
-post-RTL.  In the pre-RTL phase,
-engineers write high-level software (SW) models for Intellectual Property (), 
-which are commonly known as {\em Transaction Level Model}s
-(TLM)~\cite{codes14}.  TLMs are typically implemented using the SystemC TLM
+post-RTL.  In the pre-RTL phase, engineers write high-level 
+software (SW) models for Intellectual Property, which are commonly 
+known as {\em Transaction Level Model}s (TLM)~\cite{codes14}.  The 
+TLM models are used to verify high-level functionality of the 
+system well before the RTL is available~\cite{codes14,codes15}. 
+Co-verification of the TLM and the SW is typically performed 
+by means of testing~\cite{hvc,codes14}.
+
+\Omit{
+TLMs are typically implemented using the SystemC TLM
 library~\cite{tlm} or as plain C programs.  The goal of a TLM is to capture
@@
 SW is typically performed by means of testing~\cite{hvc,codes14}.
+}
 
@@
 of automated formal tools that support co-designs implemented in C/C++ and 
-Verilog/VHDL.   In this paper, we address some of these challenges to apply 
-formal techniques in hardware/software co-verification.
+Verilog/VHDL.   In this paper, we address some of these challenges in 
+hardware/software co-verification at post-RTL phase.
 
@@
 Concurrency is at the heart of co-verification.  Testing concurrent 
-threads requires exploring all possible interleavings between a HW 
-and FW thread.  The number of interleavings could be potentially 
-exponential.  However,~\cite{codes14,hvc} showed that the 
-interaction between a FW thread and HW thread follows a 
-producer-consumer relationship. That is, a FW 
-thread is mostly independent of the HW thread they interact with~\cite{hvc,codes14}.  
-Specifically, a FW thread is only responsible for configuring the 
-HW transactions by writing to memory mapped registers or polling 
-the interrupt status register for data transmission or receiving 
+threads requires exploring all possible interleavings between HW 
+and FW threads.  The number of interleavings could potentially be  
+exponential.  However, we observe a specific interaction pattern, 
+which resembles a producer-consumer relationship.  
+That is, a FW thread is mostly independent of the HW 
+thread they interact with~\cite{hvc,codes14}.  Specifically, 
+a FW thread is only responsible for configuring the 
+HW transactions by writing to memory mapped registers, or polling 
+the interrupt status register for data transmission, or receiving 
 incoming data packets.
@@
 Figure~\ref{fig:interleaving1} illustrates the producer-consumer relationship 
-in UART . The FW CFG is shown in the left and the 
-HW RTL code snippet is shown in the right. We abuse notations and 
+in UART . The FW CFG is shown in the left and the HW RTL code snippet 
+is shown in the right. We abuse notations and 
 represent $\mathcal{HT}$ in the form of RTL and $\mathcal{FT}$ as CFG
-for our illustration purpose. Here, $\mathcal{HT}$ is the producer of interrupt 
+for illustration purpose. Here, $\mathcal{HT}$ is the producer of interrupt 
 status signal, $irq\_o$, which is read by $\mathcal{FT}$ in state $s_1$. 
@@
 in And Inverter Graph (AIG) format.  Whereas, a word-level netlist is represented 
-in format that resembles SMT-LIB2
-standards~\footnote{http://smtlib.cs.uiowa.edu/}.  The bottom flow illustrates the
-translation of C program into static single assignment (SSA) form. 
+in format that resembles SMT-LIB2 standards~\footnote{http://smtlib.cs.uiowa.edu/}.  
+The bottom flow illustrates the translation of C program 
+into static single assignment (SSA) form. 
 Synthesizing netlist from RTL is a standard technique which is widely 
 used in hardware model checkers~\cite{DBLP:journals/tse/Clarke76}.
-Similarly, translating a C program into a SSA representation is a 
+Similarly, translating a C program into an SSA representation is a 
 standard technique which is widely used in 
@@
 co-verification.  We observe similar performance of bit-level and word-level 
-flow in \hwcbmcv. So, we only report bit-level results for \hwcbmcv in this paper. \\ 
+flow in \hwcbmcv. So, we only report bit-level results for \hwcbmcv in this
+paper. \\ 
+%\sjcmt{I think this can backfire. The reivewers may ask why were other results not reported if available}\\ 
 \textbf{\emph{Safety properties:}}
@@
 monolithic BMC in all scenarios (marked bold).  The average speedup for
-proving safety properties is on average $21\times$ for \verifox over
-\hwcbmcv.  The average speedup for detecting bugs is $48\times$ on average 
+proving safety properties is on average $21\times$ 
+%\sjcmt{is it average for table 3 only? or also table 4?} 
+for \verifox over \hwcbmcv.  The average speedup for detecting bugs is $48\times$ on average 
 for \verifox over \hwcbmcv.  Thus, \verifox outperforms \hwcbmcv 
@@
 {
-%\begin{scriptsize}
+\begin{scriptsize}
 \begin{tabular}{|l|l|l|l|l|}
@@
 The reason for better scalability of \verifox compared to 
-\hwcbmcv is attributed to the path-based exploration strategy combined 
-with eager path pruning and incremental SAT solving.  In the case of SoC, 
-the FW exercises only the micro-controller and transfer sequence of bytes to the XRAM port 
-bypassing peripherals connected to other ports such as hardware accelerator.  
+\hwcbmcv is attributed to the path-based exploration of a 
+sequential co-verification model using eager path pruning and 
+incremental SAT solving to automatically mine relevant scenario/transaction
+pairs.  In the case of SoC, the FW exercises only the micro-controller 
+and transfer sequence of bytes to the XRAM port bypassing peripherals 
+connected to other ports such as hardware accelerator.  
 This scenario allows path-based exploration techniques to prune the logic for
@@
 this interaction behavior in a sequential co-verification model through symbolic 
-execution which generates relevant scenario/transaction pairs.  However, this approach 
-is not applicable for co-designs that exhibits true concurrency~\cite{concurrency}, 
-that is, a FW its interacting HW threads do not show producer-consumer relationship.  
+execution by generating relevant scenario/transaction pairs.  However, this approach 
+is not applicable for co-designs that exhibits true concurrency~\cite{codesign}, 
+that is, a FW and its interacting HW threads do not show producer-consumer relationship.  
 In this case, it is imperative to consider all possible interleavings between participating 
-threads in an effecient manner.  However, our experience is that such 
-co-designs occurs rarely in practise.
+threads in an efficient manner.  To the best of our knowledge, the producer-consumer 
+interaction pattern is prevelant in many practical 
+co-designs~\cite{polig2014micro,polig2014fpl,giefers2015accelerating,hvc}.
 
@@
 
+\Omit{
 A system is comprised of a set of concurrent FW and HW models, which
-interleave asynchronously.  However, we observe a specific interaction
-pattern, which resembles a producer-consumer relationship.  We conjecture
-that this producer-consumer interaction pattern is not specific to the UART
- or SoC designs used as exemplars in this paper.  Malik et
-al.~in~\cite{hvc} showed that these patterns are meaningful in further
+interleave asynchronously.  Malik et al.~in~\cite{hvc} showed 
+that these patterns are meaningful in further
 settings -- a Linux device driver interacting with x86 QEMU emulator code or
-a Rockbox firmware interacting with an iAudio X5 device.
-
+a Rockbox firmware interacting with an iAudio X5 device.  Practical industrial 
+co-designs, such as IBM Text Accelerator co-design~\cite{polig2014micro,polig2014fpl} 
+and IBM coherent FFT coprocessor~\cite{giefers2015accelerating} also exhibits
+producer-consumer interaction pattern. 
+}
 Common practice in industry for system-level co-verification is to 
@@
 
+\Omit{
 The concept of symbolic execution~\cite{DBLP:journals/tse/Clarke76,
@@
 a unified co-verification model.  
-
+}
 %===============================================================================
@@
 %
-In this paper, we presented two approaches for verification of 
-HW/SW co-designs using formal techniques.  These approaches are 
-embodied in our tool \hwcbmcv and \verifox.  We presented a 
-notion of scenario and transaction for effective verification 
-of co-designs.  To this end, we presented a path-based algorithm
-to automatically mine scenario/transaction pairs.  We showed that 
-the construction of a co-verification model must leverage specification of 
-co-design properties over hardware and firmware events in order to 
-successfully apply formal methods in co-verification.  To enable this, we 
-presented two types of co-design properties, \emph{transaction level} and 
-\emph{component level}.  Our tools support co-designs written in Verilog RTL 
-and C.
-
-Our general observation is that monolithic BMC based approaches 
+In this paper, we presented two different approaches for formal verification of 
+HW/SW co-designs -- \emph{monolithic} and \emph{path-based}.  These approaches are 
+embodied in our tools, \hwcbmcv and \verifox, respectively.  Our tools support 
+co-designs written in Verilog RTL and C.  We also presented a specification language to 
+effectively capture co-design properties.  
+%To this end, we classify co-design properties into two types --  \emph{transaction level} and \emph{component level} property.  
+We proved several transaction and component level properties of UART and SoC
+design using \hwcbmcv and \verifox.  
+%We for proving safety as well as finding critical co-design bugs for a UART IP and a complex SoC design.  
+We uncovered three critical bugs in UART and one control-path bug in the SoC in 
+less than a minute.
+
+In practise, a FW exercises only a fragment of the HW state-space for a given scenario.  
+This renders many interactions between HW and FW transactions infeasible.   
+Our general observation is that bounded model checking technique in \hwcbmcv 
 cannot prune irrelevant transactions with respect to a given scenario, 
-and hence generate very complex formulas, which are difficult to solve. 
-Owing to specific optimizations in \verifox such as eager path pruning
-combined with incremental SAT solving, we experimentally show that \verifox
-is an order of magnitude faster than the \hwcbmcv.  We demonstrate applicability of our
-approach for proving safety as well as finding critical co-design bugs for 
-a UART  and a complex SoC design.  In the future, we plan to extend our 
-framework to co-design models that exhibit further interaction patterns.
+and hence generate a monolithic co-verification model, which are often 
+extremely difficult to solve with a SAT/SMT solver. On the other hand, 
+a path-based exploration strategy in \verifox is able to automatically 
+mine relevant scenario/transaction pairs in a sequential co-verification 
+model, owing to specific optimizations such as eager path pruning
+combined with incremental SAT solving.  Our experiments show that \verifox 
+is an order of magnitude faster than \hwcbmcv for proving safety as well as 
+bug finding.  In the future, we plan to extend our framework to co-design 
+models that exhibit further interaction patterns.
 

### 2017-04-07 paper.tex
sharable link

@@
     benchmarks in Verilog RTL and C 
-    here~\footnote{https://drive.google.com/folderview?id=0BynC6sd-wTYgWVQ4bXNtRDB5a2c\&usp=sharing}.\rmcmt{check
-    link}
+    here~\footnote{https://drive.google.com/file/d/0B1AtKu35m3XVOHd4U01yV0hwWlk/view?usp=sharing}.
 
@@
 compliant with industry standards for UART and interfaces with the wishbone
-bus.  The design statistics for UART is shown in Table~\ref{table:stats}.
+bus.  The design statistics for UART is shown in Table~\ref{table:stats}. \\
 %
@@
 memory.  The completion of the operation is determined by polling the
-appropriate memory-mapped registers in the FW.
+appropriate memory-mapped registers in the FW. \\
 %

### 2017-04-07 paper.tex
more fixes

@@
 drivers for circuitry well before RTL is finished.  A key risk is divergence
-of the hardware RTL from the behavior expected by the software.  Formal
-methods can deliver a proof that the RTL and the firmware match, but are
+of the hardware RTL from the behavior expected by the firmware.  Formal
+methods can deliver a proof that the RTL and the firmware behave correctly, but are
 difficult to scale up.  We propose to identify partitions of the firmware and
@@
 our tool \verifox.  We have experimentally compared \verifox with \hwcbmcv, 
-which constructs a single monolithic SAT/SMT instance, and observe speedup of 
-an order of magnitude over \hwcbmcv for proving safety properties as well as 
-detecting firmware/hardware bugs.
+which constructs a single monolithic SAT/SMT instance, and observe an average 
+speedup of $5\times$ over \hwcbmcv for proving safety properties as well as 
+detecting critical co-design bugs.
 %
@@
 Table~\ref{table:safe} shows that path-based symbolic execution dominates
-monolithic BMC in all scenarios (marked bold).  The average speedup for
-proving safety properties is on average $21\times$ 
-%\sjcmt{is it average for table 3 only? or also table 4?} 
-for \verifox over \hwcbmcv.  The average speedup for detecting bugs is $48\times$ on average 
-for \verifox over \hwcbmcv.  Thus, \verifox outperforms \hwcbmcv 
-in all scenarios.
+monolithic BMC in all scenarios (marked in bold). \verifox is on average 
+$8\times$ faster than \hwcbmcv, both for proving safety as well as 
+detecting bugs.  Thus, \verifox outperforms \hwcbmcv in all scenarios.
 
@@
 %\vspace{-1.3mm}
-\caption{Bounded safety proof times for verification of UART 
+\caption{Verification times for UART design
 \label{table:safe}}
@@
 \multicolumn{5}{|c|}{non-deterministic data and non-deterministic control} \\ \hline
-  data\_transfer & 20 & 86.92 & \textbf{17}.\textbf{42} & Safe $(\psi_{t})$ \\
-  \hline
-  data\_transfer & 30 & 102.92 & \textbf{56}.\textbf{29} & Safe $(\psi_{c})$ \\ 
+  data\_transfer & 20 & 86.18 & \textbf{17}.\textbf{42} & Safe $(\psi_{t})$ \\
+  \hline
+  AES\_feedback & 30 & 102.92 & \textbf{56}.\textbf{29} & Safe $(\psi_{c})$ \\ 
 \hline
 \multicolumn{5}{|c|}{non-deterministic data and non-deterministic control} \\ \hline
-  data\_transfer & 20 & 92.63 & \textbf{1}.\textbf{27} & Unsafe $(\psi_{c})$ \\ 
+  write\_XRAM & 20 & 92.63 & \textbf{14}.\textbf{78} & Unsafe $(\psi_{c})$ \\ 
+\hline
+  DMA & 32 & 128.63 & \textbf{68}.\textbf{19} & Safe $(\psi_{t})$ \\ 
 \hline
@@
 %\vspace{-1.3mm}
-\caption{Bounded safety proof times for verification of a SoC 
+\caption{Verification times for SoC Design
 \label{table:SoC}}
@@
 Table~\ref{table:SoC} gives the name of the scenario -- transmission with
-interrupt (data\_transfer).  Column~2 report the maximum loop bound in the 
-FW.  Column~3 present the co-verification times using \hwcbmcv
-at the bit-level.  Columns~4 report the verification time using \verifox. 
-Column~5 report the verification outcome. \\
+interrupt (data\_transfer), communication with AES (AES\_feedback), writing to 
+XRAM (write\_XRAM) and DMA (Direct Memory Access by Cryptographic Accelerator).  
+Column~2 report the maximum loop bound in the FW.  Column~3 present the 
+co-verification times using \hwcbmcv at the bit-level.  Columns~4 report 
+the verification time using \verifox. Column~5 report the verification outcome. \\
 \textbf{\emph{Safety properties:}}
@@
 component level properties for the SoC co-design.  Due to space 
-limitations, we describe some representative properties.  We check
-whether the acknowledgment for data transmission and data reception arrives
+limitations, we report~4 representative properties in Table~\ref{table:SoC}.  
+We check whether the acknowledgment for data transmission and data reception arrives
 from the micro-controller in the correct cycle.  We verify whether the
@@
 The result in Table~\ref{table:SoC} shows that \verifox is approximately
-$5\times$ faster than \hwcbmcv for proving safety.  For detecting bugs, 
-the speedup is $72\times$ for \verifox over \hwcbmcv. \\ 
+$2\times$ faster than \hwcbmcv for proving safety.  For detecting bugs, 
+the speedup is $6\times$ for \verifox over \hwcbmcv. \\ 
 \textbf{\emph{Monolithic versus Path-based:}}
@@
 %We for proving safety as well as finding critical co-design bugs for a UART IP and a complex SoC design.  
-We uncovered three critical bugs in UART and one control-path bug in the SoC in 
-less than a minute.
+We uncovered three critical bugs in UART and one control-path bug in the SoC 
+within only couple of minutes.
 

### 2017-04-07 paper.tex
spelling

@@
 for constructing a unified FW-HW model~\cite{fmsd02,emsoft07,fase10} 
-are not useful in practise for three reasons -- 1) use of abstract HW models 
+are not useful in practice for three reasons -- 1) use of abstract HW models 
 instead of RTL implementation, 2) the unified model
@@
 verification process.  However, we observe that in practice, 
-producer-consumer relationship is prevelant in many industrial 
+producer-consumer relationship is prevalent in many industrial 
 co-designs~\cite{polig2014micro,polig2014fpl,giefers2015accelerating} --
@@
 patterns.  This drastically reduces the total number of interleavings 
-between a FW and HW threads and simplies the overall complexity of the 
+between a FW and HW threads and simplifies the overall complexity of the 
 verification task. 
@@
 %
-We verify a total of 7 transaction level propertes and 12 
+We verify a total of 7 transaction level properties and 12 
 component level properties for the SoC co-design.  Due to space 
 limitations, we report~4 representative properties in Table~\ref{table:SoC}.  
-We check whether the acknowledgment for data transmission and data reception arrives
+We check whether the acknowledgement for data transmission and data reception arrives
 from the micro-controller in the correct cycle.  We verify whether the
@@
 threads in an efficient manner.  To the best of our knowledge, the producer-consumer 
-interaction pattern is prevelant in many practical 
+interaction pattern is prevalent in many practical 
 co-designs~\cite{polig2014micro,polig2014fpl,giefers2015accelerating,hvc}.
@@
 
-In practise, a FW exercises only a fragment of the HW state-space for a given scenario.  
+In practice, a FW exercises only a fragment of the HW state-space for a given scenario.  
 This renders many interactions between HW and FW transactions infeasible.   

### 2017-04-07 paper.tex
more spelling
conclusion

@@
 relevant scenario/transaction pairs through symbolic execution.  Instead, the 
-technique relies on the underlying SAT/SMT solver to effeciently reason about 
+technique relies on the underlying SAT/SMT solver to efficiently reason about 
 the co-verification model. 
@@
 combined with incremental SAT solving.  Our experiments show that \verifox 
-is an order of magnitude faster than \hwcbmcv for proving safety as well as 
+is on average $5\times$ faster than \hwcbmcv for proving safety as well as 
 bug finding.  In the future, we plan to extend our framework to co-design 

### 2017-04-07 paper.tex
fixes
minor

@@
 %
-\subsection{Approach 1: Path-based Co-verification Technique}
+\subsection{Approach 1: Path-based Co-verification}
 %
@@
 %
-\subsection{Approach 2: Monolithic Co-verification Technique}
+\subsection{Approach 2: Monolithic Co-verification}
 %
@@
 %===============================================================================
-\section{Property Specification for Co-verification}\label{property}
+\section{Co-verification Property}\label{property}
 %===============================================================================
@@
 machine with 48\,GB RAM.  All times reported are in seconds.  The timeout 
-for all our experiments was set to 2~hours.  
+for all our experiments was set to 2~hours.  The performance of bit-level 
+and word-level flow in \hwcbmcv are similar. So, we only report bit-level 
+results for \hwcbmcv.  MiniSAT-2.2.0~\cite{DBLP:conf/sat/EenB05} was used 
+as underlying SAT solver with \hwcbmcv and \verifox.  The focus of our 
+experiments is to compare the performance of path-based technique in \verifox 
+with monolithic BMC approach in \hwcbmcv for verification of UART and SoC design.  
+\\ 
 %
@@
 Column~6 gives the verification times using \verifox.  Column~7 report 
-the verification outcome. The focus of our experiment is to compare 
-the performance of path-based technique with monolithic BMC approach for 
-co-verification.  We observe similar performance of bit-level and word-level 
-flow in \hwcbmcv. So, we only report bit-level results for \hwcbmcv in this
-paper. \\ 
-%\sjcmt{I think this can backfire. The reivewers may ask why were other results not reported if available}\\ 
+the verification outcome.\\ 
+%
 \textbf{\emph{Safety properties:}}
@@
 %\vspace{-1.3mm}
-\caption{Verification times for UART design
+  \caption{Verification of UART (All time in seconds)
 \label{table:safe}}
@@
 \cline{1-5}
-      &       &   Time      & Time &  \\
+      &       &   Time (seconds)       & Time (seconds) &  \\
 \cline{1-5}      
@@
 %\vspace{-1.3mm}
-\caption{Verification times for SoC Design
+  \caption{Verification times for SoC Design (All time in Seconds)
 \label{table:SoC}}
@@
 co-designs written in Verilog RTL and C.  We also presented a specification language to 
-effectively capture co-design properties.  
-%To this end, we classify co-design properties into two types --  \emph{transaction level} and \emph{component level} property.  
-We proved several transaction and component level properties of UART and SoC
-design using \hwcbmcv and \verifox.  
-%We for proving safety as well as finding critical co-design bugs for a UART IP and a complex SoC design.  
-We uncovered three critical bugs in UART and one control-path bug in the SoC 
-within only couple of minutes.
+effectively capture co-design properties.  We proved several transaction and component 
+level properties of UART and SoC design using \hwcbmcv and \verifox.  We uncovered three 
+critical bugs in UART and one control-path bug in the SoC within only couple of minutes.
 
@@
 combined with incremental SAT solving.  Our experiments show that \verifox 
-is on average $5\times$ faster than \hwcbmcv for proving safety as well as 
-bug finding.  In the future, we plan to extend our framework to co-design 
-models that exhibit further interaction patterns.
+is on average $5\times$ faster than \hwcbmcv for proving safety as well as bug
+finding.  In the future, we plan to extend our framework to co-design 
+that exhibit further interaction patterns.
 

### 2017-04-07 paper.tex
more fixes

@@
 \scalebox{.55}{\import{figures/}{st.pspdftex}}
-\caption{Scenario and Firmware Transaction
+  \caption{Scenario (left) and Firmware Transactions (right)
 \label{fig:st}}
@@
 predicates based on the values in $adr\_i$.  The next step is determined by
-the values of predicates, $'UART\_MC, 'UART\_IE, 'UART\_CT$.  Assuming that
-$'UART\_MC$ holds true, the execution proceeds to $t_6$.  During the
+the values of predicates, $UART\_MC, UART\_IE, UART\_CT$.  Assuming that
+$UART\_MC$ holds true, the execution proceeds to $t_6$.  During the
 execution of $t_6$, three parallel state update $(dtr\_no, rts\_no,
@@
 translated into a C program, called a 
-\textit{software netlist}~\cite{mtk2016,mskm2016,mkm2015} following synthesis 
+\textit{software netlist}~\cite{mtk2016} following synthesis 
 semantics. The software netlist model is cycle-accurate as well as 
@@
 but promising approach for synthesizing software 
-models from RTL description, primarily targeted for word-level formal verification.  
-To the best of our knowledge, this is the first attempt to demonstrate the 
-efficacy of such a translation in the context of hardware/software co-verification. 
+models from RTL description, primarily targeted for formal 
+verification~\cite{mtk2016,mskm2016,mkm2015}.  To the best of our knowledge, 
+this is the first attempt to demonstrate the efficacy of such a 
+translation in the context of hardware/software co-verification. 
 % 
@@
 Figure~\ref{fig:interleaving1} illustrates the producer-consumer relationship 
-in UART . The FW CFG is shown in the left and the HW RTL code snippet 
+in UART. The FW CFG is shown in the left and the HW RTL code snippet 
 is shown in the right. We abuse notations and 
@@
 $(\mathcal{C})$. Arrows with empty description below denotes reading of interface
-variables or local variables in $\mathcal{FT}$.  Arrows with no description
+signals or local FW variables in $\mathcal{FT}$.  Arrows with no description
 simply denotes control-flow join.  The entries in the right column of
 Table~\ref{transaction} shows the corresponding transactions in HW.  We 
-denote a transaction in HW module with the name of the module,
-transmitter module in UART ($uart\_tx$), receiver module in UART ($uart\_rx$), or
-the top UART module ($uart\_top$).
+denote a transaction in HW with the name of the module, transmitter module 
+in UART ($uart\_tx$), receiver module in UART ($uart\_rx$), or the top 
+UART module ($uart\_top$).
 %
@@
 module of the HW RTL, since the translation from RTL to software preserves
-the module hierarchy.  The interface variables $\{Var\_1,\dots,Var\_n\}$ 
+the module hierarchy.  The interface signals $\{Var\_1,\dots,Var\_n\}$ 
 (input, output and inout ports) are declared inside the 
@@
 \hwcbmcv generates a monolithic co-verification model from AIG and SSA through 
-in-tandem symbolic execution of HW and FW components.
+in-tandem symbolic execution of HW and FW models.
 
@@
 A {\em component level} property ($\psi_{c}$) is defined purely at the 
-level of individual components of a co-design system. Recall that a component 
+level of individual components of a co-design. Recall that a component 
 may be a HW model, a SW model or an interface model which contains only the 
@@
 The reason for better scalability of \verifox compared to 
-\hwcbmcv is attributed to the path-based exploration of a 
+\hwcbmcv is attributed to the path-based exploration of the 
 sequential co-verification model using eager path pruning and 
 incremental SAT solving to automatically mine relevant scenario/transaction
-pairs.  In the case of SoC, the FW exercises only the micro-controller 
-and transfer sequence of bytes to the XRAM port bypassing peripherals 
-connected to other ports such as hardware accelerator.  
+pairs.  In the case of SoC scenario (data\_transfer), the FW exercises 
+only the micro-controller and transfer sequence of bytes to the XRAM port 
+bypassing peripherals connected to other ports such as hardware accelerator.  
 This scenario allows path-based exploration techniques to prune the logic for
@@
 between the HW and FW threads.  We have shown that this is extremely beneficial for 
-co-designs that exhibits producer-consumer relationship.  
+co-designs that exhibits producer-consumer relationship.  Such interaction pattern 
+is prevalent in many practical co-designs~\cite{polig2014micro,polig2014fpl,giefers2015accelerating,hvc}. 
 In particular, our path-based algorithm in \verifox is able to suitably exploit 
@@
 In this case, it is imperative to consider all possible interleavings between participating 
-threads in an efficient manner.  To the best of our knowledge, the producer-consumer 
-interaction pattern is prevalent in many practical 
-co-designs~\cite{polig2014micro,polig2014fpl,giefers2015accelerating,hvc}.
+threads in an efficient manner.
 
